\section{Proverb 11 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} Verse 4 has 13 words and 13 unique words. the words ``\emph{is}'' (italic), ``a,'' and ``his'' are used 13 times in the chapter. The 13-letter words ``transgressors,'' ``righteousness,'' and ``understanding'' are found in the chapter. So, there are three lists of 13\\
\\
The word ``a:''
\begin{compactenum}
    \item a ``just weight'' (1)
    \item a ``wicked man'' (7)
    \item a ``man of understanding'' (12)
    \item a ``faithful spirit'' (13)
    \item a ``stranger'' (15)
    \item a ``deceitful work'' (18)
    \item a ``sure reward'' (18)
    \item a ``forward heart'' (20)
    \item a ``jewel of gold'' (22)
    \item a ``swine's snout'' (22)
    \item a ``fair woman'' (22)
    \item a ``branch'' (28)
    \item a ``tree of life'' (30)\\
\end{compactenum}
The word ``his:''
\begin{compactenum}
    \item his ``delight''
    \item his ``way'' (5)
    \item his ``own wickedness'' (5)
    \item his ``stead'' (8)
    \item his ``neighbour'' (9)
    \item his ``nieghbour'' (12)
    \item his ``peace'' (12)
    \item his ``own soul'' (17)
    \item his ``own flesh'' (17)
    \item his ``own death'' (19)
    \item his ``delight'' (20)
    \item his ``riches'' (28)
    \item his ``own house'' (29)\\
\end{compactenum}
The word ``\emph{is}:''
\begin{compactenum}
    \item \emph{is} ``abomination'' (1)
     \item \emph{is} ``his delight'' (1)
    \item \emph{is} ``wisdom'' (2)
    \item \emph{is} ``shouting'' (10)
     \item ``where no counsel'' \emph{is}  (14)
     \item ``there'' \emph{is} ``safety'' (14)
    \item ``he that is'' \emph{is} ``cruel'' (17)
   \item \emph{is} ``a fair woman''   (22)
    \item \emph{is} ``only good'' (the desire of the righteous) (23)
    \item \emph{is} ``wrath'' (the expectation of the wicked) (23)
    \item \emph{is} ``that withholdeth'' (24)
    \item \emph{is} ``a tree of life'' (30)
    \item \emph{is} ``wise'' (30)
\end{compactenum}

\subsection{Proverb 11:1}
The verse directly addresses double-standards, and by implication the references in scripture to double hearts (1 Chronicles 12:33, Psalm 12:2),  double tongue (1 Timothy 5:17), and double mind (James 1:8, 4:8).  The verse is incorrectly used to argue about having ``balance'' in your live, as that is not the focus of the balance.  Balance is a good thing, and needed. But this verse is not speaking of such.  This could be a spiritual application.  The verse is speaking of equity in one's dealings in life.

\subsection{Proverb 11:14}
We have three solid examples in scripture. in 1 Kings 12:1-19, we have good counsel that is rejected. In Isaiah 19:11-14 we have bad counsel accepted. And in Acts 15:6-21, we have good counsel accepted. \footnote{\textbf{Acts 15:6-21} - And the apostles and elders came together for to consider of this matter. [7] And when there had been much disputing, Peter rose up, and said unto them, Men and brethren, ye know how that a good while ago God made choice among us, that the Gentiles by my mouth should hear the word of the gospel, and believe. [8] And God, which knoweth the hearts, bare them witness, giving them the Holy Ghost, even as he did unto us; [9] And put no difference between us and them, purifying their hearts by faith. [10] Now therefore why tempt ye God, to put a yoke upon the neck of the disciples, which neither our fathers nor we were able to bear? [11] But we believe that through the grace of the Lord Jesus Christ we shall be saved, even as they.[12] Then all the multitude kept silence, and gave audience to Barnabas and Paul, declaring what miracles and wonders God had wrought among the Gentiles by them. [13] And after they had held their peace, James answered, saying, Men and brethren, hearken unto me: [14] Simeon hath declared how God at the first did visit the Gentiles, to take out of them a people for his name. [15] And to this agree the words of the prophets; as it is written, [16] After this I will return, and will build again the tabernacle of David, which is fallen down; and I will build again the ruins thereof, and I will set it up: [17] That the residue of men might seek after the Lord, and all the Gentiles, upon whom my name is called, saith the Lord, who doeth all these things. [18] Known unto God are all his works from the beginning of the world. [19] Wherefore my sentence is, that we trouble not them, which from among the Gentiles are turned to God: [20] But that we write unto them, that they abstain from pollutions of idols, and from fornication, and from things strangled, and from blood. [21] For Moses of old time hath in every city them that preach him, being read in the synagogues every sabbath day.}\footnote{\textbf{1 Kings 12:1-19} - And Rehoboam went to Shechem: for all Israel were come to Shechem to make him king. [2] And it came to pass, when Jeroboam the son of Nebat, who was yet in Egypt, heard of it, (for he was fled from the presence of king Solomon, and Jeroboam dwelt in Egypt;) [3] That they sent and called him. And Jeroboam and all the congregation of Israel came, and spake unto Rehoboam, saying, [4] Thy father made our yoke grievous: now therefore make thou the grievous service of thy father, and his heavy yoke which he put upon us, lighter, and we will serve thee. [5] And he said unto them, Depart yet for three days, then come again to me. And the people departed. [6] And king Rehoboam consulted with the old men, that stood before Solomon his father while he yet lived, and said, How do ye advise that I may answer this people? [7] And they spake unto him, saying, If thou wilt be a servant unto this people this day, and wilt serve them, and answer them, and speak good words to them, then they will be thy servants for ever. [8] But he forsook the counsel of the old men, which they had given him, and consulted with the young men that were grown up with him, and which stood before him: [9] And he said unto them, What counsel give ye that we may answer this people, who have spoken to me, saying, Make the yoke which thy father did put upon us lighter? [10] And the young men that were grown up with him spake unto him, saying, Thus shalt thou speak unto this people that spake unto thee, saying, Thy father made our yoke heavy, but make thou it lighter unto us; thus shalt thou say unto them, My little finger shall be thicker than my father's loins. [11] And now whereas my father did lade you with a heavy yoke, I will add to your yoke: my father hath chastised you with whips, but I will chastise you with scorpions. [12] So Jeroboam and all the people came to Rehoboam the third day, as the king had appointed, saying, Come to me again the third day. [13] And the king answered the people roughly, and forsook the old men's counsel that they gave him; [14] And spake to them after the counsel of the young men, saying, My father made your yoke heavy, and I will add to your yoke: my father also chastised you with whips, but I will chastise you with scorpions. [15] Wherefore the king hearkened not unto the people; for the cause was from the LORD, that he might perform his saying, which the LORD spake by Ahijah the Shilonite unto Jeroboam the son of Nebat. [16] So when all Israel saw that the king hearkened not unto them, the people answered the king, saying, What portion have we in David? neither have we inheritance in the son of Jesse: to your tents, O Israel: now see to thine own house, David. So Israel departed unto their tents. [17] But as for the children of Israel which dwelt in the cities of Judah, Rehoboam reigned over them. [18] Then king Rehoboam sent Adoram, who was over the tribute; and all Israel stoned him with stones, that he died. Therefore king Rehoboam made speed to get him up to his chariot, to flee to Jerusalem. [19] So Israel rebelled against the house of David unto this day.}

\subsection{Proverb 11:30}
The verse is aptly applied to evangelism. It is also extended to the attempts of military and diplomacy to sway the hearts of a given population - it is much better to convince a people not to fight than to see the death and destruction of war.  ``Winning souls'' is, though, a great deal more than door-knocking and quoting the Roman's Road plan of salvation.  Winning a war is often the easy part: convincing the losers that they have lost is often a different matter.