\section{Proverb 17 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} The 13-letter words ``whithersoever,'' ``transgression,'' and ``understanding,'' are used in the chapter. There are 13 words in verses Proverb 17:7 and 17:17. There are 13 unique words in verse 10, 17, and 26.

\subsection{Proverb 17 Introduction}
A theme of the chapter might be practical comparisons between foolish actions and wise ones.

\subsection{Proverb 17:1}
A house full of sacrifices is a house of wealth that has much livestock available to be used as sacrifices. But if this wealthy house is full of contention it is misery.

\subsection{Proverb 17:2}
Which one shall get the place of trust, honor, regard, and responsibility? A goof example of a son that caused shame would be Absalom. Another would be Eli's sons. Examples of servants would include Abraham's servant, Eliezer. In addition, consider, Elisha.  Reuben was the beginning of Jacob's strength — and yet he lost his dignity to his younger brother Joseph, who, according to the customs of those times, was to be in some degree under his government. But even when partiality prevails over reason in the behavior of parents — folly, by its native consequences, and the just providence of God, does often reduce men from honor and wealth — to poverty and disgrace, and place them below those over whom they once tyrannized. (George Lawson) A bigger example might be Israel itself as God's son. They brought shame and were taken over by God's servant, Nebuchadnezzar. What about the prodigal son and his older brother? It is how they ended up that mattered. % \href{https://www.calvarychapeljonesboro.org/proverb-a-day/wisdom-and-success-for-servants-proverbs-172}{Example} \href{https://www.ptlb.com/post/2017/02/17/proverbs-17-2}{Breakfast with Solomon - Proverbs 17:2} \href{https://www.biblestudytools.com/commentaries/gills-exposition-of-the-bible/proverbs-17-2.html}{Proverbs 17:2 - Jarchi: Cyclopedia of Biblical, Theological and Ecclesiastical Literature} \href{https://www.gracegems.org/Lawson/Proverbs\%2017.htm}{George Lawson}

