\section{Proverb 12 Comments}

\section{Numeric Nuggets}
\textbf{13:} Verses 12 and 24 have 13 unique words. The 13-letter words ``understanding,'' ``transgression, '' and `righteousness'' are used in the chapter. The word ``a'' is used 13 times in the chapter.

\subsection{Proverb 12 Introduction}

\normalsize
\begin{longtable}{c|p{2.1in}|p{2.1in}}
\caption[Comparing Two Ways]{Comparing Two Ways} \label{table:Comparing Two Ways} \\ 
\hline \multicolumn{1}{|c|}{\textbf{vs}} & \multicolumn{1}{c|}{\textbf{The Good}} &
\multicolumn{1}{c|}{\textbf{The Bad}} \\ \hline 
\endfirsthead
 
\multicolumn{3}{c}
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\ 
\hline \multicolumn{1}{|c|}{\textbf{vs}} & \multicolumn{1}{c|}{\textbf{The Good}} &
\multicolumn{1}{c|}{\textbf{The Bad}} \\ \hline 
\endhead
 
\hline \multicolumn{3}{|r|}{{Continued if needed}} \\ \hline
\endfoot
 
\hline \hline
\endlastfoot
1 & loves instruction & hateth reproof \\ \hline
2 & obtains favour from the Lord & is condemned \\ \hline
3 & shall not be moved & is not established by wickedness \\ \hline
4 & virtuous woman is a crown to her husband & she that maeth ashamed is rottenness in a husband's bones \\ \hline
5 & thoughts of the righteous are right & counsels of the wicked are deceit \\ \hline
6 & mouth of the upright shall deliver them & the words of the wicked are to wait for blood \\ \hline
7 & house of the righteous shall stand & the wicked are overthrown and are not \\ \hline
8 & a man is commended according to his wisdom & those of a perverse heart are despised \\ \hline
10 & regards the life of his beast & are cruel \\ \hline
11 & he that tilleth his land shall be satisfied with bread & follows vain persons \\ \hline
12 & the root of the righteous yieldeth bread & desire the net of evil men \\ \hline
13 & shall come out of trouble & snared by the trangression of his lips \\ \hline
15 & hearkeneth unto counsel & is right in his own eyes\\ \hline
16 & a prudent man covereth shame & a fool's wrath is preentky known \\ \hline
17 & He that speaketh truth sheweth forth righteousness & false witness shews deceit \\ \hline
23 & a prudent man concealeth knowledge & heart of fools proclaimeth foolishness. \\ \hline
24 & The hand of the diligent shall bear rule  & the slothful shall be under tribute \\ \hline
27 & the substance of a diligent man is precious  & The slothful man roasteth not that which he took in hunting \\ \hline
28 & the way of righteousness is life  & death\\ \hline

\end{longtable}

\subsection{Proverb 12:1}
Proverb 12 starts with the ``brute'' in verse 1 and ends with the ``way of righteousness'' in verse 28.
\input{WordsAndPhrasesInScripture/WIS-formsOfTheWordBrute}

\subsection{Proverb 12:4}
The phrase ``virtuous woman'' is found only three times in scripture: once in Ruth 3:11, here, and in Proverb 31:10. So, we can take Ruth as the only Biblical example.\footnote{\textbf{Ruth 3:11} - And now, my daughter, fear not; I will do to thee all that thou requirest: for all the city of my people doth know that thou art a virtuous woman.}


