\section{Proverbs 8 Outlines}
\subsection{My Outlines}

\subsubsection{Wisdom is There}

\index[speaker]{Keith Anthony!Proverb 08 (Wisdom is There)}
\index[series]{Proverbs (Keith Anthony)!Pro 08 (Wisdom is There)}
\index[date]{2016/05/08!Proverb 08 (Wisdom is There) (Keith Anthony)}
%\textbf{Lineage}: adpated from S. Conway\\
%\textbf{Introduction}: 
\begin{compactenum}[I.][7]
    \item There at the \textbf{Beginning} \index[scripture]{Proverbs!Pro 08}(Pro 8)
    \item There for a \textbf{Blessing} \index[scripture]{Proverbs!Pro 08}(Pro 8)
    \item There as a \textbf{Barrier} \index[scripture]{Proverbs!Pro 08}(Pro 8)
    \item There as a \textbf{Banner} \index[scripture]{Proverbs!Pro 08}(Pro 8)
    \item There to \textbf{Behold} \index[scripture]{Proverbs!Pro 08}(Pro 8)
    \item There in \textbf{Boldness} \index[scripture]{Proverbs!Pro 08}(Pro 8)
    \item There to \textbf{Abide} \index[scripture]{Proverbs!Pro 08}(Pro 8)
\end{compactenum}


\subsubsection{What Wisdom Does}

\index[speaker]{Keith Anthony!Proverb 08 (What Wisdom Does)}
\index[series]{Proverbs (Keith Anthony)!Pro 08 (What Wisdom Does)}
\index[date]{2016/05/08!Proverb 08 (What Wisdom Does) (Keith Anthony)}
%\textbf{Lineage}: adpated from S. Conway\\
%\textbf{Introduction}: 
\begin{compactenum}[I.][7]
    \item It \textbf{Cries}  \index[scripture]{Proverbs!Pro 08:01}(Pro 8:1)
    \item It \textbf{Calls}  \index[scripture]{Proverbs!Pro 08:04}(Pro 8:4)
    \item It \textbf{Cares} for those who seek it \index[scripture]{Proverbs!Pro 08:11}(Pro 8:11)
    \item It \textbf{Provides Counsel} \index[scripture]{Proverbs!Pro 08:14}(Pro 8:14)
    \item It \textbf{Offers Communion} \index[scripture]{Proverbs!Pro 08:17}(Pro 8:17)
    \item It \textbf{Causes} Success \index[scripture]{Proverbs!Pro 08:21}(Pro 8:21)
    \item It \textbf{Condemns} \index[scripture]{Proverbs!Pro 08:36}(Pro 8:36)
\end{compactenum}

\subsubsection{More About Wisdom}

\index[speaker]{Keith Anthony!Proverb 08 (More About Wisdom)}
\index[series]{Proverbs (Keith Anthony)!Pro 08 (More About Wisdom)}
\index[date]{2016/05/08!Proverb 08 (More About Wisdom) (Keith Anthony)}
\begin{compactenum}[I.][7]
    \item The \textbf{Message of Wisdom}  \index[scripture]{Proverbs!Pro 08:05}(Pro 8:5) -- Is an appeal for mankind to listen.
    \item The \textbf{Majesty of Wisdom}  \index[scripture]{Proverbs!Pro 08:06}(Pro 8:6) -- Speaks of excellent things and of right things.
    \item The \textbf{Manner of Wisdom}  \index[scripture]{Proverbs!Pro 08:06}(Pro 8:6) -- Wisdom responds to those that seek her.  It rewards those that follow. It enriches.  It rightens those who listen.
    \item The \textbf{Mouth of Wisdom}  \index[scripture]{Proverbs!Pro 08:07,08}(Pro 8:7, 8) -- Speaks truth and only truth.  It is dependable.  It is distinct. It is definite.
    \item The \textbf{Mastery of Wisdom}  \index[scripture]{Proverbs!Pro 08:22-31}(Pro 8:22-31) -- Wisdom was there during the acts of creation. Verse 31 tells us that it rejoiced at creation. 
    \item The \textbf{Manna of Wisdom}  \index[scripture]{Proverbs!Pro 08:30}(Pro 8:30) -- Wisdom should be and is like manna to one who follows it.  It is a delight.  It is his diet.  It is his deliverance. 
    \item The \textbf{Man of Wisdom}  \index[scripture]{Proverbs!Pro 08:34}(Pro 8:34) -- Seeks, follows, obeys, and continues in wisdom. He is blessed for it. Verse 34 describes a follower of wisdom as one who is waiting for wisdom to arrive, waiting at wisdom's doorway.
\end{compactenum}

\subsubsection{Wisdom, Crying Out}

\index[speaker]{Keith Anthony!Proverb 08 (Wisdom, Crying Out)}
\index[series]{Proverbs (Keith Anthony)!Pro 08 (Wisdom, Crying Out)}
\index[date]{2021/02/07!Proverb 08 (Wisdom, Crying Out) (Keith Anthony)}
\begin{compactenum}[I.][8] 
     \item A \textbf{Pronounced} Cry \index[scripture]{Proverbs!Pro 08:01} (Pro 8:1) \footnote{Outlines inspired by Hubbard's \emph{The Preacher's Commentary - Proverbs} \cite{hubbard2004preacher}}
     \item A \textbf{Public} Cry \index[scripture]{Proverbs!Pro 08:02-03} (Pro 8:2-3) 
     \item A \textbf{Personal} Cry \index[scripture]{Proverbs!Pro 08:04-05} (Pro 8:4-5) 
     \item A \textbf{Proven} Cry \index[scripture]{Proverbs!Pro 08:06-09} (Pro 8:6-9) 
     \item A \textbf{Plain} Cry \index[scripture]{Proverbs!Pro 08:09} (Pro 8:9) 
     \item A \textbf{Purposeful} Cry \index[scripture]{Proverbs!Pro 08:09} (Pro 8:9) 
     \item A \textbf{Pointed} Cry \index[scripture]{Proverbs!Pro 08:10} (Pro 8:10
\end{compactenum} 


\subsubsection{Responding to Wisdom}

\index[speaker]{Keith Anthony!Proverb 08 (Responding to Wisdom)}
\index[series]{Proverbs (Keith Anthony)!Pro 08 (Responding to Wisdom)}
\index[date]{2021/05/07!Proverb 08 (Responding to Wisdom) (Keith Anthony)}
\begin{compactenum}
    \item The \textbf{High Places} of Wisdom (Proverb 8:1-4)
    \item The \textbf{Heart} of the Listener (Proverb 8:5)
    \item \textbf{Hearing the Cry} (Proverb 8:6-10)
    \item \textbf{Help} from Wisdom (Proverb 8:11-17)
    \item The \textbf{Honour} from Wisdom (Proverb 8:18-20)
    \item The \textbf{History} of Wisdom (Proverb 8:21-31)
    \item \textbf{Hearkening} to Wisdom (Proverb 8:32-36)
\end{compactenum}


\subsubsection{The Ministry of Wisdom}
\index[speaker]{Keith Anthony!Proverb 08 (The Ministry of Wisdom)}
\index[series]{Proverbs (Keith Anthony)!Pro 08 (The Ministry of Wisdom)}
\index[date]{2021/05/07!Proverb 08 (The Ministry of Wisdom) (Keith Anthony)}
\begin{compactenum}[I.][8]     
    \item It \textbf{Gives Us Fear of the Lord}  \index[scripture]{Proverbs!Pro 08:13}(Pro 8:13)
    \item It \textbf{Grows Spectacular Fruit}  \index[scripture]{Proverbs!Pro 08:19}(Pro 8:19)
    \item It \textbf{Provides Fountains}  \index[scripture]{Proverbs!Pro 08:28}(Pro 8:28)
    \item It \textbf{Builds Foundations}  \index[scripture]{Proverbs!Pro 08:29}(Pro 8:29)
    \item It \textbf{Makes  a Way  to Get Favour from the Lord}  \index[scripture]{Proverbs!Pro 08:35}(Pro 8:35)
\end{compactenum} 
