\section{Proverb 7 Comments}

\subsection{Numeric Nuggets}
There is one 13-letter word in Proverb 7, ``understanding.'' Verses Proverb 7:3, 7:14, and 7:19 have 13 words. Verses 8, 13, 14, and 19 had thirteen unique words. The seduction of the man void of understanding starts in verse 13. Verse 2, a commandment to ``keep my commandments'' starts with the 13$^{th}$ word in the chapter.

\subsection{Proverbs 7 Introduction}
One theme of the chapter is temptation. It is pictured by a loose woman, perhaps a harlot (she certainly is said to dress as one). This loose woman tempts with the desires of the flesh. This woman is connected with the ``strange woman'' who is further connected with false religion, and specifically the ``Babylon Mystery Religion'' of Revelation 18.\\
\\
\noindent In the chapter, Temptation:
\begin{compactenum}
    \item \textbf{Appeals} to the Senses
    \item Is \textbf{Ever-Present}
    \item Is \textbf{Opportunistic}
    \item Is \textbf{Persistent}
    \item Is \textbf{Predatory}
    \item Is \textbf{Public}
    \item Is \textbf{Impudent}
\end{compactenum}

\subsection{Proverb 7:7}
The phrase ``void of understanding'' is used 5 times, all in Proverbs 7:7, 10:13, 12:11, 17:18, and 24:30. He will (1) get to rod, (2) follow vain persons, (3) strike hands and become surety, and (4) be negligent in duties.

\subsection{Proverb 7:13}
The word ``impudent'' means ``without respect toward another.''  It is related to the word ``insolent,'' showing a rude an arrogant lack of respect.

\subsection{Proverb 7:17}
Cinnamon connects this woman to Babylon the great in Revelation 18:13, making the type all the more clear. \footnote{\textbf{Revelation 18:10-13} - Standing afar off for the fear of her torment, saying, Alas, alas, that great city Babylon, that mighty city! for in one hour is thy judgment come. [11] And the merchants of the earth shall weep and mourn over her; for no man buyeth their merchandise any more: [12] The merchandise of gold, and silver, and precious stones, and of pearls, and fine linen, and purple, and silk, and scarlet, and all thyine wood, and all manner vessels of ivory, and all manner vessels of most precious wood, and of brass, and iron, and marble, [13] And cinnamon, and odours, and ointments, and frankincense, and wine, and oil, and fine flour, and wheat, and beasts, and sheep, and horses, and chariots, and slaves, and souls of men.}