\section{Proverb 5 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} In the chapter, verses 1, 9, 16, and 18 have 13 words. The chapter uses the 13-letter word ``understanding.'' The word ``understanding'' is the 13$^{th}$ word in the chapter! Verses 11, and 6  have 13 unique words. There are 13 words in italics in the chapter.

%\subsection{Proverb 5:3}
%\subsection{Proverb 5:4}
%\subsection{Proverb 5:5}
%\subsection{Proverb 5:6}
%\subsection{Proverb 5:7}
%\subsection{Proverb 5:8}
%\subsection{Proverb 5:9}
%\subsection{Proverb 5:10} 

\subsection{Proverb 5:16}
Table~\ref{table:CorruptionProv5:16} shows modern corruptions of the verse. 

\subsection{Proverb 5:19}
See references to breasts in Song of Solomon (verses 1:13, 4:5, 7:3, 7:7, 7:8, 8:1, 8:8, and 8:10). 

\subsection{Proverb 5:20}
Why indeed? Warnings against such have been provided, the right way prepared. 

\subsection{Proverb 5:21}
One of the things being pondered, no doubt, is the question posed in verse 20. See references to the ``eyes of the Lord'', found 22 times, in 21 chapters, in 13 books (Genesis 6:8, Deuteronomy 11:12, Deuteronomy 13:18, 1 Samuel 26:24, 2 Samuel 15:25, 1 Kings 15:5, 1 Kings 15:11, 1 Kings 16:25, 1 Kings 22:43, 2 Chronicles 14:2, 2 Chronicles 16:9, 2 Chronicles 21:6, 2 Chronicles 29:6, Psalms 34:15, Proverbs 5:21, Proverbs 15:3, Proverbs 22:12, Isaiah 49:5, Jeremiah 52:2, Amos 9:8, Zechariah 4:10, and 1 Peter 3:12).

\newpage

\begin{mdframed}[style=MyFrame]
\begin{center}
\begin{longtable}{|p{.5in}|p{3.5in}|}

\caption[Corruption Alert: Proverb 5:16]{Corruption Alert: Proverb 5:16} \label{table:CorruptionProv5:16} \\ 

\hline  
\multicolumn{1}{|c|}{\textbf{Version}} & 
\multicolumn{1}{c|}{\textbf{Corruption}}  \\ \hline 
\endfirsthead
 
\multicolumn{2}{c}
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\  \hline  
\multicolumn{1}{|c|}{\textbf{Version}} & 
\multicolumn{1}{c|}{\textbf{Corruption}}  \\ \hline 
\endhead
 
\hline \multicolumn{2}{|r|}{{Continued on next page}} \\ \hline
\endfoot 
\textcolor[rgb]{0.00,0.00,1.00}{AV} & \textcolor[rgb]{0.00,0.00,1.00}{Let thy fountains be dispersed abroad, and rivers of waters in the streets.} \\ \hline
%
ASV & Should thy springs be dispersed abroad, And streams of water in the streets? \\ \hline
%
CEB &  Should your fountains flood outside, streams of water in the public squares?\\ \hline
%
ESV & Should your springs be scattered abroad, streams of water in the streets?\\ \hline
%
NASV & Should your springs overflow into the street, Streams of water in the public squares?\\ \hline
%
MEV & Should your fountains be dispersed abroad, streams of water in the streets?\\ \hline
%
NIV & Should your springs overflow in the streets, your streams of water in the public squares? \\ \hline
%
NKJV & Should your fountains be dispersed abroad, Streams of water in the streets?.\\ \hline
%
RSV & Should your springs be scattered abroad, streams of water in the streets?\\ \hline

\multicolumn{2}{p{4.3in}}{{Following the word ``not'' which was inserted by Origen into the verse. The result changes a command into a question. Where did we see that first? The conspiracy results from a misunderstanding of ``well'' in verse 15, and ``fountains'' in verse 16. The word ``well'' refers to the wife, and ``fountains'' to children. The admonition is (1) to have children with your own wife, while not allowing other men to do so, and (2) have children and send them out (like arrows in a quiver - Psalm 127:4). The singular ``fountain,'' in verse 18, is the wife.}} \\ %\hline

%\hline

\end{longtable}
\end{center}

\normalsize 
\end{mdframed}





