\section{Proverb 5 Daily Proverbs}
Compiled from Let God Be True, so this section is not for publication.\footnote{From \href{www.LetGodBeTrue.com}{Let God Be True}}

\subsection{Proverb 5:1}
Father, do you teach your son wisdom and understanding? Do you instruct him about life’s great dangers – including whorish women? Son, do you listen to your father for his counsel? Do you know he was a man before you were born and wants to help you?

Solomon told his son to listen to his instruction. Without fear or false humility, he told his son that he had wisdom and understanding his son did not have. And he told his son to pay attention and humble himself – “bow thine ear” – for his fatherly advice. Though Solomon was a king, this instruction was between a man and his son. Every father who fears God and loves wisdom will appreciate this example. Father, do it!

What is the context here? It is Solomon warning his son about whorish women, as the rest of the chapter shows (Pr 5:1-23). Solomon told his son the plain truth and danger of loose women, and he commended the sexual and family aspects of a loyal wife. Here is practical wisdom for both fathers and sons to resist a very great temptation and to learn how great fathers instruct their sons. Father, will you do it? Son, will you listen?

There is no place for fear in the father-son relationship. Father, do not be afraid to confront your son, tell him his errors, warn him of coming danger, and give him strong advice to avoid trouble. The coming pain and shame for both of you will far outweigh any discomfort you feel now. You know far more than your son, no matter how arrogant or brash he might be. If he disregards your instruction, you will have done what God expects. The LORD will bless you, and your son will recall the advice later. Count on it.

There is no place for false humility in the father-son relationship. An effeminate concept of false humility is common today. Hate it! Reject it! Your son is not your equal – he is an infant in comparison. Do not apologize for, or soft sell, your superior wisdom. It is not humility to apologize or compromise about your wisdom. It is pride to disregard God’s order and neglect your son’s training. Get a hold of this distinction. Read all of Job 32.

If your son is not a God-fearing success, you very likely compromised his training. It is that simple. Training does work (Pr 22:6,15; 29:15). But you must take the time, prepare an agenda, get with your son, and open your mouth to transfer wisdom from your heart to his ears. Playing checkers at night does not cut it, in spite of what effeminate creeps might croon on Christian radio to silly women (II Tim 3:6-7). Get real! A hormonal son facing this generation’s temptations needs a real father with real warnings in real terms.

Father, you are a man. You know your weakness for beautiful women. You know the pain of odious women. You know the trouble of fornication and adultery. You have endured your own temptations, and you have witnessed failures of others. Tell your son. Tell him plainly. Tell him graphically. Solomon did. Anything less is foolish rebellion.

Son, you are a boy. Your father is a man. Listen to him. He was a man before you were born. He fathered you by a woman before you had being. He knows more about women than you will learn in the next 20 years. He has an interest in your long-term future, which you are not presently able to appreciate. Sit down. Be still. Pay attention.

Reader, God in heaven is your Father by creation, and hopefully again by salvation in Christ. He knows more than you will ever learn on any subject by a factor called infinite. Pay attention. Humble yourself. Despise your own thoughts. Love preaching. Consider your pastor’s sentences. Review the sermons. Read your Bible. Save yourself.

\subsection{Proverb 5:2}
Do you know how to save yourself from sexual trouble? Do you know enough to teach sexual safety to others? King Solomon taught his children often about sexual sins, their powerful temptations, and their terrible consequences (Pr 2:16-19; 5:1-23; 6:20-35; 7:1-27; 9:13-18; 22:14; 23:27-28; 30:19-20; 31:3; Eccl 7:26). Pay attention. Beware, reader.

Consider the context. Solomon asked his son to humbly hear his fatherly wisdom and understanding (Pr 5:1), and he called on all his children to receive his instruction and not turn away from it (Pr 5:7). What did he fear so much in their lives? The whorish woman! He knew about her flattering speech (Pr 5:3), the incredibly painful consequences of touching her (Pr 5:4-5), and how can she easily deceive and seduce most men (Pr 5:6).

Fornication and adultery are nearly forgotten sins. They are glamorized and promoted in television, movies, books, magazines, and the Internet. Many of the stars of society – whether political, performing, or athletic stars – live sexually sinful lives that are seen by most as the good life. But the Bible condemns fornication and adultery, and it calls the children of God to sexual holiness (I Cor 6:12-20; 7:1-5; I Thess 4:1-8; Heb 13:4).

Casual sex is only casual in the foolish thoughts of two sinners doing it. The trouble that certainly follows is not casual: it is painful, permanent, and pernicious. Take your pick – you will reap one or more of these results: jealousy, syphilis, divorce, herpes, ruined reputation, gonorrhea, insecurity, HIV, sexual dysfunction, vengeful father or husband, crabs, irate wife, HPV, lost virginity, guilt, unwanted pregnancy, shame, and so forth.

The proverb has a clear lesson with two parts. First, the wise instruction from God and parents is to help save you from sexual sin and pain. Second, the wise instruction from God and parents is to help you save others from sexual sin and pain. Have you learned enough to save yourself? Have you learned enough to save others? Does wisdom guide your life and supply your speech for others? Your future and that of others depend on it.

God has revealed wonderful wisdom to mankind (Deut 29:29). It is your duty to hear and apply those words to your own life (Ps 119:11,128). And it is your duty to hear and apply those words to others’ lives (Pr 22:17-21; Jas 5:19-20). The perpetuity of truth on earth and the prosperity and success of God’s children depend on you having sexual wisdom yourself and also communicating it to children and others to protect and prosper them.

If you are a parent, have you taught and warned your children? Do you monitor their lives sufficiently to keep them from sexual sins in a generation with easy communication and transportation? If you are a pastor, do you preach against it, as Solomon did in his book of Proverbs? If you are an uncle or grandparent, you also can get involved to help those in your family tree avoid sexual sins and the evil consequences that follow them.

For all persons, have you accepted the sexual instruction and warnings of parents? Pastors? Counselors? Scripture? Most do not teach it today, but you can find many and severe warnings in the Bible. Do you know God’s answers to sexual questions? Are you ready to give an answer for your faith (Pr 22:17-21)? Get ready, for you will certainly encounter those that need clear, definitive, and persuasive answers.

\subsection{Proverb 5:3}
Another woman’s flattery can be sweeter than honey and smoother than oil. Like a bee to a flower, foolish men rush in to their own destruction, never discerning the poisonous delicacy until it is too late. It is better to limit your ears to the grunting of a sow than to fall into the treacherous net of a whore’s lying praise and deceitful invitations.

Honeycomb is one of God’s sweetest creations. Pure, golden, sweet honey oozes from its cells. It drips with delightful pleasure for the man wanting a delicious treat. Oil, which smoothes the dryness and texture of any food, and is very pleasant in a dry climate, is also a precious food. Together they represent a smooth, sweet delicacy, which Solomon used to describe the deceitful danger of flattery from a strange woman.

What is a strange woman? Any woman you have not married is a strange woman to you! She is off limits for you; she is foreign to your marriage; she is not your intimate companion; she belongs to someone else; she is an alien to your embrace. You have no right to exchange sweet words with her, for your ears and heart belong to another. Job said, “I made a covenant with mine eyes; why then should I think upon a maid” (Job 31:1). If he could not look at her body, then neither could he listen to her words.

Good fathers will warn their sons of the horrible temptation of loose women, as Solomon does in this chapter. He points out the horrible consequences of sexual sin (Pr 5:3-14), the safety in a good marital relationship (Pr 5:15-19), and the judgment of God on men who compromise in this area of life (Pr 5:20-23). This is not a light matter at all. Many strong men have been wounded and slain by her (Pr 7:26). Christian man, beware!

Solomon was a realistic father. He told the truth plainly. There is no wisdom in telling a son that whorish women are revolting. Paul admitted that sin has pleasure for a season (Heb 11:25). To tell young men otherwise is a lie, and they will be unprepared for the horrible temptation that will come their way some day. Wise fathers will admit the attractive temptation, but they will also describe the horrible consequences.

God made men to desire and seduce women, in order to bring about marriage (Pr 30:19; Gen 34:1-4; Ex 22:16; Deut 21:10-14; 24:5). It is the greatest chase of a man’s life. The adoring response of a woman, declaring her love and submission with intimate and tender words, is one of the most powerful temptations a man will ever face. Her kind and passionate words of affection, respect, and desire are like gasoline to a fire, and any man who denies this is either a liar or has an unnatural sexual problem.

Strange women know these facts well. They use their power of speech to seduce victims. It was this deceptive and delightful speech from other women that Solomon repeatedly warned against (Pr 2:16; 6:24; 7:21; 22:14). David also described the danger of soft and smooth words hiding evil motives (Ps 55:21). Men, get away from her!

Potiphar’s wife tried to seduce Joseph with words, but he defied her (Gen 39:7-12). Samson, on the other hand, fell to Delilah’s obvious and destructive lies, because they were clothed in seductive flattery (Judges 16:15-17). Do not think poorly of Samson, until you have followed Joseph’s example two or three times!

The only safety is distance. “Remove thy way far from her” (Pr 5:8). No man can easily resist the flattery of a woman. It is too pleasant, rewarding, and tantalizing. It is like honeycomb and oil, sweet and smooth. It strokes the soul and stirs the fire of a man’s sexual lusts. The willingness of a woman for intimacy, expressed in alluring and bold language, is like throwing a match in a powder keg. Get away from her!

The chapter began by Solomon asking his son to bow his ear to his father’s instruction (Pr 5:1-2). There is no room for pride or stubbornness here. A strange woman is more than a match for most any man, as sacred and profane history show many times. Every man must bow to the warning and do all he can to avoid her. There is no wisdom or right in social conversation with a woman that attracts you. Get away from her!

This sober warning applies to face-to-face conversations, telephone and cell phone conversations or texting, letters and notes, instant messaging, and emails. Seductive flattery from a woman is too much, even if it is words on a computer monitor. It will lead your heart to plan the sin that will destroy you (James 1:14-15). Get away from her!

Christian woman, there is an indirect lesson here for you. Do you understand the power of flattery and praise in pleasing and winning a man? If you do, then how good are you at using such womanly arts to love your husband? Another woman may very well do it, if you do not keep him entranced with you. He will be responsible for any sin, but you will be an accomplice (I Cor 7:1-5). When was the last time you used honeycomb and oil to seduce your husband? You know from Solomon’s Song that flattery in marriage is good and pleasant. Be a great woman, and use your mouth for righteousness.

The whorish Church of Rome offers her strange religion to men with flattering and beguiling words (Rev 17:1-6). When she speaks of peace, she only desires their souls for herself. The apostle Paul had to oppose such philosophical deception under enticing words at Colosse (Col 2:4,8), and he feared that false teachers would seduce Corinth from her spiritual virginity (II Cor 11:2-4). Get away from her (Rev 18:4)!

Only street prostitutes announce their intentions plainly. Society whores hide behind honorable terms and manners of their deceitful hearts (Pr 7:13-18). In the same way, belly worshippers – carnal Christians – hide their religious hypocrisy under good words and fair speeches (Rom 16:17-18; II Cor 11:13-15; II Tim 3:3-6). Get away from them!

The true servants of Jesus Christ are plain, bold, and direct (II Cor 1:12; 2:17; 3:12; 4:2; Eph 4:14; I Thess 2:3-6). They have sworn allegiance to their Lord, Who is known in heaven and on earth as the Faithful and True Witness (Rev 3:14; 19:11). He will not and cannot lie or flatter (Titus 1:2), and neither will they. They will never sugarcoat the truth, for they are bound in perpetual marriage to the Lord of truth for the cause of truth.

\subsection{Proverb 5:4}
Casual sex, even with a kind, loving, gorgeous, and erotic woman, is bitter and painful. A strange woman, a woman you have not married and have no right to be with, can be a great pleasure in some respects. But it is very short pleasure, and then you discover the horrible consequences of such a heinous sin. Her sweet words and kisses turn bitter like wormwood, and her smooth flattery and lovemaking cut deep like a twoedged sword.

Many men have been destroyed by this deceitful delusion. She looks, sounds, smells, and feels so inviting, and man’s lusts and pride for such a conquest swear it will be very rewarding, but the corrupting and cutting results are hidden from view. Knowing the great danger, King Solomon used this chapter to warn his son about the dire trouble a whore brings into a man’s life and the delightful and protective pleasure of a loving wife.

The proverb completes a sentence started in the previous verse. There the wise Preacher told about a whore’s sweet lips and smooth mouth. See the comments on Proverbs 5:3. The flattery of such a woman is overpowering – her offer of adoration and lovemaking is too much to resist. The proverb here states a strong warning – consider the consequences!

What is the end of a thing? Its reward, results, or consequences (Ps 37:37; 73:17). What is wormwood? An herb known for intense bitterness (Lam 3:15). How bitter? The Greeks called it “undrinkable,” and it is a usual symbol of bitterness. How sharp is a two-edged sword? Twice as sharp as a one-edged sword! It will cut you either way, or both ways.

Consider how a strange woman will be bitter and cutting. Consider it well, young man, for first impressions are deceitfully dangerous. Do not think on her beauty or flirt with her eyes (Pr 6:25). Do not listen to her enticing words (Pr 5:3). They disguise the poison; they cover the blade. She will take you to death and hell, and she will do it painfully.

She will take your time, for lusts are not satisfied with short liaisons or infrequent contact. The guilt will devour your soul day and night, even when not with her. Fear of being caught and exposed will destroy your confidence and conscience. The lie you must live to cover your sin will turn your life into a perpetual drama of deception. The joy you once had in lawful relationships will be stolen from you. How bitter! How cutting!

She deceived others to seduce you, it is only time until she deceives you for another. The betrayal of true love and devotion will leave you vulnerably insecure. The prospect of revenge by her husband or father will chase you even when you are alone in a secluded place. Your reputation will be destroyed and reduced to that of a despised adulterer. She chose to be immoral with you, so you cannot trust her to be morally right in other ways. 

She has been with others, so you must at some point admit you are merely being used by a heartless whore. And since she has been with others, your health may be at risk. Even pagans recognize the short lives of fornicators. She is not cheap, as she expects much in return for her favors, so you are reduced from being a virtuous prince to a begging slave.

And, of course, there is God, death, judgment, and then hell. How bitter! How cutting!

Man, get away from her; do not go near her (Pr 5:8). If you are in such a relationship, break it today, and never think about her or go near her again. Your life depends on it.

\subsection{Proverb 5:5}
Life can be like death, and life can be like hell, as said by metaphor. A whorish woman is a certain way to experience death and hell more than once (Pr 2:18-19; 7:27; 9:18). Sexual sins, craved by the lusts of the eyes and flesh, lead to death and hell. Adultery and fornication will destroy your soul, life, and body, and take you to hell here and hereafter.

Solomon used this chapter to warn his son, and all men, against fornication (Pr 5:1). He offered wisdom, understanding, discretion, and knowledge (Pr 5:1-2). He sought to save men from the fascinating temptation and horrible dangers of the strange woman (Pr 5:3). He described the painful consequences (Pr 5:4-14), the safety in a good marriage (Pr 5:15-20), the omniscience of God (Pr 5:21), and the judgment for sex sins (Pr 5:22-23).

Solomon had more experience with women than any hundred men. He had 700 wives and 300 concubines, and these were high class women (I Kgs 11:3). God gave him exceeding great wisdom and understanding to analyze their danger (I Kgs 4:29). He also knew of his father’s adultery with his mother (II Sam 11:1 – 12:25), his brother Amnon’s incest with his sister (II Sam 13:1-39), his brother Absalom’s folly with his father’s concubines (II Sam 16:21-22), and his brother Adonijah’s obsession with Abishag (I Kgs 2:12-25).

He saw death and hell – a miserable life of pain and trouble – caused by adultery many times. All men die physically, but they can also die to joy and success in this life. Wicked men go to hell after death, but there is another hell in this life – a torturous existence of guilt, misery, defeat, and pain. Scripture commonly uses death and hell in this figurative way (Pr 23:14; Ps 18:5; 86:13; 116:3; Jonah 2:2; Luke 15:24; I Tim 5:6; Jas 5:20).

The “other woman” has ripped many homes apart. Children were confused; long-term marriages were violated; soul pain was multiplied. Men have lost their jobs, their focus, their health, their wealth, their wives, their children, their reputations, their confidence, their peace, and their souls by this heinous sin. Its results are truly described as death and hell. Ask any sober man who has come back from its death (Pr 5:14; Ps 51:8). 

Marc Antony lost Rome, and his life, through love for the seductive Cleopatra. These words – death and hell – perfectly describe Lot, destitute in a cave after impregnating his daughters (Gen 19:30-38), and Samson, blindly grinding for the Philistines (Judges 16:21). Solomon himself knew such women to be more bitter than death (Eccl 7:26).

Yet it is no less true that wicked women take men down to literal death, eternal death, and the lake of fire. How many adulterers have been killed by the jealous spouse of their paramour (Pr 6:34-35)? How many whoremongers have died from sexual diseases (Pr 7:23)? How many have become trapped in sexual addiction (Pr 5:22-23; 6:32; Hos 4:11)?

All whoremongers, unless the Lord Jesus Christ makes an exception by grace, as in the case of David, will be in the lake of fire (Rev 21:8; I Cor 6:9-11). Her beautiful feet and mincing steps are not as attractive now, are they, young man? That sexy walk leads to death and hell! Her path of sweet seduction and loving liaisons goes down, down, down.

No wonder the Lord Jesus taught the plucking out of right eyes and cutting off of right hands, rather than following the steps of this cruel fiend to hell (Matt 5:27-30). Paul said, “Flee youthful lusts” (II Tim 2:22). Get far away from her, now (Pr 5:8). She hides the precipice over hell behind her skirts. Step back! Run away! Never go near her again!

Solomon’s own son did not heed this lifesaving advice and warning against strange women. But why should he have? His father’s example was unlimited love of many women. Rehoboam, following his dad, foolishly lost ten of Israel’s twelve tribes and desired many wives. He had 18 wives and 60 concubines (II Chron 11:21-23).

Fathers! Teach your sons plainly, practically, and pointedly the dangers of whorish women and fornication. This is no small temptation, especially in this ungodly generation with every former limitation being taken out of the way for greedy lasciviousness. Keep your sons far from her. Teach them to avoid her at all costs. There will be death and hell to pay. Her love is a lie. And her reward is bitter and sharp pain (Pr 5:4; 6:28,33; 23:27).

Such a warning applies also to the seductive beauty and charms of the Church of Rome, the great mother whore of John’s vision (Rev 17:1-6). God called for His children to come out of her to avoid her coming judgment (Rev 18:4). Paul feared even those at Corinth might be seduced away from the true Jesus to another (II Cor 11:1-4). Do not look at her enticements; look at her path; it leads down to death and hell (II Thes 2:9-15).

\subsection{Proverb 5:6}
Son, your great enemy is adaptable. She will alter her methods in order to entice and keep you, for she cannot allow you to examine your life or consider the consequences of further dealings with her. Do you know this enemy? Do you know her tactics? Do you know how to save yourself from her? Be forewarned and live, my son (Pr 5:1)!

Solomon used many proverbs to warn men about the strange woman and how she destroys men (Pr 7:26; 23:28). A strange woman is any woman not your wife, but especially a whore; he warned his son carefully about her (Pr 5:1-5). He knew her pain himself, and experience said she was a great threat to destroy young men (Eccl 7:25-29).

He knew many of her enticements. He knew about her flattering words (Pr 6:24), her beauty (Pr 6:25), her eye contact (Pr 6:25), her kisses (Pr 7:13), her pretended character (Pr 7:14), her romantic affection (Pr 7:15), her creative lovemaking (Pr 7:16-18), and her precautions for a safe rendezvous (Pr 7:19-20). But he did not know them all.

Escape from a strange woman requires a man to soberly and unemotionally examine his life and the future results of his actions. Calm reflection will show he is hanging over the pit of hell, with bitter pain and death the certain results. All she can offer is momentary and temporary pleasure. He needs to immediately get as far away from her as possible.

A whore cannot allow you to think soberly, for it would ruin her game, so she uses all her wiles to keep you from realizing your fatal situation. She entices you unrelentingly in various ways, so that you cannot escape her draw. She uses womanly instincts, hellish training, and devilish seduction to keep you off balance and under her spell. She cannot afford to let you consider your ways. She must keep your soul a slave to her desires.

Solomon had learned the hard way that her “heart is snares and nets, and her hands as bands” (Eccl 7:26). Snares and nets are the tools of those who trap unwary animals, birds, or fish. They are disguised from view; they are often moved; and they have attractive bait attached. Whorish women are like beasts of prey, crouching, sneaking, hiding, and then pouncing on their unwary victims to their mortal destruction (Pr 23:27-28; 22:14).

Samson knew Delilah sought to destroy him, by three other events; yet he could not resist her seductive wiles, and so she destroyed a strong man (Jdgs 16:4-21; Pr 7:26). Samson’s ruin is hard to believe, so Solomon gave a clear warning in the proverb here. Tamar knew she must alter her appearance and ways to snare Judah, and they worked (Gen 38:12-19).

Whores can play hard to get – or easy to have. They might be down and dirty – or upright and noble (Pr 7:14). They can offer love – or threaten revenge. They might take you with words – or with touches. They can be mysterious – or bold. They can appear to be slipping away – or promising eternal adoration. They can pretend to be innocent and virtuous – or they can be wildly bold. They will change to chain you to them!

Young man, certain safety is only by staying far from her (Pr 5:8; 4:15; Rom 13:14). Do not deceive yourself about your ability to resist her temptation. To expose yourself to her wiles is more than you can handle. Nearly any whorish woman is too much temptation for nearly any man, so get away, now! Flee fast and far (Gen 39:12; II Tim 2:22)! 

You will never escape an inviting woman unless you ponder the path of life. Do you examine yourself in the light of God’s word, where the path of life is detailed for you (Ps 139:23-24)? Do you prepare for the preaching of God’s word to convict you of any errors in your life? This exercise is essential to your safety and success in life (II Cor 13:5).

Beyond whorish women, the devil is also your enemy. He walks about seeking whom he may devour, just like a wanton woman looking for a victim (I Pet 5:8). Take the whole armor of God and stand against his enticing wiles (Eph 6:10-19). Jesus withstood the devil’s three best efforts to ruin Him by soberly applying God’s word (Matt 4:1-11).

Beyond influencing whorish women in their wicked tactics of seduction, the devil also influences false churches to change their methods to beguile unstable souls (II Pet 2:14). The chief of these churches is that in Rome, which has seduced billions of souls into her religious brothel with many abominable spiritual inventions (Rev 17:1-6).

Jesus was tempted in all points, yet without sin (Heb 2:17-18; 4:15). Being a perfect man, He experienced malicious and weak women pursuing Him (Pr 6:26), but He gloriously resisted them all. Having lived so successfully, He is a most merciful high priest for those facing such temptations. Go to Him for strength, and go to Him for forgiveness.

\subsection{Proverb 5:7}
Sex education is a duty. Good parents do not neglect it due to discomfort or fear. Here are important words of warning from a father to his children. Can you detect his anxious care for them? Can you discern his fear that they might neglect or reject his advice?

What was the grave danger warned about here? Solomon, the loving and wise father, warned his children against fornication, or sexual activity outside a proper Christian marriage (Pr 5:1-23). This chapter and chapter seven are both dedicated to the subject.

Sexual temptation is one of the greatest threats to youth. There are two reasons for this danger – the bodily and social lusts are powerful, and the consequences are terrible. If a father loves his children, he will make every effort to protect them from this temptation and its life-wrecking results. Because of inborn folly in youth, he must warn strongly.

The temptations to sexual sins are very powerful, especially for youth. They have young bodies with the highest levels of sex hormones. They are foolish and cannot see the pain that lies ahead for cheating. They are driven by peer pressure to acquire friends of the opposite sex, which often causes sexual compromise. They often have excessive freedom and numerous carnal activities that lead to frivolity and opportunities for such sins.

The consequences are terrible. Of course, the foolish young person, without proper instruction and warnings, will never appreciate the danger. They cannot rightly dread the shame, the guilt, the loss of virginity, the unwanted pregnancy, the emotional scars, the painful memories, the loss of fellowship with God, the strained relationships, the sexual bondage, the defiled conscience, the sexual diseases, the difficulty of moving forward, the broken trust, the feelings of worthlessness, the impaired intimate ability, and so on.

Today’s profane generation makes it worse. Fornication, or casual sex as they call it, is normal, wonderful, and painless. They promote it by lascivious songs, movies, novels, and magazines. They promote it by immodest clothing and immoral activities. They ridicule purity and virginity. They despise parental authority that limits activities with the opposite sex. They disregard marriage. They provide easy birth control. They pound the senses with a constant barrage of audio and visual images to destroy inhibitions.

Children! You must soberly consider and remember your parents’ warnings. Obey them. Do not think you know better. Do not think your parents are depriving you of pleasure. Do not deceive yourselves. You do not have a clue about the painful consequences listed above. The short-term pleasure of sexual sins never comes close to the long-term pain and trouble that certainly follows. Your parents and pastor are the only ones that truly care for your successful future. If you have any wisdom, hear them and obey them!

Parents! Are you plainly warning your children about the danger? Are you establishing rules from early ages against unchaperoned dating? Do you have strict rules for music, movies, reading, friends, and activities? Do you clearly point out the appeal and power of sexual lusts? Do you graphically identify the painful consequences? If you are not doing these things openly and consistently, you are an accomplice in your children’s future ruin. It does not matter that you do other things, for this may be the greatest battle.

Reader! Are you past youthful lusts? Great! But your Father hates spiritual fornication – religious compromise (Jas 4:4; II Cor 6:14-18). Do you seek and hear preaching of sound doctrine (Luke 8:18; II Tim 4:3-4)? Are you committed to the old paths of apostolic Christianity (Jer 6:16; Jude 1:3)? The danger to play the whore is great, especially with the seduction of carnal Christianity (II Tim 3:1-7). The Lord Jesus Christ will not stand for your infidelity (Rev 2:20-23). Repent! Keep yourself a pure virgin (II Cor 11:1-2)!

\subsection{Proverb 5:8}
How close should you get to a cliff in the dark? How close should you allow a baby to play near a pool? How close should pilots approach other planes? How many drops of arsenic can you allow in a drink? The more dangerous and risky a thing, the farther that wise men will get away from it. The lesson here is simple, but few men will obey it.

The strange woman, a whore or adulteress, is a great danger for men (Pr 5:1-5). Many Christian homes and pulpits are too refined to speak openly about her, and the rest are too carnal and worldly to notice or care. But God’s wisdom is to identify her, condemn her, and give men sober and practical wisdom against her. Any woman that you are not married to is a stranger to you for any intimate pleasure, and you must stay far from her.

Silence on this issue is to commit moral murder and reject God’s word, for fornication is a great threat to men. Few men can resist an attractive woman using words and wiles inviting him to sexual pleasure (Pr 7:13-21). Samson, the strongest man, gave away his great secret to a Philistine whore, whom he knew wanted to destroy him (Pr 7:26).

The proverb has a simple lesson – a wonderful rule from heaven. Do you truly want to walk with God and please Him in all things? Here is wisdom: stay far away from her, and do not even get near her. The cure for sexual temptation is to get far away from it, just as you would get far from a cliff in the dark. Get away! Get far away! Get far away now!

Sexual temptation is too powerful to play with. You must run away from any influence even leading to thoughts of other women. You cannot justify any such thoughts. Get away! You cannot play with this temptation at all. Young man, flee youthful lusts (II Tim 2:22)! If you give this sin any room at all, it will deceive and seduce your soul like no other. If you give her an opening, you will have no strength to resist her words and wiles.

Jesus told men to pluck out their eyes or cut off their hands, when it comes to sexual temptation. He did not mean literal mutilation of your body. He meant giving up anything or everything in your life, no matter how valuable or precious or pleasant, if it tempts you toward the dangerous and damning sin of fornication or adultery (Matt 5:27-30).

Paul told men to make no provision for the flesh, which means avoiding anything that might even lead toward the possibility of sin (Rom 13:13-14). Get away! Get far away! Do not even give this sin a chance to get started. Do not even give it a possibility. Run! How close should you walk or drive near a cliff in the dark? Get away from such danger.

But men play with television, where attractive women with few clothes and no morals create a powerful visual stimulus for sexual thoughts. David, the man after God’s own heart, resolved to set no wicked thing before his eyes (Ps 101:3). Reader, you must treat the television like an armed and dangerous intruder at night. Fear it, and hate it.

Job made a covenant with his eyes to avoid even looking or thinking on any woman other than his wife (Job 31:1). He knew the temptation to think sexually about the maids among his domestic staff. And he begged for painful judgment, if he did (Job 31:9-12). How much television do you think this perfect, God-fearing man would watch in a week?

But men play with pornography, where many techniques are used to create the ultimate visual images. The strange women in the pictures are everything Solomon warned against. To argue that no one gets hurt with pornography is to ignore God, your present or future wife, your own soul, and your children. Porn will destroy you from the inside out.

Men play with swimming pools, swimming beaches, and cruise ships, where women often wear less than underwear, though much prettier than underwear. What is wrong with such recreation or vacations? Proverbs 5:8, that is what! A man can no more justify such situations for himself than lighting his house on fire and trying to sleep through it.

But men play with shopping malls and popular restaurants, where barely-dressed women parade back and forth in alluring attire and provocative friendliness. Such places may be the eyes and hands you must remove from your life! Are you willing to pluck out or cut off these things to avoid the danger? Would Joseph, Job, David, or Jesus eat there?

Men play with office situations, where forward secretaries and/or women colleagues vie for male attention with sensual clothing, flirtatious ways, and flattery. You cannot quit your job because of sexual temptation? Such a move is just too extreme? Is that what you would tell Joseph, who lost his great position and went to prison to avoid his mistress?

Joseph knew what to do. He ran from her presence so hastily that he left a garment in her hands. And he did this knowing the full consequences of his right choice (Gen 39:7-20). He was charged, convicted, and imprisoned for attempted rape, but the Lord put him on the throne of Egypt and blessed his legitimate wife with two of the tribes of Israel.

Men play with temptation of neighbors, church members, and other friends. The choice is simple – either get totally away from the situation or prepare to die. You cannot play with fire and not get burned. You cannot walk the edge of a cliff in the dark and not fall. Even if the act never occurs, the damage to your soul from sexual fantasies will be deep and permanent, without God’s healing grace. The thought of foolishness is sin (Pr 24:9).

If you need to cancel magazine subscriptions or the Internet, cancel them. If you need to change gyms to avoid women in spandex, then change your membership. If you can no longer vacation at the beach, then learn to love the mountains. If you need to ask for a transfer away from your departmental secretary, then ask for it immediately.

Christian man, if you stay far away from her, you will never be with her. Simple, isn’t it? But Satan and this generation are trying to bring her into your home by way of television, the Internet, magazines, smart phones, and other media of our modern society. You must cut off these opportunities. If you cannot control them, then get rid of them altogether.

The choice is yours. If you love the Lord Jesus Christ, then you will flee anything that leads to sin against Him. If you love holiness, then you will hate iniquity and one of the greatest temptations toward it – the strange woman. Hate her! For she will damn your soul for only apparent pleasure, and that only for a few seconds. Hell will last forever!

The Lord Jesus was tempted in all points like you are, yet He never sinned. He knows about sexual temptations, but He calls with authority and affection to avoid her. Let every one that nameth the name of Christ depart from iniquity (II Tim 2:19).

\subsection{Proverb 5:9}
ornication or adultery will destroy you. Whores are cruel. They will steal and destroy your reputation, time, money, family, soul, and health. Pretending love, loyalty, and pleasure, they will use you until you no longer benefit them; then they will dump you.

Solomon warned his son about the strange woman – an adulteress or whore that preys on men (Pr 5:1-7). His advice was simple, “Remove thy way far from her, and come not nigh the door of her house” (Pr 5:8). His remedy was just as simple – have a great relationship with your legitimate wife and have lots of legitimate children (Pr 5:15-23).

Solomon’s son was the kind of man whores pursue (Pr 6:26; 23:27-28). Base or wicked men cannot provide emotional, financial, social, or intellectual satisfaction. Instead, whores seek a man of ability, confidence, intelligence, leadership, and even spirituality. Only a precious life has honor to give away. Solomon’s sons, princes all, were in danger.

When a girl gives her virginity away, or a wife commits adultery, God declares they are humbled – reduced in value and polluted (Gen 34:2; Num 5:11-31; Deut 21:14; 22:24,29; Judges 19:24; Ezek 22:10-11). Therefore, virgins carry a high premium to godly men (Ex 22:17; Lev 21:14; Deut 13:22-31; II Sam 13:18-19; II Cor 11:1-2). If it is true for the woman, it is also true for the man, who is the image and glory of God (I Cor 11:7). When a man falls to a whore, he spoils himself in the sight of God and men (Pr 6:32-33).

Samson gave away his honor as the strongest man to a conniving, conspiring, and seducing Philistine prostitute. Though he knew she was a liar and wanted to destroy him, he could not resist her wiles. He lost his strength, reputation, office, sight, and his life. His story should be read and reread by men to learn the fatal danger of flirting women.

Solomon married a thousand women, and he said of them, “And I find more bitter than death the woman, whose heart is snares and nets, and her hands as bands: whoso pleaseth God shall escape from her; but the sinner shall be taken by her” (Eccl 7:26). It is these kind of women that increase the sinners among even strong men (Pr 7:26; 23:27-28).

Nehemiah wrote, “Did not Solomon king of Israel sin by these things? yet among many nations was there no king like him, who was beloved of his God, and God made him king over all Israel: nevertheless even him did outlandish women cause to sin” (Neh 13:26). If the wise author of Proverbs got into trouble with women, you must surely avoid them.

The danger is real. An attractive woman can flatter and seduce a man into the heinous sin of adultery. Her beauty and offers of intimacy are too powerful (Pr 6:25). Therefore, Solomon warned against her honey-like words (Pr 2:16; 5:3; 6:24), and he illustrated her methods in a lengthy parable (Pr 7:6-23). Safety is by staying far away from her (Pr 5:8).

It is confounding that base women in ability, character, and intelligence can exert power over men who should know better. But their sexual sins have enslaved these men (Pr 5:22), and they give up everything for the fantasy of love from women who are hardly capable of real love. What a cheap exchange! What a wretched future! Stay far away!

A whorish woman is a cruel creature. She is selfish, only feigns affection and loyalty, and has no compassion for her victims (Pr 30:20). She will steal a man’s reputation and money, ruin his marriage, and break his heart without a twinge of conscience. When the prodigal returned home, where were the harlots that eagerly took his money, promising him love by word and deed (Luke 15:30)? As is usually true, they were lying leeches.

Men sacrifice reputations, squander money, waste time, lose jobs, leave their families, destroy their wives, ruin their children, break their parents’ hearts, get judged by their churches, contract sexual diseases, offend God, and are despised by family and friends to pursue the fantasy of love with a whore. Why? Because he did not keep his heart with all diligence and wandered too close to her house (Pr 4:23; 7:8)! Reader, how is your heart?

Young man! Do you hear the sober warning? A sexual thought or step toward a woman you have not married is a thought or step toward death and hell (Pr 2:18; 5:5; 7:27; 9:18). She does not love you, and she will not love you; whores are not capable of true love. Keep your honor. Save your life. Be a hero like Joseph, who was stronger than Samson and David. Be virtuous, and you will be worthy of a virtuous woman (Gen 41:45).

Can an adulterer reclaim his honor? Hardly. Solomon understood this question, because his father was an adulterous murderer, and he did not offer hope for natural men (Pr 6:29-35). Yet, David remained king and prophet, and saints have admired him and his Psalms very highly. There is forgiveness with God and good men (II Sam 12:13; I Cor 6:9-11), but the sin is so addicting and damning that few are ever recovered (Pr 2:18-19; 5:22).

Godly sorrow to true repentance is the only way to recover honor and clear oneself from this terrible sin. Such sorrow and repentance is quite different from the world’s idea of sorrow for getting caught. Paul defined repentance for humbled sinners, and declared that it could altogether clear sinners from guilt and spoiled reputations (II Cor 7:10-11). God’s forgiveness is greater than man’s as the heaven is higher than the earth (Is 55:6-9).

The woman of Samaria and Mary Magdalene were sinners, yet they are two highly esteemed women in the New Testament. Many harlots entered the kingdom of God, for Jesus forgave them (Matt 21:31-32). He came into the world to save sinners (I Tim 1:15). He forgave even the incestuous fornicator at Corinth (II Cor 2:6-11). Let every repentant adulterer or adulteress lift up holy praise from heart and lips to such a gracious God.

\subsection{Proverb 5:10}
Whores are expensive. At best, they want you and your money; at worst, they want your money without you. Even when they do not take your assets or income directly, they are expensive to entertain and support. If you needed another reason to avoid them, here it is.

King Solomon in this proverb gave his son another reason to stay away from the strange woman (Pr 5:3), which is any woman he had not married – whether prostitute, whore, or adulteress. It costs a lot to buy their favors or keep them happy; his assets and income would go to those outside his family, even though they do not provide any lasting benefit.

Here is the wisdom of God! To combat the powerful lusts in a young man and warn him thoroughly of the folly of fornication and adultery, you need to say more than, “Flee fornication,” (I Cor 6:18) and, “Thou shalt not commit adultery” (Ex 20:14). There are many other threats and warnings you can give to help him defeat this powerful lust.

You would hope and wish a young man could be kept sexually pure simply by knowing God has forbidden such sins, like Joseph was with Potiphar’s wife (Gen 39:9). But that is neither realistic nor wise. Many young men are not even born again to have a heart that fears God, and those that are may not be at Joseph’s level of spiritual maturity and zeal.

Most of Proverbs shows the natural consequences of sins. While some of God’s laws are stated and applied, much of the book is observations of pain and suffering caused by sin. Wise parents will take note. They can do a much more thorough job of training their children, if they follow Solomon’s lead and explain all the painful consequences of sin.

Fornication and adultery have painful consequences, no matter what the world may say positively about casual sex. Solomon knew the costs: he had seen them in his father’s life after his adultery with Bathsheba. He warned often against this destroyer of young men (Pr 2:16-19; 5:1-23; 6:23-35; 7:1-27; 9:13-18; 22:14; 23:27-28; Eccl 7:26-29). 

Whores are expensive. If a young man foolishly visits a prostitute, the price is very high for mere seconds of pleasure. She gives no discount for guilt, a grieved conscience, or an STD. His hard-earned money is split between a woman who does not care about him and her pimp, who is the lowest scum of the race. Wake up, young man! Marry a godly woman and make love freely every night with your best friend and perpetual companion.

Whores are expensive. If a young man foolishly takes an adulteress, he must give gifts, since she expects liaisons that flatter her, or he must outdo her husband. Caught in the deceitful trap of imagined and feigned love, the young fool will do all he can to pamper this wicked and unfaithful wife, forgetting that she is taking his living with no commitment, while staying married to another man. Wake up, young man! Marry a godly woman and make love freely every night with your best friend and perpetual companion.

Whores are expensive. Other young men choose the party scene of clubs and bars, where they must maintain a successful image or lose popularity and draw. Expensive cars, clothes, accessories, housing, entertainment, and lifestyle – all for merely an appearance of prosperity and power to seduce women with a soul no deeper than a dollar bill – will eventually put a man in the poor house. Wake up, young man! Marry a godly woman and make love freely every night with your best friend and perpetual companion.

Think, young man! What if your wife, friend, and lover worked with you to build a family estate of children and property, instead of taking your assets and income for the estates of others? What a difference! Solomon wrote you about it in the context (Pr 5:15-19). Think how much faster you would get ahead, how much farther you would get ahead, and how much more secure you would be. Wake up, young man! Marry a godly woman and make love freely every night with your best friend and perpetual companion.

Whores are expensive. Even pornography can rob a man, for whores and publishers, whether magazines or the Internet, want a return for their destructive wickedness. Many visual and mental adulterers have lost money and time, let alone peace, happiness, and sexual function, by funneling money to whores at a distance and/or losing their professional zeal and productivity by the distraction of the addicting and consuming sin.

Build your own estate, young man, rather than another’s. Love the wife you have, and be satisfied with her breasts and ravished by her love (Pr 5:19). Do not even think about dipping into a sexual cistern or well that does not belong to you (Pr 5:16). Have children, legitimate children, and a lot of them, and rejoice with your wife, as your family tree becomes a happy and powerful influence in the earth (Pr 5:17-18; Ps 127:3-5; 128:1-6).

For the man who has already fallen like a fool to a Delilah, save your life, and revive your soul, by running far from her and repenting like David did (II Sam 11:13; Ps 51:1-19; 32:5). There is mercy with the Lord of heaven, even for men foolish and wicked enough to chase whores of any variety. Repent! God is faithful and just to forgive those who truly repent, no matter the greatness of the crime (Pr 28:13; I Jn 1:9; Job 33:27-28).

Let every reader consider the application of this proverb to spiritual adultery. Any man or woman commits spiritual adultery when they befriend false religion or the world. Your affection, attention, time, energy, emotion, and/or money are then given to another god or entity that is an enemy of the true God of heaven and His Son Jesus Christ. The Bible is full of warnings about God’s great jealousy and His severe judgment of those who take what belongs to Him and give it to others (Jas 4:4; Ezek 16:1-59; II Cor 11:1-4; etc.).

\subsection{Proverb 5:11}
Before it kills you, think about what you are doing! Before you are on your deathbed, examine your life. The world glorifies fornication, but they will die and go to hell. Are you wise enough to grasp the importance of questioning your actions before death?

Death sobers sinners, even fornicators. When a man is in health, he justifies his sins. He enjoys their pleasures, sees no evil consequences, and thinks he has much time for amending his ways. But the deathbed brings mourning, when he wishes he could go back and relive his life. Fornicators! Hate your sin now, before it consumes body, then soul!

If a man knew he would die today, fornication would be one of the farthest things from his mind. The brevity of life, finality of death, and reality of eternal judgment would keep his mind from such folly. He would be preparing his heart and soul to depart this world and meet the terrible Judge of all. Fornicators! How do you know you will not die today?

Solomon in this proverb is in the middle of a long sentence describing the consequences of fornication (Pr 5:8-14). His lesson here is the grief that surely comes at the hopeless and painful end of life for sinning against all the instruction and wisdom of his teachers and guides. One of the warnings against sexual sin is to make a person think about dying.

Fornicators can die many ways. There is a long list of venereal or sexually transmitted diseases that ravage and consume human flesh in different ways and places. The painful wails and shrieks of the sufferers are appropriate. But whether death comes directly or indirectly, the consequences are the same. You will grievously wish to relive your life.

What can a young man learn from this proverb? “It is better to go to the house of mourning, than to go to the house of feasting: for that is the end of all men; and the living will lay it to his heart” (Eccl 7:2). Feasting, or partying, is the atmosphere and activity that leads to foolish thoughts and fornication. A funeral, however, will cause young men to consider the grave and righteous living, before it is too late. Where will you go today?

Solomon also wrote, “Remember now thy Creator in the days of thy youth, while the evil days come not, nor the years draw nigh, when thou shalt say, I have no pleasure in them” (Eccl 12:1). Painful days are coming in which you will regret your past. Your future is certain. You are going to die and give an account of your every secret thought and action. Think about it today! Think about it while you have ability and time to change your life.

Solomon, the inspired philosopher and preacher, concluded his analysis of life this way: “Let us hear the conclusion of the whole matter: Fear God, and keep his commandments: for this is the whole duty of man. For God shall bring every work into judgment, with every secret thing, whether it be good, or whether it be evil” (Eccl 12:13-14).

Every young man who repents and puts his trust in the perfect Man Christ Jesus can face that final day with joy and peace in believing, for unspeakable glory waits in heaven. Even if he foolishly sinned by fornication in the past, there is full forgiveness for the truly repentant, for Jesus was tempted in every youthful way, but without sin (Heb 4:14-16).

\subsection{Proverb 5:12}
It will soon be too late! Why continue to rebelliously disregard instruction and reproof? The day is fast approaching when you will hate your rebellion. You will regret the many times you rejected the teaching of parents, pastors, and other counselors. You will moan the words of this proverb in agony, as you find your sin very painful (Ps 36:1-4).

Here is Solomon’s lengthy warning against the strange woman – the whore of casual sex and adultery (Pr 5:3-6). A long sentence covers Proverbs 5:8-13, in which he appealed to his children to avoid her at all costs. He warned them that choosing her now will bring a day in the future when they will deeply grieve for neglecting and rejecting his advice.

When a sinner is cut down and faces destruction and death, he mourns the foolish choices he made in his life (Pr 5:11; 7:23; Deut 32:29; Jer 5:31). There are no unbelievers in hell. Few on their deathbeds! The sinner’s complaint will include remorse for ignoring and despising the faithful and kind warnings of those who tried to save him (Pr 5:12-13).

Young man, your lust for a beautiful woman is a powerful drug (Pr 6:25; 7:26), but its addicting powers and damning results exceed any chemical narcotic (Pr 5:22; 7:27). She will destroy your soul (Pr 6:32). Stay away from her at all costs. Avoid the places where she goes. Avoid anything that makes you think of her. Fill your life with good and wholesome substitutes. Beg God for a wife and overwhelming passion for that wife.

You have been warned. If you slight this warning or continue in a course of sexual lust and sin, you will soon regret your great folly. If you disregard the kind instruction and reproof that could save your life, it will add to your misery when your sin finds you out. Deliver yourself today. Heed the advice. Commit your soul. Run far away from her.

How painfully did Samson recall his parents’ warning (Judges 14:1-3)? As he blindly stumbled in a perpetual circle grinding for the Philistines, how many times did he hear, “Is there never a woman among the daughters of thy brethren, or among all my people, that thou goest to take a wife of the uncircumcised Philistines?” But the fool had let lust destroy learning, and now it was too late. The best he could hope for was suicide.

A rich man woke up in hell. He had daydreamed while the Scriptures were read in the synagogue. He had silenced the cries of his conscience. He had despised the reproofs of parents, scribes, and teachers. Now Abraham spoke, “Son, remember!” It was too late. Oh, the blessed opportunity of instruction and reproof! It was now gone. Hell was so hot. And so long! Why had he not listened? Why? His teachers had warned about this place.

Reader, how is it with you? Have you hated instruction? Despised reproof? Have you thought you know better? Have you dozed during preaching? Despised the preacher? Drowned out his sober warnings and instruction with noise and activity? You sin against kindness from God and men, and you will soon regret your miserable choice. Humble yourself today. Repent of your forwardness. Confess your sin. Choose to obey instead.

The blessed God will not put up with your rebellion forever. He will destroy you suddenly, and there will be no remedy for it (Pr 29:1). You are like a brute beast going to the slaughter (Pr 7:22-23; 10:17; 12:1). God will not convict you forever. Those kind pangs of conscience will go away, and you will be left hardened to rot in your sin.

Jesus Christ walks among His churches (Rev 1:9 – 2:1). He calls the sensible to recall how they have fallen, to repent, and to do the first works (Rev 2:5). If they refuse, He will come quickly and remove a church’s candlestick, or He will kill sinning church members (Rev 2:1-5,20-23), like He did Ananias and Sapphira (Acts 5:1-11). Remember what happened to Corinthian believers (I Cor 11:28-32). Repent! Love instruction and reproof!

\subsection{Proverb 5:13}
Sexual sinners with consciences will cry out, “Why did I not listen to my teachers? Why did I not obey their warnings? Now it is too late! My life is ruined!” These are the painful cries of a fool – who rejected advice about sexual sins. His grief is great, but it is too late.

It does not matter now. He has destroyed his life with whores. He is sick with regret. He wishes he could go back. Why did he hate instruction and despise reproof? Why did he not obey the warnings of his teachers? Note the exclamation point emphasizing his grief.

This chapter is dedicated to warning young men about sexual sins. Solomon warned his son about the sweet-talking strange woman – a whore (Pr 5:1-7). This proverb concludes a long sentence, in which he warned his children to stay far away from her, lest they end up destroying their lives and grieving hopelessly for ignoring his instruction (Pr 5:8-13).

To whom much is given shall much be required (Luke 12:47-48). If pastors, parents, teachers, and friends warned you against sexual sins, then your guilt and punishment will be more severe for sinning against greater knowledge. Consider the grief and guilt that Samson and David felt for their fornication (Judges 16:20-21; Ps 51:8). Is it true, reader, that you have been taught and warned about sexual sins? Then flee for your life!

Sex is a great gift from God, but He limited it to marriage with one spouse (Pr 5:15-19), severely condemning any other intimacy (Pr 5:20-23). Young men burn with sexual desire from God-given testosterone, but they must rule their bodies and limit sexual thoughts or activity to a wife only (Pr 5:19; I Cor 6:13-20; I Thes 4:3-8; Heb 13:4).

The world is obsessed with sex, mostly sinful sex outside of marriage, and even unnatural sex with the same gender. Morality has died. Younger and younger children seek it. Advertisers exploit it. Entertainers promote it. Legislators excuse it. Parents allow it. Pharmacists protect it. Women wear less in public; many are whores – killing inhibitions to accept casual sex. The temptations for men (and women) have never been greater.

But God has spoken. Ignoring Him will ruin your life. He limited sex to one man and one woman in a loving marriage. Intimacy with any other person is not allowed. He taught it at creation (Gen 2:18-25). The patriarchs understood it (Gen 39:7-12). The Law of Moses forbad it (Lev 18:1-30). And the gospel condemns it (Eph 5:3-7; Heb 13:4; Rev 21:8).

Your choices today will affect the rest of your life. You have been warned. If you look at pornography, which is so enticing, available, and “innocent,” you will ruin your life (Pr 5:19-23; 6:25; II Sam 11:2-4; Ps 101:3; Matt 5:28; Rom 6:16). And women must remember that their romance novels are the exact counterpart to nude pictures for men. Both of these hellish inventions excite the lusts for sexual sin and/or destroy contentment.

If you are even slightly tempted with an ungodly relationship, do anything to get away from it. Jesus would tell you to pluck out your right eye or cut off your right hand to avoid it (Matt 5:29-30). Some sins you can fight, but this sin you must flee (II Tim 2:22). If you have a pang of conscience, it is God’s pure mercy to you. Repent, and run, now!

You cannot go back once you sin sexually (Pr 6:32-33; Deut 22:13-21). What restitution will you offer? It will utterly be contemned (Pr 6:34-35; Song 8:6-7). The trap has sprung, and you are caught. Only by great grace and in rare events does God recover sexual sinners (Pr 2:18-19; 5:4-5,11,22-23; 7:26-27; 9:18; 23:27; Eccl 7:26). Do not boast of repenting tomorrow; God may leave you rotting in your sins without ability to repent.

But reader, you cannot limit this proverb to sexual sins. If you have been taught truth or wisdom on any subject, you must esteem that teaching and hate every false way (Ps 119:128). The just God will hold you accountable for sinning presumptuously against the mercy of instruction and warning (Pr 29:1; Num 15:30-31; Luke 12:47-48; Jas 4:17).

A terrible day is coming soon, of which the fear, grief, and horror cannot be described, for you shall give an account of your life to God (Eccl 12:14; Rom 14:10-11; II Cor 5:10-11; Rev 20:11-15). It will be far too late to pay attention to parents or pastors. The books will be opened, your presumptuous sins exposed, and the eternal sentence given.

In that day, you will wish the pastor had preached longer, your parents had been stricter, your pastor had preached harder, and your parents had punished more severely. You will wish you could go back and attend church differently. You will wish you had listened. The change in your perspective will be unbelievably great in only one second of time. 

There is only one way to avoid the horrific predicament of this proverb and that day: obey today what you have been taught. If you daily obey God’s rules and parental and pastoral warnings about sin, you will never experience the hopeless grief of this proverb. But if you arrogantly or rebelliously go ahead in your lusts, you will suffer most terribly.

\subsection{Proverb 5:14}
Are you a hypocrite? God and King Solomon send you a warning to keep you back from this great sin you will have to explain in the Day of Judgment (Eccl 12:13-14). They want you to take good advantage of attending church rather than it becoming an additional sin.

Are you a sexual hypocrite? Do you attend public worship of God while guilty of sexual sins or while allowing sexual fantasies against God’s laws for love, marriage, and sex? Sexual sinners will cry in this life and the next for having committed such a crime.

Hypocrite! Holding sins while pretending to worship. Hypocrite! Privately loving sin and publicly honoring religion. Hypocrite! Singing and praying with lips, while savoring lusts in the heart. Hypocrite! Visiting a holy God with an unholy soul. Hypocrite! Knowing God yet allowing the very sins He hates. The soul pain of a religious fornicator is great!

Scorner! Do you come into the house of God, where He is exalted and praised, and where His laws are read and explained, and then go your way to continue in sexual sins, either of the mind or body? You are a fool and scorner! You mock your Creator and teachers to keep your favorite sexual fantasies or activities. This error will come back to haunt you.

God burned up Nadab and Abihu, though His chosen priests, for using new incense in His worship (Lev 10:1-2). God killed Uzzah for touching the Ark when it shook in transit (II Sam 6:6-7). God gave King Uzziah leprosy in his face for thinking he could perform a priestly function (II Chr 26:16-21). Yet you go into God’s church with secret sexual sins!

Solomon in this chapter warned his son and children of the sin of adultery (Pr 5:1-2,7). By the desirable, and seemingly innocent, enticement of a strange woman (Pr 5:3), a foolish man is brought down to destruction and misery (Pr 5:4-10). When the sin has worked its course, he cannot believe his folly at rejecting the warnings (Pr 5:11-13). In the words before you, he admitted one of the greatest agonies of all – religious hypocrisy!

In the place where men go for comfort and peace – the church, he was tortured with fear, guilt, and shame. Knowing God and His hatred for sin pounding his conscience, he tried to worship, while addicted to his enslaving sin (Pr 5:22). The internal conflict was great – his new man crying against the old – the Spirit convicting against the lustful thoughts of the devil. O wretched man that I am! who shall deliver me from the body of this death?

At times, a sinning saint might wish he had not known the way of truth. Worldlings have no such pains. They sin with abandon. Their conscience is so seared as to be quite silent. The sinning saint knows such deadness is that of an atheist, which he cannot be, no matter how hard he might try. The praise of the righteous, the joy of the faithful, and the reading of Scripture are goading pains. This is the agony of a religious hypocrite!

How did it begin? Playing with a small attractive sin! He allowed exposure to the most alluring temptation for a man – another woman. Her flattery enticed him (Pr 5:3). Then his lusts had the idea that taking her offer of intimacy would bring great pleasure (Jas 1:14-15). But as quickly as the thought of pleasure came, it disappeared just as quickly, after he had damned his soul with the hated act. His conscience was now condemned!

How will he excuse his sin to God? How! He had been privileged in life to have a church where the truth was taught and godly virtue exalted, including sexual purity and integrity. But in spite of the blessed privilege, he had allowed and indulged his pet sexual sins. Now his conscience chases and tortures him – reminding him of countless warnings that he ignored and squandered. Soon he must explain his folly to the dread Judge of all. 

Reader, keep your heart with all diligence (Pr 4:23). God hates hypocrisy. He wants your heart, all of it. He does not care about your lips, if your heart is not all His first. He does not care about your attendance, if you think approvingly about sin. Men who pray in public with eyes full of adultery are marked for the darker regions of hell (II Pet 2:13-19). God seeks the sacrifice of a broken and contrite heart (Ps 51:17). Forsake your sins!

Any lukewarm approach to religion, in public or private, is repulsive to God. He would rather have you cold than lukewarm (Rev 3:14-15). Jesus Christ will spew you out of His mouth for being lukewarm (Rev 3:16). He rebuked Ephesus for having lost their first love (Rev 2:1-5). Hate your lukewarm heart. Hate your self-righteousness, just because you may not be guilty of any sexual sins. Do not despise others while you are a sinner.

Use God’s assemblies to humbly hear His word to condemn the sins in your life (Jas 1:21-25). Go into the house of God to be corrected (Ps 63:1-2; 73:16-22). If your pastor does not condemn sin plainly and powerfully from scripture, you need a new pastor or church (Is 58:1; Jer 23:28-29; Matt 5:19-20; II Tim 4:3-4). Do not drag in. Prepare. Pray. Participate. You will answer to God for every assembly you were privileged to attend.

Self-righteous woman! Have you read this warning with disdain for such foolish men and with joy at the tormenting consequences of their sin? Your wickedness is worse, for you have no conscience, nor is there much hope of your recovery. You have already drowned in the self-flattering deceit and pride of your wicked heart and simple mind. If you can find even a twinge of conscience, confess your arrogant presumption before it is gone.

Monogamous man and loyal woman! Do not think you escape the warning. Hypocrisy can occur with any sin – and all are equal to God. Neglecting or defrauding a spouse is like adultery. You owe your spouse great sex, whenever, however, and wherever they like it (I Cor 7:1-5; Pr 5:19). Backbiting and whispering are variations on murder. James warned that one sin is guilt of all before God (Jas 2:10). Any hypocrisy is a horrible sin.

This proverb has warned young men. You will face this horrible agony and misery of conscience, if you play at all with whorish women, whether by pictures, words, activities, or thoughts. Get away from them! There is no greater temptation than the strange woman, and she will take you all the way down to death and hell (Pr 2:18; 5:5; 7:27; 9:18).

However, God is merciful to the repentant (II Sam 12:13; Matt 21:31-32). At His right hand sits the Lord Jesus Christ, the great and only High Priest of the Christian religion (Heb 3:1; 8:1). He was tempted to sin, including sexual sins, just like other men (Heb 2:17-18; 4:15-16; 5:1-6), but He never sinned. He can and will intercede for you to God.

Hypocrite, have you learned it is hard to repent? Have you learned you cannot break the bondage of sexual addiction (Pr 5:22-23)? Only if God possibly gives you repentance can you be delivered from the devil (II Tim 2:25-26). What can you do? Run from your lusts (Pr 5:8; II Tim 2:22)! Run to Christ (Luke 7:36-50)! Beg God for mercy (Luke 18:9-14)! He can and will forgive you; He can and will help you; He can and will prosper you!

\subsection{Proverb 5:15}
Love your wife! Make love to her only! Make your marriage the hottest in the world! You have no right to any other woman. You should not look at another woman, think about another woman, flirt with another woman, or ever touch another woman sexually.

Go for it! Today! This is God’s plan and will for your life. He wants you to have a great sex life with your great wife. “Let her be as the loving hind and pleasant roe; let her breasts satisfy thee at all times; and be thou ravished always with her love” (Pr 5:19).

The true God knows life can be empty and frustrating, so He gave you one of His greatest gifts of creation: “Live joyfully with the wife whom thou lovest all the days of the life of thy vanity, which he hath given thee under the sun, all the days of thy vanity: for that is thy portion in this life, and in thy labour which thou takest under the sun” (Eccl 9:9).

God created love, sex, and every aspect of the woman you need – your wife. He knows you need and want sex, so He chose the woman that is your wife to practice with until you are both experts. All other women are off limits. “Marriage is honourable in all, and the bed undefiled: but whoremongers and adulterers God will judge” (Heb 13:4). 

The Bible is the perfect love, marriage, and sex manual. God invented sex, so He has perfect knowledge about it. Have you read the Bible and heard it preached to maximize your marriage? If you have read and heard it preached, have you submitted to God’s sovereign, providential choice of your wife and His orders for how you should treat her?

Water, a precious blessing in the dry climate of the Middle East, is here a metaphor for sexual pleasure with a woman. Water satisfies thirst, is necessary for survival, and is very pleasant to a thirsty soul (Pr 25:25). Men drew fresh water from wells; they stored extra water in cisterns. Every man needed his own supply to protect his family and himself.

Men need the water of sexual pleasure, for God put a great desire and need in them for it (Gen 2:18; Deut 21:11; I Cor 7:2,5,9). Any exceptions confirm this well-known rule rather than modify or nullify it (Matt 19:10-12; I Tim 4:3; I Cor 9:5). Men need sex one way or another, but God condemns all other creatures or persons but one – your wife. 

Men also crave food by God’s design, and they desire and enjoy His blessing of it (Ps 104:14-15; Eccl 9:7), but drinking and eating without limitation or discipline are sin and folly (Pr 23:20). Men must hate and reject gluttony and drunkenness, and they should never forget that breaking God’s rules for sexual water is sin and deserves judgment.

A man’s own wife is a great gift from God, for which he should be thankful (Pr 18:22; 19:14). Consider Jacob: “And Jacob served seven years for Rachel; and they seemed unto him but a few days, for the love he had to her” (Gen 29:20). A man may drink deeply of sexual pleasure from his own wife only, not from any other woman, single or married.

No man should even consider the cisterns or wells of others, for the wife God picked for him is more than enough for his needs and happiness. To think upon the cisterns and wells of others is to sin and open the door for great folly (Pr 6:25; Job 31:1; Matt 5:28). Any woman is more than enough for any man, and God chose your wife for just you.

Are you disappointed or frustrated in your marriage? Do you agree with what has been written, but you personally are not experiencing it? Are you thirsty, and your wife seems to have run dry? Or you can see the water, but you seldom or never taste any of it? Is the water of your cistern and well now somewhat lukewarm and putrid, not very appealing?

If the water supply at home is lacking in any way, maybe the pump needs priming. How do you prime a pump to bring forth running water? Treat your wife the way the Creator of love, sex, marriage, and women told you to treat her. It is that simple. God made her as perfect as a rose, but lack of sunshine, rain, soil, and nurture will cause her to close up.

God and Solomon order you to treat her as delicately and tenderly as a pet female deer, to be totally satisfied with her body, and to choose to greatly enjoy her lovemaking. “Let her be as the loving hind and pleasant roe; let her breasts satisfy thee at all times; and be thou ravished always with her love” (Pr 5:19). God knows your wife. Try His way.

Paul told you to love your wife and to cherish and nourish her, like you do your own body (Eph 5:25-29). King Solomon wrote a love song that describes the passion and details of lovers and lovemaking. Have you read the Song of Solomon? Have you tried talking to your wife and treating her the way that this man treated his lover wife?

The strong warning intended by this proverb to limit yourself to your own wife includes use of pornography, which foolishly steals visual pleasure from another woman, causes discontentment with your woman, and hurts your woman’s confidence or desire to ever be the lover you need and want. Your wife will be as hot as you choose or help her to be.

Every Christian woman, every daughter of God, should be careful and faithful in making sure her husband drinks deeply, often, and pleasantly, lest she drive him to wells that are not his, due to bitterness or dryness in his own cistern and well (I Co 7:2-5). Let husbands and wives, with the husband leading the way in love, maximize the pleasure of marriage.

\subsection{Proverb 5:16}
A happy and influential family is a great blessing and goal. It cannot happen by adultery or fornication. Whores cannot help a man build a family tree – they destroy it instead. This corrupt generation rejects family glory and value, but God exalted the family, and so did the noble and accomplished generations of the past. Here is another reason to avoid and despise adultery, casual sex, fornication, same-sex marriages, and other sexual sins.

Fornication and adultery are powerful lusts. A remedy for these temptations is to consider the wonderful blessing of lawful children. The strange woman is a dangerous enemy. Young men must be taught early the glory of a godly family from honorable pleasure with their fruitful wife. The wise Preacher Solomon taught a further lesson against sexual sin. Let every man consider his inspired advice well; let every woman also learn wisdom.

The fifth chapter of Proverbs deals with the strange woman – which is any other woman than your wife. Solomon warned his son against the great temptation she creates (Pr 5:1-3,6-8,20). He described the horrible consequences of sinning with her (Pr 5:4-5,9-14,21-23). Here is the perfect father warning his son about life’s great trap. For the bitterness of wormwood and sharpness of a two-edged sword are very painful metaphors (Pr 5:4).

He raised several practical arguments against sexual sin. He told plainly of the bitter pain, death, and hell it brings (Pr 5:4-5). He warned it will destroy his reputation (Pr 5:9) and devour his living (Pr 5:10). He warned about the pain of a violated conscience (Pr 5:11-14). He commanded loyalty to his lawful wife (Pr 5:15) and fascination with her body and lovemaking (Pr 5:19-20). He warned of God’s judgment for sexual sins (Pr 5:21) and the addicting nature of sexual liberties (Pr 5:22-23). Here is excellent, practical wisdom!

Sexual enjoyment of a wife is one of God’s greatest gifts to man. It is honorable in the sight of God (Heb 13:4); it is to be used frequently and wisely to the complete pleasure of husband and wife (I Cor 7:1-5); and it is a great remedy against wandering lusts (Pr 5:19-20). It is described as drinking waters out of your own cistern and well (Pr 5:15), for men should satisfy their sexual thirst from their own wives only.

But this proverb contains even another argument against the strange woman. A wise man will consider the blessing and glory of a legitimate family, where his influence and pleasure is realized through his children marrying and having more children of their own. These are the fountains and rivers, which a man should desire and enjoy. By lawful offspring, a man can disperse influence and glory abroad in the streets of his city.

Children resulting from sexual sins are not like this. Men are ashamed to admit bastards are theirs. Bastards are a perpetual reminder of shame. Jephthah is a good example (Judges 11:1-2). Even God the Father spoke of them disrespectfully (Heb 12:5-8). While a man may love a child born out of wedlock, the trouble and difficulties are great. The example of Isaac and Ishmael prove this clearly, even though Abram did “marry” Hagar. 

Solomon pursued this practical argument against the strange woman for three verses (Pr 5:16-18). A man should delight in the natural use of his wife; he should desire and enjoy her conception, pregnancy, and childbirth; he should rejoice with his wife being a mother of children. Here is something the strange woman cannot offer – the creation of a legitimate and godly family for the glory of God and the pleasure of two noble parents. 

The fountains of a man are his children, who are able to have more children of their own, bearing his name and character. Jacob, or Israel, was a fountain – he had twelve sons (Deut 33:28)! And Judah was one of his rivers of waters – for he grew into a mighty nation (Is 48:1). The nation of Israel was the fountain from Israel, or Jacob (Ps 68:26). Balaam also used creative metaphors from water for Israel’s great increase (Num 24:7).

A man’s particular fountain is his singular wife, which is stated rather clearly in the context. Read, “Let thy fountain be blessed: and rejoice with the wife of thy youth” (Pr 5:18). And this woman is able to bear him the additional fountains of this proverb, the children who in turn can increase his influence in the city and the whole earth A blessed situation is to have boy and girls playing in the streets, all from your loins (Zech 8:5).

Children, and several of them, are God’s blessing. “Lo, children are an heritage of the LORD: and the fruit of the womb is his reward. As arrows are in the hand of a mighty man; so are children of the youth. Happy is the man that hath his quiver full of them: they shall not be ashamed, but they shall speak with the enemies in the gate” (Ps 127:3-5). The wisdom of how many varies by circumstances, but God allowed many as a general rule.

A fertile wife, like a gushing fountain and fruitful vine, is God’s blessing. “Thy wife shall be as a fruitful vine by the sides of thine house: thy children like olive plants round about thy table. Behold, that thus shall the man be blessed that feareth the LORD. The LORD shall bless thee out of Zion: and thou shalt see the good of Jerusalem all the days of thy life. Yea, thou shalt see thy children’s children, and peace upon Israel” (Ps 128:3-6).

But the world hates God and His perfect plan, so they reject the family to promote sexual sins. They euphemistically call adultery a love affair, sodomy gay, fornication casual sex, and two men in bed a same-sex marriage. The educational and entertainment industries lead this revolt against God’s plan for families and instead glorify base couplings that are below those of animals, which instinctively know mating is for producing offspring.

The rule of wisdom in this proverb is helpful in selecting a spouse. A woman desiring to be a mother will likely find a matching prince; a woman belittling motherhood will get a player. Since she does not want to give her husband children, then she should not be surprised when he is unfaithful, since a family is one of God’s remedies against adultery.

Young men should be taught the glory of a pregnant wife and a nursing mother. Conception should be praised, pregnancy enjoyed, childbirth celebrated, nursing exalted, and children esteemed highly. The present generation is perverse, for pregnancy is generally avoided; it is thought a burden and judgment when it does occur. God forbid such folly! Let the righteous raise the birthrate and increase their numbers in the world.

If a man took this great blessing seriously, he would have no desire or time for a strange woman, who cannot build with him a noble family tree with approval by God and men. The whore must avoid conception or birth to hide her sin, and illegitimate children are a perpetual problem rather than a productive pleasure. Whoredom does not bring increase (Hos 4:10). Let every young man hate the folly that would steal his increase and glory.

God the Father arranged for the Lord Jesus Christ to marry His bride, the church. He has predestinated a godly seed through the union (Rom 8:29). These adopted children are His fountain, His numerous progeny (Heb 2:13). They are for signs and wonders in Israel, to the glory of His grace (Is 8:18). He saw His seed and prolonged His days (Is 53:10). Praise Him, ye children! Give glory to God through Jesus Christ for being in His family! 

It is by the careful cultivation of relationships in the family of God that further increase occurs, by His blessing (Col 2:19; Eph 4:15-16). The children of God, the citizens of Zion, the bride of Christ, should have an influence in the world for the glory of their Husband and Father (Mal 2:15; Matt 5:13-16). Blessed God, help your children fulfill their great privilege as your offspring to disperse your knowledge throughout the earth.

\subsection{Proverb 5:17}
Bastards are a big problem, especially to kings. Solomon warned his son to avoid whores, lest he corrupt his family tree. A wise man delights in a legitimate family of children, but one consequence of sexual sin can be the painful difficulties of bastards or stepchildren.

Sex is mainly for pleasure, though a church in Rome says differently. Sex is also to reproduce, as a husband and wife can create a family by God blessing their lovemaking. Such a marriage is called wedlock, because other spouses or children are locked out!

Solomon warned his son against sexual sins (Pr 5:1-23). Though the world calls it casual sex, God calls it fornication, adultery, and whoredom, and He will judge every violator (Heb 13:4). As part of the lesson, he exhorted his son to maximize his sexual pleasure with his wife only (Pr 5:15,19-20). He then added the precious incentive of having a legitimate family without any confusion of it by other women or children (Pr 5:16-18).

The plural pronoun “them” in the first clause, “Let them be only thine own,” are the fountains and rivers of waters of the previous verse, which are the legitimate children and descendants of a good and noble man (Pr 5:16). The children must all be legitimate by his lawful wife to maximize the pleasure, peace, reputation, and power of a great family.

Godly men, great men, understand the value of a large, happy, and prosperous family (Ps 107:41; 127:3-5; 128:1-6). They know it is one of the great blessings and goals of life. They are not like today’s perverts, who choose other men for their lovers or use women for sex with neither marriage nor children desired. A great family is a valuable motive for godly men to avoid whorish women. Wise parents will include this in their child training.

The “strangers” of the second clause are whores (Pr 23:27). Kings have had mistresses from the beginning, because of their power and wealth. King Solomon warned his son to limit sex to his wife (Pr 5:19-20). He used the euphemism “strange woman” often (Pr 2:16; 5:3,20; 6:24; 7:5; 23:27; Judges 11:1-2). She is a stranger in that she is foreign to his marriage bed; he has no right to intimacy with her, for he promised all lovemaking to his wife. Though he may know her well personally, she is outside his sexual territory.

God allowed polygamy because of the hardness of men’s hearts (Matt 19:8). Though He could easily have created many wives for Adam, He chose one wife for each man for a very good reason (Mal 2:14-15) – godly children. Polygamy corrupts families, as the Old Testament history shows, even though polygamy actually involved legitimate marriages.

Sarah encouraged her husband Abraham to take a second wife named Hagar. But as soon as Hagar conceived, even before any children were born, the envy and trouble had started (Gen 16:1-6). When each wife had birthed a son for Abraham, the rivalry came out in the open, and Abraham’s polygamous family was ripped apart permanently (Gen 21:1-11).

David’s sons fought among themselves, because David had polluted his family tree by polygamy (I Chron 3:1-9). Solomon had witnessed this deadly conflict personally, when Absalom killed Amnon for molesting his half-sister (II Sam 13:1-39). And he had experienced it himself, when Adonijah tried to steal his throne (I Kgs 1:1-53; 2:12-25).

Adultery is worse than polygamy, for there is no commitment or marriage at all. Children conceived by adultery do not have two loving parents, for one parent is missing from the child’s home, and the stepparent may not have strong affection for the stepchild. It is such troubles of a mistress conceiving that Solomon warned his son and you against.

But how much worse are children stolen from opposite-sex intercourse to provide children for two men or two women in same-sex sham marriages? Even nature itself condemns such unions and denies them ability to reproduce (Rom 1:24-27,31; I Cor 6:9; I Tim 1:10; II Tim 3:3), yet they want the result of opposite-sex love. Solomon never saw such perversity. The proverb applies even more powerfully against such inventions, for it declares, “Let [your children] be only thine own, and not strangers’ with thee” (Pr 5:17).

The living and true God, Who limited marriage and sex to one man and one woman, also condemned most divorces – the kind that occur in about 50% of first marriages in America. He hates such divorces (Mal 2:16), and He declared that they are merely a legal fraud to whitewash the terrible sin of adultery (Matt 5:31-32; 19:3-9). These divorces also violate the proverb, for they break up marriages and confuse families with stepchildren. 

The children of God should marry godly and virtuous spouses of the opposite sex for life and build great families with legitimate and loved children, whom they train to love godliness and hate this world’s abominations. May such children see the glory, feel the joy, and know the profit of a godly and real family. May they learn to hate fornication, adultery, sodomy, and unscriptural divorce as enemies of the family. May the fountains and rivers of such godly children increase more and more (Pr 5:15-18; Ps 144:11-15).

The God of heaven has His family of children by glorious wedlock to the Lord Jesus Christ (Eph 3:14-15; 5:25-27; Heb 2:10-13). All others outside the electing grace of God are bastards, and He denies them His love and chastening (Heb 12:5-8; Eph 1:3-6; Rom 8:28-33; 9:21-24). Jesus Christ guaranteed eternal life to every one of these children (Jn 6:38-39; 10:27-28; 17:1-4), and they shall spend eternity rejoicing in a new heaven and earth with Him and their Father (Ps 16:11; 36:8; John 14:1-3; Rom 8:17-23; Eph 2:4-7).

\subsection{Proverb 5:18}
Married men have a fountain. They should thank God for it, protect it, honor it, and use it. It is the wife of their youth that gives birth to their children. A wife is like a fountain in that she sends forth children to spread a man’s influence. A wise man highly values this advantage of a lawful wife over a whore. He should enthusiastically enjoy life with her.

Fathering children with a wife is a glorious and wonderful thing. Solomon warned his son against adultery by praising the privilege and pleasure of a legitimate family (Pr 5:15-18). The fountain is a man’s generative power with a woman, which he restricted to only his son’s wife. And he exalted a happy family as a blessing and delight worthy of rejoicing.

Adultery destroys this good thing. Whores cannot give it. They avoid conception, lest they be discovered. When a child is born out of wedlock, it causes more problems than blessings. And adultery crushes the heart of your wife. It is only legitimate children from a monogamous marriage that bring blessing and joy to two loving parents. Solomon condemned adultery by promoting a legitimate family.

Boys should be taught early that marrying young – the wife of thy youth – and having a happy family with children are great sexual and social goals. Girls should believe being a wife and mother are their most fulfilling and noble roles. Childbirth, a nursing mother, and happy children are blessings (Pr 17:6; Job 21:11; 42:16; Ps 107:41; 127:3-5; 128:1-6). They are also great deterrents to the short, deadly pleasure of fornication or adultery.

This perverse generation despises and ridicules the large families of several generations ago. Family size in America has fallen from an average of 7.0 children in 1800 to 3.5 in 1900 to 1.6 in 2000. This collapse is partly due to change from an agrarian/rural society to a service/urban one, but it also reflects the selfish and whorish lifestyles of most adults.

Defying the wisdom of a happy family, this lascivious generation promotes a lifestyle of casual sex, multiple partners, commitment-free love, professional women, marriage without children, and spousal independence. The family unit God ordained and blessed, which was for man’s pleasure, prosperity, and protection, has become an item of scorn.

Divorce, single parenting, cohabitation, and same-sex marriages are in. Many children are raised in one-parent homes. When there are two parents, the one child they have is spoiled beyond description. These children’s dysfunctional lives condemn the trends of this evil generation by the obvious results. God’s wisdom of the family is never outdated.

The righteous, who fear God and trust His Word, must restore the glory and prosperity of the family – a man and wife committed for life, loving their several or more children, and rejoicing in their family extension by grandchildren. You can do this by building your own marriage and family to be an example of blessing and pleasure, by condemning and avoiding all forms of casual sex outside marriage, by teaching your children these things, and by reproving and ridiculing all societal trends against God’s family ordinances.

\subsection{Proverb 5:19}
Contentment with your wife is crucial to a happy marriage. Solomon warned his son to make three important choices – cherish his wife tenderly as a delicate object of affection, appreciate her body and sexuality only, and let her affection and devotion consume him. This inspired proverb contains some of the most necessary marital advice for husbands. A man can profit very much by learning and doing this wisdom and that in Colossians 3:19.

If a man lets bitterness harden him toward his wife, desires the bodies of other women, or despises his wife’s efforts to be his lover, he will destroy his marriage, his sexuality, and his soul. Discontentment, especially in marriage, has terrible consequences. Beware! The blessed God, who knows more about marital love and pleasure than all men combined, gave precious instruction to those that will humble themselves, hear it, and apply it.

A bitter man is horribly unhappy, constantly frustrated, and sexually impaired. He will hurt and neglect his wife, until she cannot love him, and the marriage becomes a sham. He will be vulnerable to strange women, whose breasts cannot satisfy, no matter how beautiful, for they belong to cruel women God has condemned (Pr 5:9). Solomon, the loving and wise father, soberly warned his son against the dangers of discontentment.

A hind is a female deer, usually of the red deer. A roe is a small species of deer of Europe and Asia. Together the words describe a small, delicate, graceful, and tender female deer. These deer were caught, tamed, and enjoyed as pets by kings and others in Solomon’s time. Their refined, gentle natures were the delight of both men and women. And the wise man will refer to them again when describing his wife’s beauty (Song 4:5; 7:3).

Coupled with Solomon’s adjectives of loving and pleasant, you see a wonderful word picture of a delightful and prized woman worthy of love and protection. Lady Wisdom calls all men to view their wives this way and treat them accordingly. A husband should carefully treat his wife with gentle affection and patient tenderness, just as if he were caring for a loving and pleasant female deer. Paul confirmed this rule in the N.T., where he commanded men to cherish – treat with special care – their wives (Eph 5:28-29).

God formed Eve’s breasts and all other details of her body that were so marvelous to Adam’s eyes and touch. And nothing has changed – men still marvel at a woman’s body. God made men to be attracted by a woman’s body, and within marriage, it keeps the man coming back for more. Her body and lovemaking should be a constant source of delight, and a wise woman will know and exploit this for his and her happiness and pleasure.

The frequency, creativity, passion, and variety of sexual lovemaking are not suggestions, possibilities, or preferences; they are commandments (I Cor 7:1-5). It is a horrible act of covenant breaking, defrauding, and hatred to shortchange your spouse in any aspect of this dutiful privilege and honorable pleasure. God will judge all selfish or stingy spouses, for even the New Testament warns that God expects both spouses to be fully satisfied.

While breasts are mentioned by name in this proverb, they are synecdoche for her whole body and sexual pleasure. But the perpetual importance of breasts for attraction and lovemaking is forcefully brought to our attention by Solomon’s plain language. Nothing has changed; breasts are still beautiful and important in the appearance and performance of a woman (Song 4:5; 7:1-10; Ezek 16:7; 23:3,8; Hos 2:2). Women in Solomon’s day were as concerned about their breasts as much as women are today (Song 1:13; 8:8-10).

But this wicked society tries to expose breasts to public view, which Christians must fight with all their power. Immodest clothes that emphasize, enhance, or expose the size or shape of breasts must be rejected. And this rule of holiness and godliness must apply to the other parts of a woman’s body that also attract the attention and desire of men. The present state of public undress makes it hard for men to be satisfied husbands at home for great marriages. God hates female immodesty (Is 3:16-24; I Tim 2:9-10; I Pet 3:3-4).

This proverb binds every man to be content and satisfied with his wife’s breasts, the rest of her body, and her lovemaking. It is a choice. Every husband must choose to focus on what he has, rather than bemoan his fate for what he does not have. It is a command. The proverb here is not a suggestion, and every man can do it, if he will obey the Lord. Of course, if his wife is depriving him of sexual pleasure or has let her appearance decline, it is his duty and right to correct the situation by wise and loving management of the marriage (Gen 3:16; I Cor 7:3-5; 11:9; 14:34-35; Eph 5:22-24; Tit 2:4-5).

The infinite Creator, who designed love, sex, and every detail of both bodies, limited man sexually to one woman, and her only in marriage. To keep monogamy from becoming monotony, He gave these rules of marital advice for men. If a man keeps them, he will realize the glorious happiness and fulfillment the LORD intended in creating Eve for Adam (Gen 2:18; I Cor 11:9). He will fervently say with His Creator, “It is very good!” Hollywood and Playboy are abject losers when it comes to love and sex, as their lives, divorces, dysfunction, and unhappiness prove. Ultimate love is for obedient Christians.

To ravish a thing is to seize and carry it away by violent force, as plundering spoil from an enemy. To ravish a person is to overpower them and take them away, as in sweeping them off their feet! Wise men choose to be overcome by their wives’ affection, devotion, and lovemaking. The rule here is not ravishing your wife, but rather being ravished by your wife. But since she is a responder, it includes your love of her. It is a choice to be spoiled by her affection, so the strange woman has no means of approach or seduction.

With a little knowledge and experience, any woman has more ability and capacity for sexual pleasure than any man, which means your wife is more than you can handle, if you love her properly. The true God does all things well, including this often overlooked fact about men and women. Though she was created for the man (Gen 2:18; I Cor 11:9), his greatest pleasure comes through emphasizing her pleasure (Song 2:6-7; 8:3-4). Help your wife to be the best, and rejoice in her love without regard to women outside your home.

It should be obvious that pornography is totally condemned by this proverb. Being satisfied with your wife’s breasts and body at all times does not allow even brief looks at the breasts or bodies of other women. In order for a man to keep this proverb, he must also be exceedingly careful with television and magazines and avoid public beaches or pools, shopping malls in summertime, coed gyms, and offices with immodest women. If such rules are too hard for you, then do not complain about your unhappy marriage.

Women can also destroy their marriages, sexuality, and souls, when they wish their husbands were different. A woman must not desire the communication, emotion, intelligence, leadership, personality, spirituality, success, or any other trait she sees in other men. She must avoid thinking on these things. Such thoughts are the same as her husband wishing for the face, breasts, waist, or legs of another woman. She must choose to be content with the man she has married, just as she wants him to be content with her.

Romance novels, describing fantasy men, passionate seduction, and unrealistic emotions in idealized settings, are a woman’s pornography. Reading such fairy tales will lead a woman to be unhappy with her husband, for no man will ever measure up to such ridiculous ideas. Reading and dreaming about them is self-destructive and insanity. It is the same sin as men making their wives physically inferior by viewing pornography.

Contentment in marriage is a learned choice, as it is in other things (Phil 4:11). It is an attitude, not better circumstances (Phil 4:12). There is no perfect spouse, and there never will be. Neither is there a perfect job, business, house, car, or vacation. So the key to success in marriage is to be content – totally satisfied, even ravished – by the one you have married. Do not wait for the one you have to change, or wish you were with another. Great gain is godliness with contentment (I Tim 6:6), and it certainly applies to marriage.

Husband, you have just read marital advice worth a fortune from the wisest man who ever lived, who had 1000 wives (I Kgs 11:3). Marital happiness, fulfilling love, and satisfying sex are dependent on you. The advice is simple: consider and treat her delicately with tender affection, choose to be always satisfied with her body and lovemaking, and focus on her devotion, love, and loyalty. You can be immensely happy!

Do not let another woman come near in these areas. Solomon’s words are very valuable for promoting a great marriage, but they were given to ward off the temptations of the strange woman. By exalting your wife to her rightful place, you will be protected from the vexing draw of other women, who seek to tantalize, frustrate, and destroy you. There is no true peace, pleasure, or prosperity for the adulterer. Therefore, the word of God is simple – do not look or think about another woman (Pr 6:25; Job 31:1; Matt 5:28).

Wife, if your husband should be satisfied, even ravished, with you in the three ways described for a great marriage, what are you doing to help him? Are you a delicate and gracious creature deserving affection, like a loving hind and pleasant roe? Do you diet and exercise to maintain the resemblance of a woman’s hourglass body? Do you use it boldly for his regular pleasure? Do you lavish affection, devotion, lovemaking, and praise on him? Do you do it aggressively, with passion? Do you over- or under-whelm him?

The Lord’s soon return will bring a marriage where the Bridegroom and bride are perfect. There will be no longing for another, for He will be gloriously magnificent to an infinite degree beyond anything you can or will imagine, and He will have made you perfectly beautiful for Him (Ps 45:10-15; Eph 5:25-27; Rev 19:7-8). Come quickly, Lord Jesus!

\subsection{Proverb 5:20}
Why do you even think about it? A beautiful woman offering sexual intimacy is a great temptation. Her flattering affection and intriguing body overwhelm most men. But the horrible consequences crush the pleasure! Why do you think about it? It will ruin you.

Good fathers warn their sons plainly about whores, as Solomon did often (Pr 2:16-19; 5:1-23; 6:20-35; 7:1-27; 9:13-18; 22:14; 23:26-28,33; Eccl 7:26). They are one of the greatest dangers for young men, especially for princes. Do you know their great danger?

No matter how desirable she appears, no matter how flatteringly she speaks, and no matter how certain you will not be caught, fornication with a strange woman is a foolish and horrible crime. The consequences are more painful than death, more permanent than life, deep as hell, and hardly any are recovered to return to the land of the living.

A strange woman is any woman you have not married. Since you have not married her, you have no right to touch her. Your wife is your companion for life, and any other woman is a stranger. After giving negative (Pr 5:1-14) and then positive (Pr 5:15-19) reasons against the strange woman, Solomon asked why his son would even consider her.

The cure for the strange woman is a great marriage with your wife (Pr 5:19; I Cor 7:1-5; Heb 13:4). By exalting your wife in your mind, by choosing to be satisfied with her body, and by choosing to be overwhelmed with her love, there is no room for another woman. You cannot allow any bitterness or faults to spoil your affection for your wife (Col 3:19).

The consequences of sex with a strange woman are horrific. Solomon described them as death and hell (Pr 2:18; 5:5; 7:27; 9:18). A life of death and hell, and hell after death! Few ever recover (Pr 2:19). Young man, forget the beautiful face and body. Ignore the flattering words. Reject any invitation. Do not let her touch or kiss you. Run far away.

You will break your wife’s heart, which God sees (Mal 2:13). You will lose your sure companion (Mal 2:14). You will lose your money (Pr 5:10) and your reputation (Pr 5:9). You will have a husband or father hating you (Pr 6:34-35). No one will understand why you did it (Pr 6:30-33). God will see it and punish you (Pr 5:21; 15:3; Heb 13:4).

You will create a binding sexual addiction to destroy you (Pr 5:22-23; 23:27). Your conscience will punish you with pain (Pr 5:11-14). You will lose a prosperous family of legitimate children (Pr 5:15-18). The pleasure is for a moment; the pain is forever (Pr 9:17-18). You will give occasion for God’s enemies to blaspheme (II Sam 12:14). Your prayers will not be heard (Ps 66:18), and you will face the lake of fire (Rev 21:8).

God in great mercy made Eve for Adam, and He ordained marriage for you to be sexually fulfilled with a devoted and helpful wife (I Cor 7:1-5; Heb 13:4). He invented love, marriage, and sex. Why would you ever think of disregarding the Creator’s rules for His invention? Humble yourself before His infinite wisdom and maximize your marriage.

If you played the fool and embraced the bosom of a stranger, there is hope, but it requires godly sorrow and repentance that most cannot understand or produce (II Cor 7:11). David was God’s favorite before and after his aggravated adultery and murder, because he totally humbled himself before God and confessed his heinous crime correctly (Job 33:27-28; II Sam 12:13; Ps 51:1-19). God will not despise your broken and contrite heart.

\subsection{Proverb 5:21}
God’s eyes are everywhere, watching all actions (Pr 15:3; Ps 11:4; 139:1-12). Every thought, word, and deed is naked and exposed to the all-seeing eyes of the omniscient God. He sees and considers all your doings, so you should fear Him and hate sin. You should order your life, both in private and public, to please Him in all ways, at all times.

But the warning is considerably more pointed – you should fear God seeing your sexual sins. Here the wise father Solomon warned his son about the strange woman and taught the cure for her. She is bitter, painful, and takes men down to death and hell (Pr 5:4-5); she destroys lives (Pr 5:9-11); she brings bondage (Pr 5:22-23). Inspired safety is to be totally in love with your wife and content with her body and lovemaking (Pr 5:15-19).

Sexual sins are done in secret. Adulterers meet in private or dark places (Pr 7:9; Job 24:15). Pornography addicts hide materials or media and make excuses for being alone (Ezek 16:17; 23:14-16). The fantasizing person believes thoughts, imaginations, and desires are totally hidden from everyone (Pr 24:9; Ps 10:11; Ezek 8:12). The defrauding wife thinks she is justified and safe avoiding sex with her husband (I Cor 7:3-5).

But the Lord God sees and knows all such deeds and thoughts. Nothing is hid from His eyes. Darkness is as noonday to Him. He fills heaven and earth; where will you hide? He discerns the very thoughts and intents of your heart. He knows and considers it all. And He hates and judges sexual sins (Ex 20:14; Lev 18:6-25; 20:10-21; Matt 5:28; Heb 13:4). It means nothing at all to Him that you have hid your sexual crimes from other men.

The father asked his son, “Why love or touch a strange woman?” (Pr 5:20). She brings terrible pain and destruction (Pr 5:4-11); she causes bondage and death (Pr 5:22-23). But he especially wanted his son to know that God sees every sexual activity and thought, and He considers and weighs them all. The Lord of heaven will give blessings to the sexually pure and faithful; He will send painful, punishing judgment upon the filthy and foolish.

People go to great lengths hiding sexual sins from others for guilt, fear, and shame, but the only Judge they should fear sees every deed and the thoughts behind them clearly. Why fear others knowing your sexual sins, when the holy God is a much greater Judge? This proves the deceitfulness and insanity of the depraved and willful human heart, using fig leaves to cover nakedness, when only the blood of an innocent life can truly protect. 

The LORD sees and knows your sexual secrets, and you had better keep your sexual life pure and holy, for this is the will of God (I Thess 4:1-8). He watches all your sexual activities, thoughts, and words. He will surely bless the righteous and judge the wicked. You cannot hide or escape His penetrating view, and you cannot avoid the consequences.

The Lord Jesus Christ was tempted in all points as you are, but He remained faithful to His God, even better than Joseph. Single, followed by many devoted women, and more desirable and affectionate than any man, He lived with absolute fidelity and purity to God His Father. Confess and repudiate your sexual sins already committed to Him, and then follow His holy example today. He will give you increasing strength as you obey Him.

\subsection{Proverb 5:21}
Solomon warned about sexual addiction 3000 years ago. Psychologists have only recently stumbled on it. Having warned his son about sexual sins and God’s punishment of them (Pr 5:1-21), Solomon added the sober warning of being bound by those sins for total destruction (Pr 5:22-23). Pleasures of sexual sins for a season may imprison you for life.

The context is plain and simple – sexual intimacy with anyone but your lawful spouse (Pr 5:1-21). The man of this proverb is a fool that rejected the warnings and proceeded to sin sexually with a woman. His sexual sins will take hold of his body and spirit, and he will be held in the chain-like shackles of them. They will capture and hold his very soul.

Sexual sins captivate a person’s soul more than others. Alcohol may lead to drunkenness and a chemical addiction, but fornication can lead to obsession with immoral thoughts and activity. Men who sin sexually are seldom recovered (Pr 2:18-19; 5:5-13; 6:26-35; 7:22-27; 9:17-18). Only God’s glorious grace can deliver a man from this bondage.

Sexual sins are also addictive in how they demand more and more stimulus to provide the original thrill. A voyeur seldom remains a voyeur. Few men are content with moderate pornography; they progressively seek more extreme and graphic images in order to feel the same level of sexual and sinful thrill of their first experiences with it.

Pornography itself is a case study in this progressive degeneration. What was called pornography 40-60 years ago is vastly different from pornography today. The difference is remarkable! Fools who began with female nudity in their teens must explore sodomy, bestiality, and pedophilia in their forties to get the same thrill. And instead of improving marital pleasure, as their hearts lie to them, it destroys marital ability and satisfaction.

Young man! Older man! This proverb is as true as gravity. If you play with fantasies, pornography, fornication, or sodomy, you will destroy yourself. Your own sins will capture and imprison your soul. You will be unable to free yourself. You will never again love God, your wife, or godly living without a miracle from heaven. And God has not promised you or any other fornicator such a gracious and undeserved deliverance.

Consider Samson. He had good parents, was a Nazarite for life, was fearless of other men, and judged Israel twenty years. Samson lusted after Philistine women for their looks (Judges 14:1-3; 16:1), until he was helpless with Delilah. In spite of obvious intentions to destroy him, she was his omnipotent master (Judges 16:4-21). Why did he not catch on? Was he insane? He was a slave to sexual obsession. He ended up blind and a suicide.

Consider Amnon. He had good parents, was the firstborn son of King David, had the true religion of Jehovah, and could have had any eligible woman in Israel. But he sexually fantasized about his sister Tamar until he was sick with obsession for her. His addiction to this fantasy led to cruelly raping her, consequently hating her, and justifiably being killed by her brother Absalom (II Sam 13:1-39). He was a bond slave to his fantasies.

Consider Solomon. He wrote Proverbs. He wrote this proverb. But women destroyed his life (I Kgs 11:4-13). How did it happen? He first married out of the Lord, against God’s command (Deut 7:1-6; I Kgs 3:1). He then became polygamous, also against God’s command (Deut 17:17; I Kings 11:1-3). His love of female variety became his sexual obsession, until he had 1000 women, exotic ones, which destroyed his life (Eccl 7:26-29).

Man! If you play with fantasies, pornography, fornication, or friendship with a woman not wholly the Lord’s, you are a flattering fool. You are a fool, because you have rejected God’s warnings. You are a flattering fool, because you have lied to yourself that you can get away with it. You will soon hate your precious sin, which will destroy you (Ps 36:2).

You are a fool to think you can escape your sin and its punishment by repenting later, for you are in perfect bondage to your lusts; you will neither be able nor willing to set yourself free. If you do escape sexual diseases, the rage of a jealous husband, or the sentence of the judge, you will be infallibly overtaken by the righteous judgment of God.

There is no greater bondage than a child of God who cannot repent and find joy and peace with his Lord. Do you hear it, sinner? You cannot repent! Why can you not repent? Because you have become a slave to your lusts, and your own heart is in the death throes of sinful thoughts and actions. Every time you allow a sinful thought or action in your life, you twist another sinful strand into the cords that will bind you in your sexual sins.

If you are playing with fantasies, pornography, or a sinful relationship, get away now. Flee youthful lusts, Paul would say (II Tim 2:22). Do not go near any place or thing that tempts you to sin sexually (Pr 4:15; 5:8; Ps 101:3; Rom 13:11). Pluck out your right eye or cut off your right hand rather than play with sexual sin, Jesus would say (Mat 5:28-30).

If you are addicted to a sexual sin, your case is not hopeless, but you will never free yourself by your means or strength. You must cut off the sin violently, totally, now! Repent with these words (Job 33:27-28). Beg God’s power in Jesus’ name to deliver you from sin, sex, and Satan. Humble yourself to a spouse, a parent, or a pastor with every condemning detail. Pursue God’s worship in public and private with your whole heart.

Nothing is too hard for the Lord Christ! You can read that harlots went into the kingdom of God before religious Pharisees (Matt 21:31). Paul told of many sexual sinners at Corinth, “And such were some of you: but ye are washed, but ye are sanctified, but ye are justified in the name of the Lord Jesus, and by the Spirit of our God” (I Cor 6:11).

\subsection{Proverb 5:22}
Solomon warned about sexual addiction 3000 years ago. Psychologists have only recently stumbled on it. Having warned his son about sexual sins and God’s punishment of them (Pr 5:1-21), Solomon added the sober warning of being bound by those sins for total destruction (Pr 5:22-23). Pleasures of sexual sins for a season may imprison you for life.

The context is plain and simple – sexual intimacy with anyone but your lawful spouse (Pr 5:1-21). The man of this proverb is a fool that rejected the warnings and proceeded to sin sexually with a woman. His sexual sins will take hold of his body and spirit, and he will be held in the chain-like shackles of them. They will capture and hold his very soul.

Sexual sins captivate a person’s soul more than others. Alcohol may lead to drunkenness and a chemical addiction, but fornication can lead to obsession with immoral thoughts and activity. Men who sin sexually are seldom recovered (Pr 2:18-19; 5:5-13; 6:26-35; 7:22-27; 9:17-18). Only God’s glorious grace can deliver a man from this bondage.

Sexual sins are also addictive in how they demand more and more stimulus to provide the original thrill. A voyeur seldom remains a voyeur. Few men are content with moderate pornography; they progressively seek more extreme and graphic images in order to feel the same level of sexual and sinful thrill of their first experiences with it.

Pornography itself is a case study in this progressive degeneration. What was called pornography 40-60 years ago is vastly different from pornography today. The difference is remarkable! Fools who began with female nudity in their teens must explore sodomy, bestiality, and pedophilia in their forties to get the same thrill. And instead of improving marital pleasure, as their hearts lie to them, it destroys marital ability and satisfaction.

Young man! Older man! This proverb is as true as gravity. If you play with fantasies, pornography, fornication, or sodomy, you will destroy yourself. Your own sins will capture and imprison your soul. You will be unable to free yourself. You will never again love God, your wife, or godly living without a miracle from heaven. And God has not promised you or any other fornicator such a gracious and undeserved deliverance.

Consider Samson. He had good parents, was a Nazarite for life, was fearless of other men, and judged Israel twenty years. Samson lusted after Philistine women for their looks (Judges 14:1-3; 16:1), until he was helpless with Delilah. In spite of obvious intentions to destroy him, she was his omnipotent master (Judges 16:4-21). Why did he not catch on? Was he insane? He was a slave to sexual obsession. He ended up blind and a suicide.

Consider Amnon. He had good parents, was the firstborn son of King David, had the true religion of Jehovah, and could have had any eligible woman in Israel. But he sexually fantasized about his sister Tamar until he was sick with obsession for her. His addiction to this fantasy led to cruelly raping her, consequently hating her, and justifiably being killed by her brother Absalom (II Sam 13:1-39). He was a bond slave to his fantasies.

Consider Solomon. He wrote Proverbs. He wrote this proverb. But women destroyed his life (I Kgs 11:4-13). How did it happen? He first married out of the Lord, against God’s command (Deut 7:1-6; I Kgs 3:1). He then became polygamous, also against God’s command (Deut 17:17; I Kings 11:1-3). His love of female variety became his sexual obsession, until he had 1000 women, exotic ones, which destroyed his life (Eccl 7:26-29).

Man! If you play with fantasies, pornography, fornication, or friendship with a woman not wholly the Lord’s, you are a flattering fool. You are a fool, because you have rejected God’s warnings. You are a flattering fool, because you have lied to yourself that you can get away with it. You will soon hate your precious sin, which will destroy you (Ps 36:2).

You are a fool to think you can escape your sin and its punishment by repenting later, for you are in perfect bondage to your lusts; you will neither be able nor willing to set yourself free. If you do escape sexual diseases, the rage of a jealous husband, or the sentence of the judge, you will be infallibly overtaken by the righteous judgment of God.

There is no greater bondage than a child of God who cannot repent and find joy and peace with his Lord. Do you hear it, sinner? You cannot repent! Why can you not repent? Because you have become a slave to your lusts, and your own heart is in the death throes of sinful thoughts and actions. Every time you allow a sinful thought or action in your life, you twist another sinful strand into the cords that will bind you in your sexual sins.

If you are playing with fantasies, pornography, or a sinful relationship, get away now. Flee youthful lusts, Paul would say (II Tim 2:22). Do not go near any place or thing that tempts you to sin sexually (Pr 4:15; 5:8; Ps 101:3; Rom 13:11). Pluck out your right eye or cut off your right hand rather than play with sexual sin, Jesus would say (Mat 5:28-30).

If you are addicted to a sexual sin, your case is not hopeless, but you will never free yourself by your means or strength. You must cut off the sin violently, totally, now! Repent with these words (Job 33:27-28). Beg God’s power in Jesus’ name to deliver you from sin, sex, and Satan. Humble yourself to a spouse, a parent, or a pastor with every condemning detail. Pursue God’s worship in public and private with your whole heart.

Nothing is too hard for the Lord Christ! You can read that harlots went into the kingdom of God before religious Pharisees (Matt 21:31). Paul told of many sexual sinners at Corinth, “And such were some of you: but ye are washed, but ye are sanctified, but ye are justified in the name of the Lord Jesus, and by the Spirit of our God” (I Cor 6:11).

\subsection{Proverb 5:23}
What happens to men who play with whores? They will be punished and die in shame. There are good and bad ways to die, but ending a life of fornication is one of the worst.

Chapter five of Proverbs warns about whores – women having sex outside marriage (Pr 5:1-14). Solomon wanted to save his son from fornication and adultery. Wisdom’s cure is to rejoice in the body and lovemaking of your own wife (Pr 5:15-19), for God sees and judges sexual sins (Pr 5:20-21), and sexual addiction will destroy fools (Pr 5:22). 

Why did Solomon warn so often about whores? They are a great threat to young men, who by youth and hormones are vulnerable to them. This generation makes it worse by casual sex, loose women, lascivious movies and music, birth control, immodest clothing, pornography, mixed swimming, co-educational schools, carnal churches, no civil threat, abortion, coed gyms, unchaperoned dating, coed offices, sexting, and weak parenting.

The man here was instructed (Pr 5:12-14). He was taught often and well by parents and pastors to abstain from fornication (I Thess 4:3-8). He chose the life of a hypocrite by attending church but allowing himself to participate in fornication. At the end, when this horrible sin has killed his soul and ruined his life, he will die without benefiting from the instruction he had been given. He rejected the good advice and destroyed himself by sex.

Sexual sins give pleasure for a season, but it is a very short season (Heb 11:25). And then comes destruction and misery (Pr 5:9-11). Just ask Samson! The lust of the flesh craves sex, which is a man’s bodily desire for it (I Cor 7:1-9). The lust of the eyes fantasizes about women, either in person or in pictures. The pride of life tells a man he is the best and deserves the best, so he justifies sexual liberties. The combination of lusts is lethal. 

The blinded victim cannot see past the curvaceous body, the wanton eyes, the bold face, and the painted lips to the destruction ahead (Pr 6:25; 7:13). He cannot hear above her flattering voice the warnings of his teachers (Pr 5:3; 7:14-18). His lusts have conspired together to take a woman for great pleasure. He goes after her as an ox to the slaughter and a bird to the snare (Pr 7:22-23); he cannot see he is committing suicide (Pr 2:18-19).

What he thought was for pleasure becomes his destruction! Sex outside marriage is sin, and God will judge it (Heb 13:4). Being the addicting sin that it is (Pr 5:22), it will lead a man astray from every good path (Pr 5:23). Though he was taught thoroughly about a successful life, the illusion of pleasure will destroy him inside and out. His great folly in thinking he can escape the consequences will take him forever from the paths of life.

Listen! Who do you think you are? You are not special. You were born, and you will die, just like others. God is not mocked. If you persist in this sin, He can and will blind you to do inconvenient things and ruin your life. Listen to your teachers. Repent today. Run not only from whores, but run as well from anything tending toward them (Matt 5:27-30; Ps 101:3; Rom 13:14). Maybe God will have mercy. Maybe it is not too late.

Can such an addicted prisoner be freed? Yes! By the gift of repentance from God (II Tim 2:25-26)! But the repentance must be the kind that God recognizes and rewards – the godly kind that clears men from sins (II Cor 7:10-11). David repented of his adultery and murder, and God freely forgave him and delivered him gloriously from destruction.

Thanks be to God! Jesus Christ has provided cleansing for all kinds of sexual sins (I Cor 6:9-11). And God sent Him to “proclaim liberty to the captives, and the opening of the prison to them that are bound” (Is 61:1). Sexual sinners can be forgiven and freed from the bondage of their sins. Ask the woman of Samaria and others. Thanks be to God!











