\chapter{Proverb 7}
\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{BEHOLD A FOOL}}\\ (Proverb 7:1-27) \begin{compactenum}[I.][8]
    \item The \textbf{Victim} \index[scripture]{Proverbs!Pro 007:07} (Pro 7:7)
    \item The \textbf{Void} \index[scripture]{Proverbs!Pro 007:07} (Pro 7:7)
    \item The \textbf{Vestments} \index[scripture]{Proverbs!Pro 007:10} (Psa 7:10)
    \item The \textbf{Voice} \index[scripture]{Proverbs!Pro 007:11} (Pro 7:11)
    \item The \textbf{Vigour} \index[scripture]{Proverbs!Pro 007:11} (Pro 7:11)
    \item The \textbf{Vows} \index[scripture]{Proverbs!Pro 007:14} (Pro 7:14)
    \item The \textbf{Vamp} \index[scripture]{Proverbs!Pro 007:18} (Pro 7:18)
\end{compactenum}}


\marginpar{\scriptsize \centering \fcolorbox{bone}{yellow}{\textbf{WISDOM}}\\ (Proverb 7:1-27) \begin{compactenum}[I.][8]
    \item \textbf{Portrayed as a Desirable Woman}
    \item \textbf{Propagated by a Disciplined Way}
    \item \textbf{Promoted by Dutiful Warnings}
    \item \textbf{Pictured as a Devoted Wife} \index[scripture]{Proverbs!Pro 31}(Pro 31)
    \item \textbf{Proclaimed \& Displayed Worldwide}
    \item \textbf{Present in the Daily World}
    \item \textbf{Provided to Devoted Wayfarers (Pilgrims)}
    \item \textbf{Points to the the Darling Word (the Living Word)}\end{compactenum}}

\marginpar{\scriptsize \centering \fcolorbox{bone}{black}{\textbf{\textcolor[cmyk]{0,0,0,0}{DEVIL IN A BLUE DRESS}}}\\ (Proverb 7) 
\begin{compactenum}[I.][8]
    \item  \textbf{Flattering Words}  \index[scripture]{Proverbs!Pro 007:05} \index[scripture]{Proverbs!Pro 007:21} (Pro 7:5, 21) 
    \item The \textbf{Foolish Direction}  \index[scripture]{Proverbs!Pro 007:08} (Pro 7:8) 
    \item A \textbf{Found Victim}  \index[scripture]{Proverbs!Pro 007:15} (Pro 7:15) 
    \item The \textbf{Filled Senses}  \index[scripture]{Proverbs!Pro 007:18} (Pro 7:18) 
	\item The \textbf{Fair Speech}  \index[scripture]{Proverbs!Pro 007:21} (Pro 7:21) 
	\item \textbf{Forced Deed?}  \index[scripture]{Proverbs!Pro 007:21} (Pro 7:21) 
   \item The \textbf{Fatal Decision}  \index[scripture]{Proverbs!Pro 007:23} (Pro 7:23) 
\end{compactenum}}

\marginpar{\scriptsize \centering \fcolorbox{bone}{blue}{\textbf{\textcolor[cmyk]{0,0,0,0}{A FOOLISH YOUNG MAN}}}\\ (Proverb 7) 
\begin{compactenum}[I.][8]
    \item \textbf{Caught}  \index[scripture]{Proverbs!Pro 007:13}  (Pro 7:13) 
    \item The \textbf{Coverings}  \index[scripture]{Proverbs!Pro 007:16} (Pro 7:16)
    \item The \textbf{Carvings}  \index[scripture]{Proverbs!Pro 007:16} (Pro 7:16)
    \item The \textbf{Cinnamon}  \index[scripture]{Proverbs!Pro 007:17} (Pro 7:17)
    \item The \textbf{Conquest}  \index[scripture]{Proverbs!Pro 007:21} (Pro 7:21)
    \item The \textbf{Correction}  \index[scripture]{Proverbs!Pro 007:22} (Pro 7:22)
    \item The \textbf{Corpses}  \index[scripture]{Proverbs!Pro 007:22} (Pro 7:22)
\end{compactenum}}

\marginpar{\scriptsize \centering \fcolorbox{bone}{orange}{\textbf{STUPID MEETS SENSUAL}}\\ (Proverb 7:7-23) \begin{compactenum}[I.][14]
    \item A \textbf{Simple} One \index[scripture]{Proverbs!Pro 007:07} (Pro 7:7)
    \item The \textbf{Streets} \index[scripture]{Proverbs!Pro 007:07} \index[scripture]{Proverbs!Pro 007:11}(Pro 7:7, 11)
    \item The \textbf{Setting}  \index[scripture]{Proverbs!Pro 007:09} (Pro 7:9)
    \item The \textbf{Subtilty}  \index[scripture]{Proverbs!Pro 007:10} (Pro 7:10)
    \item The \textbf{Stubbornness}  \index[scripture]{Proverbs!Pro 007:11} (Pro 7:11)
    \item The \textbf{Seduction}  \index[scripture]{Proverbs!Pro 007:13} (Pro 7:13)
    \item The \textbf{Sensuality}  \index[scripture]{Proverbs!Pro 007:16-17} (Pro 7:16-17)
    \item The \textbf{Speech}  \index[scripture]{Proverbs!Pro 007:21} (Pro 7:21)
    \item The \textbf{Solace}  \index[scripture]{Proverbs!Pro 007:18} (Pro 7:18)
    \item \textbf{Straightway}  \index[scripture]{Proverbs!Pro 007:22} (Pro 7:22)
    \item The \textbf{Slaughter}  \index[scripture]{Proverbs!Pro 007:22} (Pro 7:22)
    \item The \textbf{Stocks}  \index[scripture]{Proverbs!Pro 007:22} (Pro 7:22)
    \item The \textbf{Snare}  \index[scripture]{Proverbs!Pro 007:23} (Pro 7:23)
    \item The \textbf{Striking}  \index[scripture]{Proverbs!Pro 007:23} (Pro 7:23)
\end{compactenum}}



\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/bible.html}{\textcolor[cmyk]{0.99998,1,0,0}{Proverbs Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{My\textcolor{jungle}{$_{2496}^{1}$} son, keep my words, and lay up my commandments with thee.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{Keep\textcolor{jungle}{$_{2508}^{13}$} my commandments, and live; and my law as the apple of thine eye.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{Bind\textcolor{jungle}{$_{2522}^{27}$} them upon thy fingers, write them upon the table of thine heart.}\footnote{\textbf{Proverb 3:3} - Let not mercy and truth forsake thee: bind them about thy neck; write them upon the table of thine heart:}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Say\textcolor{jungle}{$_{2535}^{40}$} unto wisdom, Thou \emph{art} my sister; and call \fcolorbox{bone}{MYGOLD}{understanding} \emph{thy} kinswoman:}
[5] \textcolor[cmyk]{0.99998,1,0,0}{That\textcolor{jungle}{$_{2547}^{52}$} they may keep thee from the strange woman, from the stranger \emph{which} flattereth with her words.}\footnote{\textbf{Proverb 2:16} - To deliver thee from the strange woman, even from the stranger which flattereth with her words; }\footnote{\textbf{Proverb 23:27} - or a whore is a deep ditch; and a strange woman is a narrow pit.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{For\textcolor{jungle}{$_{2564}^{69}$} at the window of my house I looked through my casement,}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And\textcolor{jungle}{$_{2576}^{81}$} beheld \fcolorbox{bone}{lime}{among} \fcolorbox{bone}{lime}{the} \fcolorbox{bone}{lime}{simple} \fcolorbox{bone}{lime}{ones}, I discerned among the youths, a young man \fcolorbox{bone}{lime}{void} of \fcolorbox{bone}{MYGOLD}{understanding},}\footnote{\textbf{Proverb 1:22} - How long, ye simple ones, will ye love simplicity?}\footnote{\textbf{Proverb 10:13} - In the lips of him that hath understanding wisdom is found: but a rod is for the back of him that is void of understanding.}\footnote{\textbf{Proverb 12:11} - (Proverbs 12:11) "He that tilleth his land shall be satisfied with bread: but he that followeth vain persons is void of understanding.}\footnote{\textbf{Proverb 17:18} - A man void of understanding striketh hands, and becometh surety in the presence of his friend.}\footnote{\textbf{Proverb 24:30} -  I went by the field of the slothful, and by the vineyard of the man void of understanding;}
[8] \textcolor[cmyk]{0.99998,1,0,0}{Passing\textcolor{jungle}{$_{2593}^{98}$} through the street near her corner; and he went the way to her house,}
[9] \textcolor[cmyk]{0.99998,1,0,0}{In\textcolor{jungle}{$_{2608}^{113}$} the twilight, in the evening, in the black and dark night:}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And\textcolor{jungle}{$_{2620}^{125}$}, behold, there met him a woman \emph{with} the \fcolorbox{bone}{lime}{attire} of an harlot, and subtil of heart.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{(She\textcolor{jungle}{$_{2637}^{142}$} \emph{is} \fcolorbox{bone}{lime}{loud} and stubborn; her feet \fcolorbox{bone}{lime}{abide not} in her house:}
[12] \textcolor[cmyk]{0.99998,1,0,0}{Now\textcolor{jungle}{$_{2649}^{154}$} \emph{is} \emph{she} without, now in the streets, and lieth in wait at every corner.)}
[13] \textcolor[cmyk]{0.99998,1,0,0}{So\textcolor{jungle}{$_{2664}^{169}$} she caught him, and kissed him, \emph{and} with an impudent face said unto him,}\footnote{\textbf{Exekiel 2:4} - For they are impudent children and stiffhearted. I do send thee unto them; and thou shalt say unto them, Thus saith the Lord GOD.}\footnote{\textbf{Ezekiel 3:7} - But the house of Israel will not hearken unto thee; for they will not hearken unto me: for all the house of Israel are impudent and hardhearted.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{\emph{I}\textcolor{jungle}{$_{2679}^{184}$} \emph{have} peace offerings with me; this day have I payed my vows.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{Therefore\textcolor{jungle}{$_{2692}^{197}$} came I forth to meet thee, diligently to seek thy face, and I have found thee.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{I\textcolor{jungle}{$_{2709}^{214}$} have decked my bed with coverings of tapestry, with carved \emph{works}, with fine linen of Egypt.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{I\textcolor{jungle}{$_{2726}^{231}$} have perfumed my bed with myrrh, aloes, and cinnamon.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{Come\textcolor{jungle}{$_{2736}^{241}$}, \fcolorbox{bone}{lime}{let us take our fill} of love until the morning: let us solace ourselves with loves.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{For\textcolor{jungle}{$_{2753}^{258}$} the goodman \emph{is} not at home, he is gone a long journey:}
[20] \textcolor[cmyk]{0.99998,1,0,0}{He\textcolor{jungle}{$_{2766}^{271}$} hath taken a bag of money with him, \emph{and} will come home at the day appointed.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{With\textcolor{jungle}{$_{2783}^{288}$} her much fair speech she caused him to yield, with the flattering of her lips she forced him.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{He\textcolor{jungle}{$_{2802}^{307}$} goeth after her straightway, as an ox goeth to the slaughter, or as a fool to the correction of the stocks;}
[23] \textcolor[cmyk]{0.99998,1,0,0}{Till\textcolor{jungle}{$_{2824}^{329}$} a \fcolorbox{bone}{lime}{dart strike through} his liver; as a bird hasteth to the snare, and knoweth not that it \emph{is} for his life.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Hearken\textcolor{jungle}{$_{2847}^{352}$} unto me now therefore, O ye children, and attend to the words of my mouth.}\footnote{\textbf{Proverb 5:1} - My son, attend unto my wisdom, and bow thine ear to my understanding}
[25] \textcolor[cmyk]{0.99998,1,0,0}{Let\textcolor{jungle}{$_{2863}^{368}$} not thine heart decline to her ways, go not astray in her paths.}
[26] \textcolor[cmyk]{0.99998,1,0,0}{For\textcolor{jungle}{$_{2877}^{382}$} she hath cast down many wounded: yea, many strong \emph{men} have been slain by her.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{Her\textcolor{jungle}{$_{2893}^{398}$} house \emph{is} the way to hell, going down to the chambers of death\textcolor{jungle}{$_{2906}^{411}$}.}




