\section{Proverb 8 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} There are 13 words in verses Proverb 8:16 and 8:35. Verses 7, 9, 19, and 22 contain 13 unique words. The 13-letter words ``understanding,'' ``righteousness,'' and ``understandeth,'' are found in the chapter. The word ``me'' is found 13 times in the chapter (in the chapter, ``me'' is wisdom speaking or herself), and the 13 instances may just be portraying man's decision to not follow the voice of wisdom.

\subsection{Proverb 8 Introduction}
A theme of the chapter is ``Responding to Wisdom,'' with the following suggested outline:
\begin{compactenum}
    \item The \textbf{High Places} of Wisdom (Proverb 8:1-4)
    \item The \textbf{Heart} of the Listener (Proverb 8:5)
    \item \textbf{Hearing the Cry} (Proverb 8:6-10)
    \item \textbf{Help} from Wisdom (Proverb 8:11-17)
    \item The \textbf{Honour} from Wisdom (Proverb 8:18-20)
    \item The \textbf{History} of Wisdom (Proverb 8:21-31)
    \item \textbf{Hearkening} to Wisdom (Proverb 8:32-36)
\end{compactenum}

\subsection{Proverbs 8:1}
Wisdom is speaking, crying, even shouting, and hence mankind is told (1) to hear  in verse 6, (2) to receive instruction in verse 10, (3) to hearken in verse 32, and (4) to hear in verse 33. \cite{ruckman1972proverbs}


\subsection{Proverbs 8:8}
What is being spoken of are the ``words'' from the mouth of wisdom.

\subsection{Proverb 8:13}
It is instructive that the ``fear of the LORD'' shows up in verse 13, associating it with man's rebellion. As a whole, mankind fully embraces pride, arrogancy, the evil way, and the froward mouth.

\subsection{Proverbs 8:24}
From the verse, we can conclude that there was a time when the ``depths'' were not there (``depths'' equated with the ``deep'', used elsewhere), as were not the ``fountains.''

\subsection{Proverbs 8:28}
These fountains were there for Noah's flood back in Genesis 7:11 and 8:2.\footnote{\textbf{Genesjs 7:11} - In the six hundredth year of Noah’s life, in the second month, the seventeenth day of the month, the same day were all the fountains of the great deep broken up, and the windows of heaven were opened.}\footnote{\textbf{Genesis 8:2} - The fountains also of the deep and the windows of heaven were stopped, and the rain from heaven was restrained;}


\subsection{Proverbs 8:31}
Perhasp the verse is referring to the pre-Adamic earth, partly in and partly out of the water, spoken of in 2 Peter 3:5.\footnote{\textbf{2 Peter 3:5} - For this they willingly are ignorant of, that by the word of God the heavens were of old, and the earth standing out of the water and in the water:}