\subsection{Outlines from Others}

\subsubsection{What a Friend}
\index[speaker]{Clarence Billheimer!Proverbs 18:24 (What a Friend)}
\index[series]{Proverbs (Clarence Billheimer)!Pro 18:24 (What a Friend)}
\index[date]{2015/04/12!Pro 18:24 (What a Friend) (Clarence Billheimer)}
\textbf{Introduction: } How many of you have friends? How about close friends? How many of you ever lost a friend (other than by death)? How about a close friend? Someone said we can count our true friends on one hand. Having a true friend is really more rare than we think. But the Bible tells us about the Lord Jesus Christ, a true friend, one, who as this passage says, ``sticks closer than a brother.'' Let us look at six things about this true friend, using the letters of the word friend.
\begin{compactenum}[I.]
    \item \textbf{He is faithful} \index[scripture]{1 John!1 John 1:09}(1 John 1:9)
    \item \textbf{He is our redeemer} \index[scripture]{Job!Job 19:25}(Job 19:25)
    \item \textbf{He is interested} \index[scripture]{Philippians!Phil 4:06}(Phil 4:6)
    \item \textbf{He is empathetic} \index[scripture]{Hebrews!Heb 04:15}(Heb 4:15)
    \item \textbf{He is near} \index[scripture]{Hebrews!Heb 13:05}(Heb 13:5)
    \item \textbf{He is our deliverer} (\index[scripture]{2 Samuel!2 Sam 22:02}2 Samuel 22:2, \index[scripture]{Psalm!Psa 18:02}Psalm 18:2)
\end{compactenum}
\textbf{Conclusion: } There are many other things about Jesus Christ that make Him a very special friend. Do you know Him as not only a friend, but as your Savior?

\subsubsection{Jesus, My Best Friend}
\textbf{Creator: }Matthew Hines\\ 
\textbf{Source: }Fundamental Baptist Sermon Outlines\\ 
\index[speaker]{Matthew Hines!Proverbs 18:24 (Jesus, My Best Friend)}
\index[series]{Proverbs (Matthew Hines)!Pro 18:24 (Jesus, My Best Friend)}
\index[date]{2017/17/13!Proverbs 18:24 (Jesus, My Best Friend) (Matthew Hines)}
\textbf{Introduction: } Friends make this life much more enjoyable. There is nothing like serving the Lord with brothers and sisters in Christ. Maybe you fish, hunt, or enjoy other types of activities with those you cherish in this life. We all have special people in our lives that we love to spend time with; however, our best friend should always be the Lord Jesus Christ. In times of trouble, grief, sorrow, and despair, Jesus has been there for you and I. In times of joy, happiness, excitement, and gain, Jesus has been there for you and I!
Notice several things with me about this friendship you and I ought to cherish:
\begin{compactenum}[I.]
    \item The \textbf{PERSON of This Friendship: Gods SON} \index[scripture]{Proverbs!Pro 18:24} (Pro 18:24)
    \item The \textbf{PRICE of This Friendship: SACRIFICE} \index[scripture]{John!John 15:13} (John 15:13)
    \item The \textbf{POWER of This Friendship: Gives me STRENGTH} \index[scripture]{Philippians!Phil 04:13} (Phil 4:13)
    \item The \textbf{PERPETUITY of This Friendship: He is STEDFAST} \index[scripture]{Proverbs!Pro 17:17} (Pro 17:17)
    \item  \textbf{PROOF of This Friendship: SERVICE in His name} \index[scripture]{John!John 14:15} (John 14:15)
    \end{compactenum}
\textbf{Conclusion: } consider these thoughts from the scripture as you go throughout your day. Jesus is the greatest friend you have. He desires that you would know Him on a real and personal level. Do you know him today? If not make a new friend, the best friend you'll ever have!

%\subsubsection{What a Friend}
%\textbf{Creator: }Richard Drummond\\ 
%\textbf{Source: }Fundamental Baptist Sermon Outlines\\ 
%\index[speaker]{Richard Drummond!Proverbs 18:24 (What a Friend)}
%\index[series]{Proverbs (Richard Drummond)!Proverbs 18:24 What a Friend)}
%\index[date]{2017/17/13!Proverbs 18:24 (What a Friend) (Richard Drummond)}
%\textbf{Introduction: } Friends make this life much more enjoyable. There is nothing like serving the Lord with brothers and sisters in Christ. Maybe you fish, hunt, or enjoy other types of activities with those you cherish in this life. We all have special people in our lives that we love to spend time with; however, our best friend should always be the Lord Jesus Christ. In times of trouble, grief, sorrow, and despair, Jesus has been there for you and I. In times of joy, happiness, excitement, and gain, Jesus has been there for you and I!
%Notice several things with me about this friendship you and I ought to cherish:
%\begin{compactenum}[I.]
%%    \item The \textbf{Availability} of a Friend\index[scripture]{Proverbs!Pro 18:24} (Proverb 18:24)
%    \begin{compactenum}[A.]
%    	\item Nature desires friends
%    	\item Need demands friends
%    \end{compactenum}
%    \item The \textbf{Attributes} of a Friend\index[scripture]{Proverbs!Pro 18:24} (Proverb 18:24)
%    \begin{compactenum}[A.]
%    	\item Sympathetic touched when mistreated, sorrow, loss, cries, misunderstood
%    	\item Steadfast - there all the time \index[scripture]{Proverbs!Pro 17:17} (Proverbs 17:17)
%    	\item Strong
%    \end{compactenum}
%    \item The \textbf{Accessibility} of a Friend\index[scripture]{Proverbs!Pro 18:24} (Proverb 18:24)    \begin{compactenum}[A.]
 %   	\item He accepts us \index[scripture]{John!Jhn 6:37} (John. 6:37)
 %   	\item He affirms us \index[scripture]{1 John!1Jn 3:1} (1 John 3:1)
%    	\item He assists \index[scripture]{Philippians!Phil 4:13} (Phil 4:13)
%    \end{compactenum}
%\end{compactenum}






