\subsection{Outlines from Brian Eades}

\subsubsection{Finding A Wife Finding a Good Thing}

\index[speaker]{Brian Eades!Proverb 18:22 (Finding A Wife Finding a Good Thing)}
\index[series]{Proverbs (Brian Eades)!Pro 18:22 (Finding A Wife Finding a Good Thing)}
\index[date]{2018/10/22!Pro 18:22 (Finding A Wife Finding a Good Thing) (Brian Eades)}

\index[FACEBOOK]{SERMON HINTS!Brian Eades (Finding A Wife Finding a Good Thing) - Proverb 18:22!2018/10/22}

\noindent  \textbf{Introduction: } When God created everything, he said that it all was "very good" with the exception of one thing, and that was the loneliness of man. That was the only thing that God said was "not good". Shall we say that God makes things that aren't good so that good can come from it? 
That only seems to be the picture in the story of creation. I think the statement that man being alone was "not good" was God's way of saying that he was not finished with the full  (or complete) creation of Humanity as he intended it.
Here in the Book of Proverbs we have the statement that when man finds a wife he finds a good thing. I can tell of many instances where when a man found a wife it was the worst thing, but the overall picture here is that a man finds someone who honors God with their life and supports him, and helps complete him in life. God intended the woman to be a help that was meet for him, or right for him. There are many women that are NOT right for any man!\\
\\
*Finding a wife should be a: \\
\begin{compactenum}[I.]
    \item A \textbf{PRAYERFUL SEARCH}
    \item A \textbf{POSITIVE SEARCH}
    \item A \textbf{PATTERNED SEARCH}
    \item A \textbf{PROFITABLE SEARCH}
    \item A \textbf{PLEASING SEARCH}
\end{compactenum}
