\subsection{Outlines from Chapman}


\subsubsection{A Sure Sign of Intelligence}

\index[speaker]{Jimmy Chapman!Proverb 17:27-28 (A Sure Sign of Intelligence)}
\index[series]{Proverbs (Jimmy Chapman)!Pro 17:27-28 (A Sure Sign of Intelligence)}
\index[date]{2020/02/22!Proverb 17:27-28 (A Sure Sign of Intelligence) (Jimmy Chapman)}

\noindent  \textbf{Introduction: } Before us are references to individuals having “knowledge” and “understanding” and being “counted wise.” These are individuals that possess an intelligence that is cunning, skillful, and discerning in its nature. These are attributes needed by each of us if we are to live a life that exalts and magnifies our Saviour, the Lord Jesus Christ. These individuals not only share the substance of intelligence but the sign of intelligence!

\begin{compactenum}[I.]
    \item RESTRAINT -  Their intelligence is marked by the ability to control their tongue. He that “spareth his words” knows something about RESTRAINT. This person knows not only when to talk, but how much! This person knows that “A soft answer turneth away wrath: but grievous words stir up anger” (Proverbs 15:1).
    \item RESPONSE - He that “holdeth his peace” knows something about RESPONSE. The word “holdeth” means to be silent, to let alone, to be deaf. This person has discovered that there are times when the best thing to do is quietly turn and walk away; a verbal response will only fuel the fire!
    \item REFUSAL -He that “shutteth his lips” knows something about REFUSAL. The word “shutteth” means to close, shut or stop. The man of understanding knows to “Answer not a fool according to his folly, lest thou also be like unto him” (Proverbs 26:4). Sometimes the best answer is no answer! An old mountain proverb says, “Better to be silent and thought a fool than open your mouth and prove it!” A sure sign of intelligence may not be what comes out of your mouth, but what doesn’t! Are you showing the sure sign of intelligence?
\end{compactenum}



\index[FACEBOOK]{JUST BAPTIST  OUTLINES!Jimmy Chapman (A Sure Sign of Intelligence) - Proverb 17:27-28!2020/02/22}


