\section{Proverb 5 Outlines}

\subsection{My Outlines}

\subsubsection{Regrets of a Sensual Son}
\textbf{Introduction: }In Proverb 5 we see what the sensual son regrets he did not do. He wishes he had:
\index[speaker]{Keith Anthony!Proverb 05 (Regrets of a Sensual Son)}
\index[series]{Proverbs (Keith Anthony)!Pro 05 (Regrets of a Sensual Son)}
\index[date]{2014/12/06!Proverb 05 (Regrets of a Sensual Son) (Keith Anthony)}
\begin{compactenum}[I.][8]

    \item  \textbf{Chased the Honeycomb!} \index[scripture]{Proverbs!Pro 05:03} (Pro 5:3)
    \item  \textbf{Wasted His Health} \index[scripture]{Proverbs!Pro 05:11} (Pro 5:11)
    \item  \textbf{Gave Away his Honor} \index[scripture]{Proverbs!Pro 05:09} (Pro 5:9)
    \item \textbf{Hated Instruction} \index[scripture]{Proverbs!Pro 05:12} (Pro 5:12)
    \item Did Not \textbf{Heed Correction} \index[scripture]{Proverbs!Pro 05:12} (Pro 5:12)
    \item Did Not \textbf{Harken Unto Teachers} \index[scripture]{Proverbs!Pro 05:13} (Pro 5:13)
    \item Did Not \textbf{Hear His Instructors} \index[scripture]{Proverbs!Pro 05:13} ( Pro 5:13)
    
\end{compactenum}


\subsubsection{Thine Own Cistern}

\index[speaker]{Keith Anthony!Proverb 05 (Thine Own Cistern)}
\index[series]{Proverbs (Keith Anthony)!Pro 05 (Thine Own Cistern)}
\index[date]{2014/12/06!Proverb 05 (Thine Own Cistern) (Keith Anthony)}

\begin{compactenum}[I.][8]
    \item \textbf{Running Waters} \index[scripture]{Proverbs!Pro 05:15}(Pro 5:15)
    \item The \textbf{Reserving} \index[scripture]{Proverbs!Pro 05:17}(Pro 5:17)
    \item The \textbf{Rejoicing} \index[scripture]{Proverbs!Pro 05:18}(Pro 5:18)
    \item The \textbf{Roe} \index[scripture]{Proverbs!Pro 05:19}(Pro 5:19)
    \item The \textbf{Ravished} \index[scripture]{Proverbs!Pro 05:19}\index[scripture]{Proverbs!Pro 05:20}(Pro 5:19, 20)
    \item A \textbf{Rejection} \index[scripture]{Proverbs!Pro 05:20}(Pro 5:20)
    \item A \textbf{Review} \index[scripture]{Proverbs!Pro 05:21}(Pro 5:21)
\end{compactenum}





\subsubsection{Stay Pure and Enjoy it}
\textbf{Introduction:} Proverbs 5 is entirely devoted to the subject of sexual and marital Proverbs 5 contains essential wisdom on pre-marital and extra-marital sexual relations:
\index[speaker]{Keith Anthony!Proverb 05 (Stay Pure and Enjoy it)}
\index[series]{Proverbs (Keith Anthony)!Pro 05 (Stay Pure and Enjoy it)}
\index[date]{unknown!Proverb 05 (Stay Pure and Enjoy it) (Keith Anthony)}

\begin{compactenum}[I.]
    \item \textbf{The Father's Appeal} \index[scripture]{Proverbs!Pro 05:01,07}(Proverbs 5:1, 7) There are two separate appeals in the proverb, in verses 1 and 7.  Some divide the chapter into three sections: verses 1-6, verses 7-14, and verses 15-23. The first two contain the father's emotional appeal.
    \item \textbf{A Fleshly Appetite} The appetite for sexual relations is built into mankind.  It exists.  It is natural. It is even wholesome when directed according to God's will. As with all things, though, Satan provides counterfeit and convenient ways to get side-tracked.
    \item \textbf{A Fatal Attraction} \index[scripture]{Proverbs!Pro 05:03-05}(Pro 5:3-5) Consider the death spiral of verses 3-5.
    \item \textbf{A Foolish Absurdity} - It is foolish and absurd to think that marital infidelity can be done is secret or with impunity. \index[scripture]{Proverbs!Pro 05:21}(Pro 5:21) reminds that the ``eyes of the Lord'' are watching, and seemingly watching especially this!
    \item \textbf{Faithful Attention} The challenge is given to the son to stay faithful to only the one God has provided, and to garner immense satisfaction from the relationship. The challenge is given to want, to be ravished by, what you already have, and not to want something else.
    \item \textbf{A Fruitful Arrangement} \index[scripture]{Proverbs!Pro 05:15-19}(Pro 5:15-19) In verses 15 and 16, the author uses the metaphor of a flowing waters (cisterns, wells, foundations, rivers). In verse 17, attention is brought to the unique privilege of marriage. In verses 18 and 19, a request is made to bless the wife in the context of marital relations.
    \item \textbf{Final Accountability} \index[scripture]{Proverbs!Pro 05:21}(Pro 5:21) The passage, finally, and teachers of it should also, reminds us that God will hold all accountable for behavior, including sexual behavior. In the temporal experience, even modern   medicine, psychology, and sociology confirm that promiscuity is self-destructive.
\end{compactenum}

\subsubsection{See the Seductress}
\textbf{Introduction:} Proverb 5 is entirely devoted to the subject of sexual and marital purity. The chapter contains 4 verses with 13 words, with 4 being the number for creation (all 4 directions on a compass) and 13 the number of rebellion. The number 5, the chapter address, is also the number of death, suggesting the serious of the issue.  Verses 3-5 even have a 5-fold description of the the strange woman:
\index[speaker]{Keith Anthony!Proverb 05 (See the Seductress)}
\index[series]{Proverbs (Keith Anthony)!Pro 05 (See the Seductress)}
\index[date]{unknown!Proverb 05 (See the Seductress) (Keith Anthony)}
\begin{compactenum}[I.]
    \item She has lips of honey \index[scripture]{Proverbs!Pro 05:03} (Pro 5:3) 
    \item She has a mouth smooth as oil \index[scripture]{Proverbs!Pro 05:03} ( Pro 5:3)
    \item Her end is as bitter wormwood \index[scripture]{Proverbs!Pro 05:04} (Pro  5:4)
    \item Her feet walk the road to ruin \index[scripture]{Proverbs!Pro 05:05} (Pro 5:5)
    \item Her steps (direction) are to death \index[scripture]{Proverbs!Pro 05:05} Pro 5:5)
\end{compactenum}
\textbf{Conclusion:} Chapter 5, though, also contains God's wonderful solution to the problem of mankind's promiscuity. This suggests that the problem discussed in the chapter is a very common and natural (to a natural lost man and lost culture) thing.  Adultery assuredly is a common problem even among Christian marriages. Pre-marital relationships are trap which often keeps one for life. Proverbs 5 does not deal with the issue delicately: it deals with the issue directly.  There are sexual urges and appetites that exist and which must be controlled and directly the correct way.  Otherwise, it will be misery and ruin.