\subsection{Outlines from Hines}

\subsubsection{Jesus, My Best Friend}

\index[speaker]{Matthew Hines!Proverb 18:24 (Jesus, My Best Friend)}
\index[series]{Proverbs (Matthew Hines)!Pro 18:24 (Jesus, My Best Friend)}
\index[date]{2017/17/13!Proverb 18:24 (Jesus, My Best Friend) (Matthew Hines)}

\noindent  \textbf{Introduction: } Friends make this life much more enjoyable. There is nothing like serving the Lord with brothers and sisters in Christ. Maybe you fish, hunt, or enjoy other types of activities with those you cherish in this life. We all have special people in our lives that we love to spend time with; however, our best friend should always be the Lord Jesus Christ. In times of trouble, grief, sorrow, and despair, Jesus has been there for you and I. In times of joy, happiness, excitement, and gain, Jesus has been there for you and I!
Notice several things with me about this friendship you and I ought to cherish:
\begin{compactenum}[I.]
    \item The \textbf{PERSON of This Friendship: Gods SON} \index[scripture]{Proverbs!Pro 18:24} (Pro 18:24)
    \item The \textbf{PRICE of This Friendship: SACRIFICE} \index[scripture]{John!John 15:13} (John 15:13)
    \item The \textbf{POWER of This Friendship: Gives me STRENGTH} \index[scripture]{Philippians!Phil 04:13} (Phil 4:13)
    \item The \textbf{PERPETUITY of This Friendship: He is STEDFAST} \index[scripture]{Proverbs!Pro 17:17} (Pro 17:17)
    \item  \textbf{PROOF of This Friendship: SERVICE in His name} \index[scripture]{John!John 14:15} (John 14:15)
    \end{compactenum}
\textbf{Conclusion: } consider these thoughts from the scripture as you go throughout your day. Jesus is the greatest friend you have. He desires that you would know Him on a real and personal level. Do you know him today? If not make a new friend, the best friend you'll ever have!


\index[FACEBOOK]{FUNDAMENTAL BAPTIST SERMON OUTLINES!Matthew Hines - Proverb 18:24!2017/17/13}