\chapter{Proverb 15}\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{RIGHTEOUS LIPS}}\\ (Proverbs 15:1-33) \begin{compactenum}[I.][8]
    \item \textbf{Turn Away Wrath}  \index[scripture]{Proverbs!Pro 15:01}(Pro 15:1)
    \item \textbf{Dispense Knowledge} \index[scripture]{Proverbs!Pro 15:02, 07}(Pro 15:2, 7)
    \item \textbf{Are Wholesome} \index[scripture]{Proverbs!Pro 15:04}(Pro 15:4)
    \item \textbf{Offer counsel} \index[scripture]{Proverbs!Pro 15:22}(Pro 15:22)
    \item \textbf{Speak in Due Season} \index[scripture]{Proverbs!Pro 15:23}(Pro 15:23)
    \item \textbf{Are Pure and Pleasant} \index[scripture]{Proverbs!Pro 15:26}(Pro 15:26)
    \item \textbf{Answer Slowly} \index[scripture]{Proverbs!Pro 15:28}(Pro 15:28) -- some answers are not easy
\end{compactenum}}

\marginpar{\scriptsize \centering \fcolorbox{bone}{yellow}{\textbf{RESPONDING TO CORRECTION}}\\ (Proverbs 15:1-33) \begin{compactenum}[I.][8]
    \item \textbf{Wrath}  \index[scripture]{Proverbs!Pro 15:01} 
                                      \index[scripture]{Proverbs!Pro 15:18} 
                                      (Pro 15:1, 18)
    \item \textbf{Reproof}  \index[scripture]{Proverbs!Pro 15:05} 
                                      \index[scripture]{Proverbs!Pro 15:10} 
                                      \index[scripture]{Proverbs!Pro 15:12} 
                                      \index[scripture]{Proverbs!Pro 15:31} 
                                      \index[scripture]{Proverbs!Pro 15:32}  (Pro 15:5, 10, 12, 31, 32)
    \item God's \textbf{Reconnaissance}  \index[scripture]{Proverbs!Pro 15:03}  (Pro 15:3)
    \item \textbf{Regard}  \index[scripture]{Proverbs!Pro 15:05}  (Pro 15:5)
    \item \textbf{Righteousness}  \index[scripture]{Proverbs!Pro 15:06} \index[scripture]{Proverbs!Pro 15:09} \index[scripture]{Proverbs!Pro 15:19} \index[scripture]{Proverbs!Pro 15:28} 
    \index[scripture]{Proverbs!Pro 15:29}  (Pro 15:6, 9, 19, 28, 29)
    \item \textbf{Refusal}  \index[scripture]{Proverbs!Pro 15:32}  (Pro 15:32)
    \item \textbf{Receiving}  \index[scripture]{Proverbs!Pro 15:32}  (Pro 15:32)
\end{compactenum}}
    
\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/proverbs_15.html}{\textcolor[cmyk]{0.99998,1,0,0}{Proverbs Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{A soft answer \fcolorbox{bone}{lime}{turneth away wrath}: but grievous words stir up anger.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{The tongue of the wise \fcolorbox{bone}{lime}{useth knowledge} aright: but the mouth of fools poureth out foolishness.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{The eyes of the LORD \emph{are} in every place, beholding the evil and the good.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{lime}{A wholesome tongue} \emph{is} a tree of life: but perverseness therein \emph{is} a breach in the spirit.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{A fool despiseth his father's instruction: but he \fcolorbox{bone}{bone}{that} regardeth reproof is prudent.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{In the house of the righteous \emph{is} much treasure: but in the revenues of the wicked is trouble.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{The lips of the wise \fcolorbox{bone}{lime}{disperse knowledge}: but the heart of the foolish \emph{doeth} not so.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{The sacrifice of the wicked \emph{is} an abomination to the LORD: but the prayer of the upright \emph{is} his delight.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{The way of the wicked \emph{is} an abomination unto the LORD: but he loveth him \fcolorbox{bone}{bone}{that} followeth after righteousness.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Correction \emph{is} grievous unto him \fcolorbox{bone}{bone}{that} forsaketh the way: \emph{and} he \fcolorbox{bone}{bone}{that} hateth reproof shall die.}\footnote{\textbf{Jeremiah 2:30} - In vain have I smitten your children; they received no correction: your own sword hath devoured your prophets, like a destroying lion.}\footnote{\textbf{Jeremiah 5:3} - O LORD, are not thine eyes upon the truth? thou hast stricken them, but they have not grieved; thou hast consumed them, but they have refused to receive correction: they have made their faces harder than a rock; they have refused to return.}\footnote{\textbf{Jeremiah 7:28} - But thou shalt say unto them, This is a nation that obeyeth not the voice of the LORD their God, nor receiveth correction: truth is perished, and is cut off from their mouth.}\footnote{\textbf{Zephaniah 3:2} - She obeyed not the voice; she received not correction; she trusted not in the LORD; she drew not near to her God.}\footnote{\textbf{2 Timothy 3:16} - All scripture is given by inspiration of God, and is profitable for doctrine, for reproof, for correction, for instruction in righteousness:}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Hell and destruction \emph{are} before the LORD: how much more then the hearts of the children of men?}
[12] \textcolor[cmyk]{0.99998,1,0,0}{A scorner loveth not one \fcolorbox{bone}{bone}{that} reproveth him: neither will he go unto the wise.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{A merry heart maketh a cheerful countenance: but by sorrow of the heart the spirit is broken.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{The heart of him \fcolorbox{bone}{bone}{that} hath understanding seeketh knowledge: but the mouth of fools feedeth on foolishness.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{All the days of the afflicted \emph{are} evil: but he \fcolorbox{bone}{bone}{that} is of a merry heart \emph{hath} a continual feast.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{Better \emph{is} little with the fear of the LORD than great treasure and trouble therewith.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Better \emph{is} a dinner of herbs where love is, than a stalled ox and hatred therewith.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{A wrathful man stirreth up strife: but \emph{he} \emph{that} \emph{is} slow to anger appeaseth strife.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{The way of the slothful \emph{man} \emph{is} as an hedge of thorns: but the way of the righteous \emph{is} made plain.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{A wise son maketh a glad father: but a foolish man despiseth his mother.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{Folly \emph{is} joy to \emph{him} \emph{that} \emph{is} destitute of wisdom: but a man of understanding walketh uprightly.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{Without \fcolorbox{bone}{lime}{counsel} purposes are disappointed: but in the multitude of \fcolorbox{bone}{lime}{counsellors} they are established.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{A man hath joy by the answer of his mouth: and a word \emph{spoken} \fcolorbox{bone}{lime}{in due season}, how good \emph{is} \emph{it}!}
[24] \textcolor[cmyk]{0.99998,1,0,0}{The way of life \emph{is} above to the wise, \fcolorbox{bone}{bone}{that} he may depart from hell beneath.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{The LORD will destroy the house of the proud: but he will establish the border of the widow.}
[26] \textcolor[cmyk]{0.99998,1,0,0}{The thoughts of the wicked \emph{are} an abomination to the LORD: but \emph{the} \emph{words} of the pure \emph{are} \fcolorbox{bone}{lime}{pleasant words}.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{He \fcolorbox{bone}{bone}{that} is greedy of gain troubleth his own house; but he \fcolorbox{bone}{bone}{that} hateth gifts shall live.}
[28] \textcolor[cmyk]{0.99998,1,0,0}{The heart of the righteous \fcolorbox{bone}{lime}{studieth to answer}: but the mouth of the wicked poureth out evil things.}
[29] \textcolor[cmyk]{0.99998,1,0,0}{The LORD \emph{is} far from the wicked: but he heareth the prayer of the righteous.}
[30] \textcolor[cmyk]{0.99998,1,0,0}{The light of the eyes rejoiceth the heart: \emph{and} a good report maketh the bones fat.}
[31] \textcolor[cmyk]{0.99998,1,0,0}{The ear \fcolorbox{bone}{bone}{that} heareth the reproof of life abideth among the wise.}
[32] \textcolor[cmyk]{0.99998,1,0,0}{He \fcolorbox{bone}{bone}{that} refuseth instruction despiseth his own soul: but he \fcolorbox{bone}{bone}{that} heareth reproof getteth understanding.}
[33] \textcolor[cmyk]{0.99998,1,0,0}{The fear of the LORD \emph{is} the instruction of wisdom; and before honour \emph{is} humility.}


