\subsection{Outlines from Billheimer}

\subsubsection{What a Friend}
\index[speaker]{Clarence Billheimer!Proverbs 18:24 (What a Friend)}
\index[series]{Proverbs (Clarence Billheimer)!Proverbs 18:24 (What a Friend)}
\index[date]{2015/04/12!Pro 18:24 (What a Friend) (Clarence Billheimer)}

\noindent  \textbf{Introduction: } How many of you have friends? How about close friends? How many of you ever lost a friend (other than by death)? How about a close friend? Someone said we can count our true friends on one hand. Having a true friend is really more rare than we think. But the Bible tells us about the Lord Jesus Christ, a true friend, one, who as this passage says, ``sticks closer than a brother.'' Let us look at six things about this true friend, using the letters of the word friend.
\begin{compactenum}[I.]
    \item \textbf{He is faithful} \index[scripture]{1 John!1 John 1:09}(1 John 1:9)
    \item \textbf{He is our redeemer} \index[scripture]{Job!Job 19:25}(Job 19:25)
    \item \textbf{He is interested} \index[scripture]{Philippians!Phil 4:06}(Phil 4:6)
    \item \textbf{He is empathetic} \index[scripture]{Hebrews!Heb 04:15}(Heb 4:15)
    \item \textbf{He is near} \index[scripture]{Hebrews!Heb 13:05}(Heb 13:5)
    \item \textbf{He is our deliverer} (\index[scripture]{2 Samuel!2 Sam 22:02}2 Samuel 22:2, \index[scripture]{Psalm!Psa 18:02}Psalm 18:2)
\end{compactenum}
\textbf{Conclusion: } There are many other things about Jesus Christ that make Him a very special friend. Do you know Him as not only a friend, but as your Savior?



\index[FACEBOOK]{FUNDAMENTAL BAPTIST SERMON OUTLINES!Clarence Billheimer (What a Friend) - Proverbs 18:24!2015/04/12}