\subsection{Devotionals from Os Hillman}


\subsubsection{The Purpose of Crucibles}

\index[speaker]{Os Hillman!Proverbs 17:3 (The Purpose of Crucibles)}
\index[series]{TGIF1 (Os Hillman)!Proverbs 17:3 (The Purpose of Crucibles)}
\index[date]{2022/01/19!Proverbs 17:3 (The Purpose of Crucibles) (Os Hillman)}

This proverb describes one of God's strangest mysteries. It is a description of God's formula to refine the human heart in order to bring out its finest qualities. The significant leaders who make the greatest mark for the Kingdom had to experience their own crucible and fire. Without it, the dross can never be removed from the human heart. Without it, the encumbrances weigh us down. God understands the human heart. He understands that for us to become all that He hopes for us, there are seasons of fire. Joseph went through many tests. Succeeding in the test qualified him for greater responsibility. The greater the use in the Kingdom the greater the crucible to prepare the right foundation. Some of God's greatest crucibles are found in the workplace where we live every day: the employee who betrays our trust, the client who refuses to pay, the vendor who falls short of our expectations.\\
\\
\noindent Each of these is a test from God to find out how we will respond. What tests are being brought your way today? His grace has been provided that we might pass the tests that He brings before us. Should we fail, we need not fear. His grace is sufficient for this as well. Ask God for the grace to walk with Him in whatever tests He has placed before you this day. He is able to accomplish what He wants for you.

\index[DEVOTIONAL]{TGIF1!Os Hillman (The Purpose of Crucibles) - Proverbs 17:3!2022/01/19}


