\chapter{Deuteronomy 31}


\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{MOSES' LAST NEGATIVE SERMON}}\\ (Deuteronomy 31:1-30) \begin{compactenum}[I.][8]
    \item The \textbf{Approaching Situation}  \index[scripture]{Deuteronomy!Deu 31:04}(Deu 31:4)
    \item \textbf{Appointed Success}  \index[scripture]{Deuteronomy!Deu 31:05}(Deu 31:5)
    \item An \textbf{Available Successor}  \index[scripture]{Deuteronomy!Deu 31:07}(Deu 31:7)
    \item \textbf{Another Song}  \index[scripture]{Deuteronomy!Deu 31:19}\index[scripture]{Deuteronomy!Deu 31:21}\index[scripture]{Deuteronomy!Deu 31:22}\index[scripture]{Deuteronomy!Deu 31:30}(Deu 31:19, 21, 22, 30)
    \item An \textbf{Appropriate Speech}  \index[scripture]{Deuteronomy!Deu 31:26--30}(Deu 31:26--30)
    \item An \textbf{Absolute Standard}  \index[scripture]{Deuteronomy!Deu 31:26}(Deu 31:26)
    \item \textbf{Abundant Sin}  \index[scripture]{Deuteronomy!Deu 31:27}(Deu 31:27)
\end{compactenum}}

\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://www.audioverse.org/english/audiobibles/books/ENGKJV/O/Deut/1}{\textcolor[cmyk]{0.99998,1,0,0}{Deuteronomy Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And Moses went and spake these words unto all Israel.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} said unto them, I \emph{am} an hundred and twenty years old this day; I can no more go out and come in: also the LORD hath said unto me, Thou shalt not go over this Jordan.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{The LORD thy God, \fcolorbox{bone}{bone}{he} will go over before thee, \emph{and} \fcolorbox{bone}{bone}{he} will destroy these nations from before thee, and thou shalt possess them: \emph{and} Joshua, \fcolorbox{bone}{bone}{he} \fcolorbox{bone}{bone}{shall} go over before thee, as the LORD hath said.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD \fcolorbox{bone}{bone}{shall} do \fcolorbox{bone}{lime}{unto them} as \fcolorbox{bone}{bone}{he} did  \fcolorbox{bone}{bone}{to} Sihon and  \fcolorbox{bone}{bone}{to} Og, kings of the Amorites, and unto the land of them, whom \fcolorbox{bone}{bone}{he} destroyed.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD \fcolorbox{bone}{bone}{shall} give them up before your face, that ye may do \fcolorbox{bone}{lime}{unto them} according unto all the commandments  \fcolorbox{bone}{bone}{which}  I have commanded you.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{Be strong and of a good courage, fear not, nor be afraid of them: for the LORD thy God, \fcolorbox{bone}{bone}{he} \emph{it} \emph{is} that doth go with thee; \fcolorbox{bone}{bone}{he} will not fail thee, nor forsake thee.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Moses called unto \fcolorbox{bone}{lime}{Joshua}, and said unto him in the sight of all Israel, Be strong and of a good courage: for thou must go with this people unto the land  \fcolorbox{bone}{bone}{which}  the LORD hath sworn unto their fathers  \fcolorbox{bone}{bone}{to} give them; and thou shalt cause them  \fcolorbox{bone}{bone}{to} inherit it.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD, \fcolorbox{bone}{bone}{he} \emph{it} \emph{is} that doth go before thee; \fcolorbox{bone}{bone}{he} will be with thee, \fcolorbox{bone}{bone}{he} will not fail thee, neither forsake thee: fear not, neither be dismayed.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Moses wrote this law, and delivered it unto the priests the sons of Levi,  \fcolorbox{bone}{bone}{which}  bare the ark of the covenant of the LORD, and unto all the elders of Israel.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And Moses commanded them, saying, At the end of \emph{every} seven years, in the solemnity of the year of release, in the feast of tabernacles,}
[11] \textcolor[cmyk]{0.99998,1,0,0}{When all Israel is come  \fcolorbox{bone}{bone}{to} appear before the LORD thy God in the place  \fcolorbox{bone}{bone}{which}  \fcolorbox{bone}{bone}{he} \fcolorbox{bone}{bone}{shall} choose, thou shalt read this law before all Israel in their hearing.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{Gather the people together, men, and women, and children, and thy stranger that \emph{is} within thy gates, that they may hear, and that they may learn, and fear the LORD your God, and observe  \fcolorbox{bone}{bone}{to} do all the words of this law:}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And \emph{that} their children,  \fcolorbox{bone}{bone}{which}  have not known \emph{any} \emph{thing}, may hear, and learn  \fcolorbox{bone}{bone}{to} fear the LORD your God, as long as ye live in the land whither ye go over Jordan  \fcolorbox{bone}{bone}{to} possess it.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said unto Moses, Behold, thy days approach that thou must die: call Joshua, and present yourselves in the tabernacle of the congregation, that I may give him a charge. And Moses and Joshua went, and presented themselves in the tabernacle of the congregation.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD appeared in the tabernacle in a pillar of a cloud: and the pillar of the cloud stood over the door of the tabernacle.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said unto Moses, Behold, thou shalt sleep with thy fathers; and this people will rise up, and go a whoring after the gods of the strangers of the land, whither they go \emph{to} \emph{be} among them, and will forsake me, and break my covenant  \fcolorbox{bone}{bone}{which}  I have made with them.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Then my anger \fcolorbox{bone}{bone}{shall} be kindled against them in that day, and I will forsake them, and I will hide my face from them, and they \fcolorbox{bone}{bone}{shall} be devoured, and many evils and troubles \fcolorbox{bone}{bone}{shall} befall them; so that they will say in that day, Are not these evils come upon us, because our God \emph{is} not among us?}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And I will surely hide my face in that day for all the evils  \fcolorbox{bone}{bone}{which}  they \fcolorbox{bone}{bone}{shall} have wrought, in that they are turned unto other gods.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{Now therefore write ye this \fcolorbox{bone}{lime}{song} for you, and teach it the children of Israel: put it in their mouths, that this song may be a witness for me against the children of Israel.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{For when I \fcolorbox{bone}{bone}{shall} have brought them into the land  \fcolorbox{bone}{bone}{which}  I sware unto their fathers, that floweth with milk and honey; and they \fcolorbox{bone}{bone}{shall} have eaten and filled themselves, and waxen fat; then will they turn unto other gods, and serve them, and provoke me, and break my covenant.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And it \fcolorbox{bone}{bone}{shall} come  \fcolorbox{bone}{bone}{to} pass, when many evils and troubles are befallen them, that this \fcolorbox{bone}{lime}{song} \fcolorbox{bone}{bone}{shall} testify against them as a witness; for it \fcolorbox{bone}{bone}{shall} not be forgotten out of the mouths of their seed: for I know their imagination  \fcolorbox{bone}{bone}{which}  they go about, even now, before I have brought them into the land  \fcolorbox{bone}{bone}{which}  I sware.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Moses therefore wrote this \fcolorbox{bone}{lime}{song} the same day, and taught it the children of Israel.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} gave Joshua the son of Nun a charge, and said, Be strong and of a good courage: for thou shalt bring the children of Israel into the land  \fcolorbox{bone}{bone}{which}  I sware unto them: and I will be with thee.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And it came to pass, when Moses had made an end of writing the words of this law in a book, until they were finished,}
[25] \textcolor[cmyk]{0.99998,1,0,0}{That Moses commanded the Levites,  \fcolorbox{bone}{bone}{which}  bare the ark of the covenant of the LORD, saying,}
[26] \textcolor[cmyk]{0.99998,1,0,0}{Take this book of the law, and put it in the side of the ark of the covenant of the LORD your God, that it may be there for a \fcolorbox{bone}{lime}{witness} against thee.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{For I know thy \fcolorbox{bone}{lime}{rebellion}, and thy stiff neck: behold, while I am yet alive with you this day, ye have been rebellious against the LORD; and how much more after my death?}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Gather unto me all the elders of your tribes, and your officers, that I may speak these words in their ears, and call heaven and earth  \fcolorbox{bone}{bone}{to} record against them.}
[29] \textcolor[cmyk]{0.99998,1,0,0}{For I know that after my death ye will utterly corrupt \emph{yourselves}, and turn aside from the way  \fcolorbox{bone}{bone}{which}  I have commanded you; and evil will befall you in the latter days; because ye will do evil in the sight of the LORD,  \fcolorbox{bone}{bone}{to} provoke him  \fcolorbox{bone}{bone}{to} anger through the work of your hands.}
[30] \textcolor[cmyk]{0.99998,1,0,0}{And Moses spake in the ears of all the congregation of Israel the words of this \fcolorbox{bone}{lime}{song}, until they were ended.}