\chapter{Deuteronomy 33}






\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{THE LORD RETURNS}}\\ (Deuteronomy 33:1-29) \begin{compactenum}[I.][8]
    \item A \textbf{Mistaken Interpretation} \index[scripture]{Deuteronomy!Deu 33:01--02}(Deu 33:1--2) The verses speak of the second advent and note of the exodus from Egypt
    \item A \textbf{Mighty Return} \index[scripture]{Deuteronomy!Deu 33:02}(Deu 33:2)
    \item The \textbf{Millennial Inheritance} \index[scripture]{Deuteronomy!Deu 33:04}(Deu 33:4)
    \item A \textbf{Massive Gathering} \index[scripture]{Deuteronomy!Deu 33:05}(Deu 33:5)
    \item \textbf{Mercy \fcolorbox{bone}{bone}{for} Reuben} \index[scripture]{Deuteronomy!Deu 33:06}(Deu 33:6) (note 13 words in verse)
    \item A \textbf{Mountain of Gratitude} \index[scripture]{Deuteronomy!Deu 33:19}\index[scripture]{Isaiah!Isaiah 02:02}(Deu 33:19, Isa 2:2) The mountain of the Lord in the Millennium with commemorative sacrifices
    \item A \textbf{Magnificent Guardian} \index[scripture]{Deuteronomy!Deu 33:28}(Deu 33:28) 
\end{compactenum}}






\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/deuteronomy_33.html}{\textcolor[cmyk]{0.99998,1,0,0}{Deuteronomy 33 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And this \emph{is} the blessing, wherewith Moses the man of God blessed the children of Israel before his death.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And he said, The LORD \fcolorbox{bone}{lime}{came from Sinai}, and rose up from Seir unto them; he shined forth from mount Paran, and he came \fcolorbox{bone}{lime}{with ten thousands of saints}: from his right hand \emph{went} a fiery law \fcolorbox{bone}{bone}{for} them.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{Yea, he loved the people; all his saints \emph{are} in thy hand: and they sat down at thy feet; \emph{every} \emph{one} shall receive of thy words.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Moses commanded us a law, \emph{even} the \fcolorbox{bone}{lime}{inheritance} of the congregation of Jacob.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And he was king in Jeshurun, when the heads of the people \emph{and} the tribes of Israel were \fcolorbox{bone}{lime}{gathered} together.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{lime}{Let Reuben live}, and not die; and let \emph{not} his men be few.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And this \emph{is} \emph{the} \emph{blessing} of Judah: and he said, Hear, LORD, the voice of Judah, and bring him unto his people: let his hands be sufficient \fcolorbox{bone}{bone}{for} him; and be thou an help \emph{to} \emph{him} from his enemies.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Levi he said, \emph{Let} thy Thummim and thy Urim \emph{be} with thy holy one, whom thou didst prove at Massah, \emph{and} \emph{with} whom thou didst strive at the waters of Meribah;}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Who said unto his father and to his mother, I have not seen him; neither did he acknowledge his brethren, nor knew his own children: \fcolorbox{bone}{bone}{for} they have observed thy word, and kept thy covenant.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{They shall teach Jacob thy judgments, and Israel thy law: they shall put incense before thee, and whole burnt sacrifice upon thine altar.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Bless, LORD, his substance, and accept the work of his hands: smite through the loins of them that rise against him, and of them that hate him, that they rise not again.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\emph{And} of Benjamin he said, The beloved of the LORD shall dwell in safety by him; \emph{and} \emph{the} \emph{LORD} shall cover him all the day long, and he shall dwell between his shoulders.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Joseph he said, Blessed of the LORD \emph{be} his land, \fcolorbox{bone}{bone}{for} the precious things of heaven, \fcolorbox{bone}{bone}{for} the dew, and \fcolorbox{bone}{bone}{for} the deep that coucheth beneath,}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{for} the precious fruits \emph{brought} \emph{forth} by the sun, and \fcolorbox{bone}{bone}{for} the precious things put forth by the moon,}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{for} the chief things of the ancient mountains, and \fcolorbox{bone}{bone}{for} the precious things of the lasting hills,}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{for} the precious things of the earth and fulness thereof, and \emph{for} the good will of him that dwelt in the bush: let \emph{the} \emph{blessing} come upon the head of Joseph, and upon the top of the head of him \emph{that} \emph{was} separated from his brethren.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{His glory \emph{is} \emph{like} the firstling of his bullock, and his horns \emph{are} \emph{like} the horns of unicorns: with them he shall push the people together to the ends of the earth: and they \emph{are} the ten thousands of Ephraim, and they \emph{are} the thousands of Manasseh.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Zebulun he said, Rejoice, Zebulun, in thy going out; and, Issachar, in thy tents.}
[19] \textcolor[cmyk]{0.99998,1,0,0}{They shall call the people unto the \fcolorbox{bone}{lime}{mountain}; there they shall offer sacrifices of \fcolorbox{bone}{MYGOLD}{righteousness}: \fcolorbox{bone}{bone}{for} they shall suck \emph{of} the abundance of the seas, and \emph{of} treasures hid in the sand.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Gad he said, Blessed \emph{be} he that enlargeth Gad: he dwelleth as a lion, and teareth the arm with the crown of the head.}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And he provided the first part \fcolorbox{bone}{bone}{for} himself, because there, \emph{in} a portion of the lawgiver, \emph{was} \emph{he} seated; and he came with the heads of the people, he executed the justice of the LORD, and his judgments with Israel.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Dan he said, Dan \emph{is} a lion's whelp: he shall leap from Bashan.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Naphtali he said, O Naphtali, satisfied with favour, and full with the blessing of the LORD: possess thou the west and the south.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And of Asher he said, \emph{Let} Asher \emph{be} blessed with children; let him be acceptable to his brethren, and let him dip his foot in oil.}
[25] \textcolor[cmyk]{0.99998,1,0,0}{Thy shoes \emph{shall} \emph{be} iron and brass; and as thy days, \emph{so} \emph{shall} thy strength \emph{be}.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\emph{There} \emph{is} none like unto the God of Jeshurun, \emph{who} rideth upon the heaven in thy help, and in his excellency on the sky.}
[27] \textcolor[cmyk]{0.99998,1,0,0}{The eternal God \emph{is} \emph{thy} refuge, and underneath \emph{are} the everlasting arms: and he shall thrust out the enemy from before thee; and shall say, Destroy \emph{them}.}
[28] \textcolor[cmyk]{0.99998,1,0,0}{Israel then shall \fcolorbox{bone}{lime}{dwell in safety alone}: the fountain of Jacob \emph{shall} \emph{be} upon a land of corn and wine; also his heavens shall drop down dew.}
[29] \textcolor[cmyk]{0.99998,1,0,0}{Happy \emph{art} thou, O Israel: who \emph{is} like unto thee, O people saved by the LORD, the shield of thy help, and who \emph{is} the sword of thy excellency! and thine enemies shall be found liars unto thee; and thou shalt tread upon their high places.}

