\chapter{Deuteronomy 34}



\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{MOSES DIES}}\\ (Deuteronomy 34:1-12) \begin{compactenum}[I.][8]
    \item \textbf{Death in the Wilderness} \index[scripture]{Deuteronomy!Deu 34:05} (Deu 34:5)
    \item \textbf{Divorce for the Woman} \index[scripture]{Deuteronomy!Deu 34:05} (Deu 34:5)
    \item No \textbf{Diminishing of the Weight} (of the Law) \index[scripture]{Deuteronomy!Deu 34:07} (Deu 34:7)
    \item \textbf{Distress and Weeping} \index[scripture]{Deuteronomy!Deu 34:08} (Deu 34:8)
    \item \textbf{Denial and Wickedness} seen in the gospels -- Jews trying to hang on to a dead religion and their Law. All the Law did was condemn them, but they were using it for self-righteousness %\index[scripture]{Deuteronomy!Deuteronomy 34:05}(Deuteronomy 34:5)
    \item A \textbf{Deliverer in the Wings} \index[scripture]{Deuteronomy!Deu 34:09} (Deu 34:9)
    \item The \textbf{Distinguished One} -- the Prophet like unto Moses will be Jesus \index[scripture]{Deuteronomy!Deu 34:10} (Deu 34:10)
\end{compactenum}}






\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/deuteronomy_34.html}{\textcolor[cmyk]{0.99998,1,0,0}{Deuteronomy 34 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And Moses went up from the plains of Moab unto the mountain of Nebo, to the top of Pisgah, that \emph{is} over against Jericho. And the LORD shewed him all the land of Gilead, unto Dan,}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And all Naphtali, and the land of Ephraim, and Manasseh, and all the land of Judah, unto the utmost sea,}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And the south, and the plain of the valley of Jericho, the city of palm trees, unto Zoar.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said unto him, This \emph{is} the land which I sware unto Abraham, unto Isaac, and unto Jacob, saying, I will give it unto thy seed: I have caused thee to see \emph{it} with thine eyes, but thou shalt not go over thither.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{So Moses the servant of the LORD  \fcolorbox{bone}{lime}{died} there in the land of Moab, according to the word of the LORD.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And he buried him in a valley in the land of Moab, over against Beth-peor: but no man knoweth of his sepulchre unto this day.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Moses \emph{was} an hundred and twenty years old when he died: his eye was  \fcolorbox{bone}{lime}{not dim}, nor his natural force abated.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And the children of Israel wept for Moses in the plains of Moab thirty days: so the days of  \fcolorbox{bone}{lime}{weeping} \emph{and} mourning for Moses were ended.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Joshua the son of Nun was full of the spirit of wisdom; for Moses had laid his hands upon him: and the children of Israel hearkened unto him, and did  \fcolorbox{bone}{lime}{as the LORD commanded Moses}.}\footnote{\textbf{Numbers 27:1-23} - And the LORD said unto Moses, Take thee Joshua the son of Nun, a man in whom is the spirit, and lay thine hand upon him; [19] And set him before Eleazar the priest, and before all the congregation; and give him a charge in their sight. [20] And thou shalt put some of thine honour upon him, that all the congregation of the children of Israel may be obedient. [21] And he shall stand before Eleazar the priest, who shall ask counsel for him after the judgment of Urim before the LORD: at his word shall they go out, and at his word they shall come in, both he, and all the children of Israel with him, even all the congregation. [22] And Moses did as the LORD commanded him: and he took Joshua, and set him before Eleazar the priest, and before all the congregation: [23] And he laid his hands upon him, and gave him a charge, as the LORD commanded by the hand of Moses.}\footnote{\textbf{Joshua 1:16-18} - And they answered Joshua, saying, All that thou commandest us we will do, and whithersoever thou sendest us, we will go. [17] According as we hearkened unto Moses in all things, so will we hearken unto thee: only the LORD thy God be with thee, as he was with Moses. [18] Whosoever he be that doth rebel against thy commandment, and will not hearken unto thy words in all that thou commandest him, he shall be put to death: only be strong and of a good courage.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And there arose not a prophet since in Israel  \fcolorbox{bone}{lime}{like unto Moses}, whom the LORD knew face to face,}\footnote{\textbf{Deuteronomy 18:15} - The LORD thy God will raise up unto thee a Prophet from the midst of thee, of thy brethren, like unto me; unto him ye shall hearken;}\footnote{\textbf{Acts 3:22-23} - or Moses truly said unto the fathers, A prophet shall the Lord your God raise up unto you of your brethren, like unto me; him shall ye hear in all things whatsoever he shall say unto you. [23] And it shall come to pass, that every soul, which will not hear that prophet, shall be destroyed from among the people.}\footnote{\textbf{Acts 7:37-38} - This is that Moses, which said unto the children of Israel, A prophet shall the Lord your God raise up unto you of your brethren, like unto me; him shall ye hear. [38] This is he, that was in the church in the wilderness with the angel which spake to him in the mount Sina, and with our fathers: who received the lively oracles to give unto us:}
[11] \textcolor[cmyk]{0.99998,1,0,0}{In all the signs and the wonders, which the LORD sent him to do in the land of Egypt to Pharaoh, and to all his servants, and to all his land,}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And in all that mighty hand, and in all the great terror which Moses shewed in the sight of all Israel.}