\chapter{Psalm 74}
\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\textcolor[rgb]{0.00,0.00,1.00}{O God, why hast thou cast \emph{us} off for ever? \emph{why} doth thine anger \fcolorbox{blue}{yellow}{smoke} against the \fcolorbox{blue}{yellow}{sheep} of thy pasture?}\index[AWIP]{O!Psalms!Psa 074:001}\index[AWIP]{God!Psalms!Psa 074:001}\index[AWIP]{why!Psalms!Psa 074:001}\index[AWIP]{hast!Psalms!Psa 074:001}\index[AWIP]{thou!Psalms!Psa 074:001}\index[AWIP]{cast!Psalms!Psa 074:001}\index[AWIP]{\emph{us}!Psalms!Psa 074:001}\index[AWIP]{off!Psalms!Psa 074:001}\index[AWIP]{for!Psalms!Psa 074:001}\index[AWIP]{ever!Psalms!Psa 074:001}\index[AWIP]{\emph{why}!Psalms!Psa 074:001}\index[AWIP]{doth!Psalms!Psa 074:001}\index[AWIP]{thine!Psalms!Psa 074:001}\index[AWIP]{anger!Psalms!Psa 074:001}\index[AWIP]{smoke!Psalms!Psa 074:001}\index[AWIP]{against!Psalms!Psa 074:001}\index[AWIP]{the!Psalms!Psa 074:001}\index[AWIP]{sheep!Psalms!Psa 074:001}\index[AWIP]{of!Psalms!Psa 074:001}\index[AWIP]{thy!Psalms!Psa 074:001}\index[AWIP]{pasture!Psalms!Psa 074:001}\index[NWIV]{21!Psalms!Psa 074:001}\index[PNIP]{God!Psalms!Psa 074:001}\footnote{[RUCKMAN] Nothing is difficult in the matter of placement for the Psalm; it is somewhere past 1993. Asaph is a prophet. Although historically you might place the Psalm on Nebuchadnezzar in 586 B.C., it would still come to nothing, because Asaph died at least three hundred years before Nebuchadnezzar was born.  When the King James translators adopted the word “synagogues” in verse 8, they blew every “good, godly, dedicated, recognized, qualified authority” into the Bermuda Triangle. This gave any reader an advanced revelation, in 1611, which had to be eradicated by every translator, revisor, scholar, teacher, professor, and linguist since then. They all erased it. Not even Elmer Towns, Curtis Hutson, James Combs, Truman Dollar, A. V. Henderson, or Jerry Falwell would tolerate such a revelation; they removed it from the NKJV and left you with “Dead Duck Otherism”--a heresy taught at BJU. “O God, why hast thou cast us off for ever?” This is Lamentations 5:20--22, to the letter, which pictures what will take place very soon--if our calendar is correct. But “God hath not cast away his people which he foreknew” (Rom. 11:2). The remnant (Joel 2:32) will be saved in its entirety (Romans 11:26). Here, we find five similitudes of the church which do not apply doctrinally to the church, thereby leading every postmillennial and amillennial expositor on seven continents astray.
\begin{compactenum}
\item Sheep (vs. 1).
\item Congregation (vs. 2).
\item A purchased possession (vs. 2).
\item Inheritance (vs. 2).
\item The redeemed (vs. 2).
\end{compactenum}
Doctrinally, the inheritance is that of Jeremiah 52:3, 52:13--15, and Deuteronomy 32:9, which places the passage right into Daniel’s Seventieth Week where Kroll (Liberty University) can’t find it (see below). Verse 3 should be compared to Isaiah 63:18. Asaph reaches out beyond Nebuchadnezzar and views the temple as rebuilt and burned (vs. 2) so that God no longer dwells in it, and the synagogues that took its place between 400 B.C. and A.D. 2002 are also burned to the ground. The “Champions for Christ,” at Falwell’s, can do nothing with the passage. The ravages of Nebuchadnezzar and Titus (before and after the birth of Christ) are only preludes to the opera. The opera will take place in the next few years, and there will not be one SYNAGOGUE--and I don’t mean “meeting place”—left in the land of Israel. “The rod of thine inheritance.” It began with a rod (see Exod. 4:2–4), and a  shepherd’s rod at that. The sheep are the sheep of Isaiah 63:11, and Jacob was the shepherd who used a rod to increase this flock (Gen. 30:37–42). “Lift up thy feet.” In the Bible, eyes, hands, and voices are “lifted” up. God is asked to lift up His feet, and He does (see Ps. 7:6 and 94:2). The idea is to take a step (or “kick”—see Ps. 60:8) in the right direction. The temple is desolated (vs. 3), so all of the scholars missed all the prophetic references; they are in Daniel 9:27, 11:31, and Matthew 24:15. The NIV (with its corrupt ancestors—the RV, ASV, NASV, RSV, and NRSV) took the word clean out (“desolations”) so you would lose the revelation given in the chain references of 1611. \cite{Ruckman1992Psalms} }
[2] \textcolor[rgb]{0.00,0.00,1.00}{Remember thy congregation, \emph{which} thou hast purchased of old; the rod of thine inheritance, \emph{which} thou hast redeemed; this mount Zion, wherein thou hast dwelt.}
[3] \textcolor[rgb]{0.00,0.00,1.00}{Lift up thy feet unto the perpetual desolations; \emph{even} all \emph{that} the enemy hath done wickedly in the \fcolorbox{blue}{yellow}{sanctuary}.}\footnote{The phrase ``perpetual desolations'' is foudn 4 times in the AV: (1) Psalm 74:3, (2) Jeremiah 25:9, (3) Jeremiah 25:12, and (4) Ezekiel 35:9. Specifically it refers to the the destruction of Babylon after the 70  year captivity of the Jews. In Ezekiel 35:2, they boast of the desolation they have brought upon Israel -- God will ``do unto others, as they have done unto Israel!''. \textbf{Ezekiel 35:9--15}: I will make thee perpetual desolations, and thy cities shall not return: and ye shall know that I am the LORD. [10] Because thou hast said, These two nations and these two countries shall be mine, and we will possess it; whereas the LORD was there: [11] Therefore, as I live, saith the Lord GOD, I will even do according to thine anger, and according to thine envy which thou hast used out of thy hatred against them; and I will make myself known among them, when I have judged thee. [12] And thou shalt know that I am the LORD, and that I have heard all thy blasphemies which thou hast spoken against the mountains of Israel, saying, They are laid desolate, they are given us to consume. [13] Thus with your mouth ye have boasted against me, and have multiplied your words against me: I have heard them. [14] Thus saith the Lord GOD; When the whole earth rejoiceth, I will make thee desolate. [15] As thou didst rejoice at the inheritance of the house of Israel, because it was desolate, so will I do unto thee: thou shalt be desolate, O mount Seir, and all Idumea, even all of it: and they shall know that I am the LORD.}
[4] \textcolor[rgb]{0.00,0.00,1.00}{Thine enemies roar in the midst of thy congregations; they set up their ensigns \emph{for} \fcolorbox{blue}{yellow}{signs}.}\index[AWIP]{Thine!Psalms!Psa 074:004}\index[AWIP]{enemies!Psalms!Psa 074:004}\index[AWIP]{roar!Psalms!Psa 074:004}\index[AWIP]{in!Psalms!Psa 074:004}\index[AWIP]{the!Psalms!Psa 074:004}\index[AWIP]{midst!Psalms!Psa 074:004}\index[AWIP]{of!Psalms!Psa 074:004}\index[AWIP]{thy!Psalms!Psa 074:004}\index[AWIP]{congregations!Psalms!Psa 074:004}\index[AWIP]{they!Psalms!Psa 074:004}\index[AWIP]{set!Psalms!Psa 074:004}\index[AWIP]{up!Psalms!Psa 074:004}\index[AWIP]{their!Psalms!Psa 074:004}\index[AWIP]{ensigns!Psalms!Psa 074:004}\index[AWIP]{\emph{for}!Psalms!Psa 074:004}\index[AWIP]{signs!Psalms!Psa 074:004}\index[NWIV]{16!Psalms!Psa 074:004}\index[PNIP]{Thine!Psalms!Psa 074:004}\footnote{[RUCKMAN] “Thine enemies roar in the midst” of the congregation (singular, not plural), if you are stupid enough to correct the text like Jamieson, Fausset, and Brown. Having brought their readers down to their level of ignorance, they are aped by the translators of the NIV, ASV, RV, RSV, NASV, and the NRSV, who convert “congregations” into the temple itself, or “the holy place.” Stupidity is infectious. Jerry Falwell is drawn away with the “feeble minded” and the dissimulation and says “meeting place” (NKJV). Dead Duck Otherism. There is only ONE English Bible that reveals the truth; this means if you ever get the whole truth, you will be called a “heretic” by those who turn up their snotty noses at “King James Onlyism.”  Having rejected the wording of verse 8--due to pressure by Satan--all of the modern perverters and corrupters of Scripture must now get rid of the plural in verse 4, where it deals with the congregations that were meeting in synagogues. They do it, and they do it with one consent, hoping that fear of “King James Onlyism” will sidetrack the reader into thinking they know what they are doing. (“Thank you, Mario, but our princess is in another castle!”) The “enemies” broke up the congregations (1933–1945) and set up “ensigns”—in Hitler’s case swastikas and in Titus’ case eagles—and before Satan is through, they will be Chi Rho (P) “crosses” like Constantine saw. The enemies “roar” because they are like lions (Rev. 9:17) and their father is a lion (1 Pet. 5:8). Kroll (Liberty University) throws the whole passage (vss. 2--3, 5--8) back five centuries before the birth of Christ. His prophetic view (having “the spirit of prophecy,” Rev. 19:10) goes out almost six inches beyond his nose. The destruction of the temple--it takes place THREE times (Nebuchadnezzar, Titus, the Son of Perdition)--is described, although it had not been built when Asaph writes. The builders of the temple had hewn the trees in Lebanon (1 Kings 5:6--9), but now the hewers arrive who break down their work (Jer. 39:8). They set fire to the sanctuary (2 Kings 25:9) and level the temple (vs. 7). This did not happen literally until A.D. 70 (Matt. 24:2). Still, Kroll dumps it backwards five centuries. Jamieson, Fausset, and Brown hastily run you to Lamentations 2:2 where the reference is to “strong holds” and “habitations”—not to the temple—hoping you will think the passage was fulfilled in 586 B.C. instead of A.D. 70. Nice try. We don’t buy it. Once they begin to mess with that Book we are on “red alert.”\cite{Ruckman1992Psalms}}
[5] \textcolor[rgb]{0.00,0.00,1.00}{\emph{A} \emph{man} was famous according as he had lifted up axes upon the thick trees.}\index[AWIP]{\emph{A}!Psalms!Psa 074:005}\index[AWIP]{\emph{man}!Psalms!Psa 074:005}\index[AWIP]{was!Psalms!Psa 074:005}\index[AWIP]{famous!Psalms!Psa 074:005}\index[AWIP]{according!Psalms!Psa 074:005}\index[AWIP]{as!Psalms!Psa 074:005}\index[AWIP]{he!Psalms!Psa 074:005}\index[AWIP]{had!Psalms!Psa 074:005}\index[AWIP]{lifted!Psalms!Psa 074:005}\index[AWIP]{up!Psalms!Psa 074:005}\index[AWIP]{axes!Psalms!Psa 074:005}\index[AWIP]{upon!Psalms!Psa 074:005}\index[AWIP]{the!Psalms!Psa 074:005}\index[AWIP]{thick!Psalms!Psa 074:005}\index[AWIP]{trees!Psalms!Psa 074:005}\index[NWIV]{15!Psalms!Psa 074:005}
[6] \textcolor[rgb]{0.00,0.00,1.00}{But now they break down the carved work thereof at once with axes and hammers.}\index[AWIP]{But!Psalms!Psa 074:006}\index[AWIP]{now!Psalms!Psa 074:006}\index[AWIP]{they!Psalms!Psa 074:006}\index[AWIP]{break!Psalms!Psa 074:006}\index[AWIP]{down!Psalms!Psa 074:006}\index[AWIP]{the!Psalms!Psa 074:006}\index[AWIP]{carved!Psalms!Psa 074:006}\index[AWIP]{work!Psalms!Psa 074:006}\index[AWIP]{thereof!Psalms!Psa 074:006}\index[AWIP]{at!Psalms!Psa 074:006}\index[AWIP]{once!Psalms!Psa 074:006}\index[AWIP]{with!Psalms!Psa 074:006}\index[AWIP]{axes!Psalms!Psa 074:006}\index[AWIP]{and!Psalms!Psa 074:006}\index[AWIP]{hammers!Psalms!Psa 074:006}\index[NWIV]{15!Psalms!Psa 074:006}
[7] \textcolor[rgb]{0.00,0.00,1.00}{They have cast fire into thy sanctuary, they have defiled \emph{by} \emph{casting} \emph{down} the dwelling place of thy name to the ground.}\index[AWIP]{They!Psalms!Psa 074:007}\index[AWIP]{have!Psalms!Psa 074:007}\index[AWIP]{cast!Psalms!Psa 074:007}\index[AWIP]{fire!Psalms!Psa 074:007}\index[AWIP]{into!Psalms!Psa 074:007}\index[AWIP]{thy!Psalms!Psa 074:007}\index[AWIP]{sanctuary!Psalms!Psa 074:007}\index[AWIP]{they!Psalms!Psa 074:007}\index[AWIP]{have!Psalms!Psa 074:007 (2)}\index[AWIP]{defiled!Psalms!Psa 074:007}\index[AWIP]{\emph{by}!Psalms!Psa 074:007}\index[AWIP]{\emph{casting}!Psalms!Psa 074:007}\index[AWIP]{\emph{down}!Psalms!Psa 074:007}\index[AWIP]{the!Psalms!Psa 074:007}\index[AWIP]{dwelling!Psalms!Psa 074:007}\index[AWIP]{place!Psalms!Psa 074:007}\index[AWIP]{of!Psalms!Psa 074:007}\index[AWIP]{thy!Psalms!Psa 074:007 (2)}\index[AWIP]{name!Psalms!Psa 074:007}\index[AWIP]{to!Psalms!Psa 074:007}\index[AWIP]{the!Psalms!Psa 074:007 (2)}\index[AWIP]{ground!Psalms!Psa 074:007}\index[NWIV]{22!Psalms!Psa 074:007}
[8] \textcolor[rgb]{0.00,0.00,1.00}{They said in their hearts, Let us destroy them together: they have burned up all the synagogues of God in the land.}\index[AWIP]{They!Psalms!Psa 074:008}\index[AWIP]{said!Psalms!Psa 074:008}\index[AWIP]{in!Psalms!Psa 074:008}\index[AWIP]{their!Psalms!Psa 074:008}\index[AWIP]{hearts!Psalms!Psa 074:008}\index[AWIP]{Let!Psalms!Psa 074:008}\index[AWIP]{us!Psalms!Psa 074:008}\index[AWIP]{destroy!Psalms!Psa 074:008}\index[AWIP]{them!Psalms!Psa 074:008}\index[AWIP]{together!Psalms!Psa 074:008}\index[AWIP]{they!Psalms!Psa 074:008}\index[AWIP]{have!Psalms!Psa 074:008}\index[AWIP]{burned!Psalms!Psa 074:008}\index[AWIP]{up!Psalms!Psa 074:008}\index[AWIP]{all!Psalms!Psa 074:008}\index[AWIP]{the!Psalms!Psa 074:008}\index[AWIP]{synagogues!Psalms!Psa 074:008}\index[AWIP]{of!Psalms!Psa 074:008}\index[AWIP]{God!Psalms!Psa 074:008}\index[AWIP]{in!Psalms!Psa 074:008 (2)}\index[AWIP]{the!Psalms!Psa 074:008 (2)}\index[AWIP]{land!Psalms!Psa 074:008}\index[NWIV]{22!Psalms!Psa 074:008}\index[PNIP]{God!Psalms!Psa 074:008}\footnote{[RUCKMAN] o go if you are an apostate Fundamentalist like Bob Jones IV, Kroll, Sumner, Kutilek, Curtis Hutson, Afman, Martin, Price, or Farstad. It will have  to go if you are a dead orthodox Conservativelike the faculties and staffs of Dallas Theological Seminary, Cedarville, Grace Theological Seminary, Wheaton, Moody, Fuller, and Pacific Coast Bible College. Naturally the Liberals agree with the Fundamentalists; all of the NCC publications throw it out with the blessing of Bishop Pike, Bishop Oxnam, Harry Emerson Fosdick, Dean Luther Weigle, and Leslie Weatherhead, and company. 1. NKJV: “meeting places.” 2. RSV and NRSV: “meeting places.” 3. Living Bible: “assembly places.” 4. NIV: “every place.” 5. Baethgen and Duhm: “houses.” 6. New English Bible: “holy places.” Anything but the text. Anything but the word of God. Anything but the Scriptures. Anything but the Holy Spirit. Anything but the Holy Bible: ANYTHING. The Nicolaitans in the Scholar’s Union simply will not tolerate divine revelation. They themselves must be the oracles for the Sphinx. Charles Haddon Spurgeon: “There is no allusion to places called synagogues” (p. 274). I’ll tell you one better than that, Charlie: “evil communications corrupt good manners” (1 Cor. 15:33). Lie down with the dogs get up with the fleas. Now, watch that old .66 caliber, black backed, anti aircraft cannon blast the Scholars Union out of the sky and leave nothing but scraps on the landscape small enough to sweep up in a vacuum cleaner.\cite{Ruckman1992Psalms}}
[9] \textcolor[rgb]{0.00,0.00,1.00}{We see not our signs: \emph{there} \emph{is} no more any prophet: neither \emph{is} \emph{there} among us any that knoweth how long.}\index[AWIP]{We!Psalms!Psa 074:009}\index[AWIP]{see!Psalms!Psa 074:009}\index[AWIP]{not!Psalms!Psa 074:009}\index[AWIP]{our!Psalms!Psa 074:009}\index[AWIP]{signs!Psalms!Psa 074:009}\index[AWIP]{\emph{there}!Psalms!Psa 074:009}\index[AWIP]{\emph{is}!Psalms!Psa 074:009}\index[AWIP]{no!Psalms!Psa 074:009}\index[AWIP]{more!Psalms!Psa 074:009}\index[AWIP]{any!Psalms!Psa 074:009}\index[AWIP]{prophet!Psalms!Psa 074:009}\index[AWIP]{neither!Psalms!Psa 074:009}\index[AWIP]{\emph{is}!Psalms!Psa 074:009 (2)}\index[AWIP]{\emph{there}!Psalms!Psa 074:009 (2)}\index[AWIP]{among!Psalms!Psa 074:009}\index[AWIP]{us!Psalms!Psa 074:009}\index[AWIP]{any!Psalms!Psa 074:009 (2)}\index[AWIP]{that!Psalms!Psa 074:009}\index[AWIP]{knoweth!Psalms!Psa 074:009}\index[AWIP]{how!Psalms!Psa 074:009}\index[AWIP]{long!Psalms!Psa 074:009}\index[NWIV]{21!Psalms!Psa 074:009}\footnote{[RUCKMAN] Verse 9 locks the criminals in the slammer after safely “securing” their handcuffs and foot chains. You see, the signs did not disappear from Israel until after Titus had destroyed the temple in A.D. 70. “The signs of an apostle” (2 Cor. 12:12) were there as long as the “Acts of the Apostles” were being “enacted.” John is still alive in A.D. 90. “There is no more any prophet”? John the Baptist shows up long after Nebuchadnezzar destroys the sanctuary. Ezekiel prophesies while it is being destroyed, and Daniel prophesies immediately after it is destroyed. Verse 9 lands you into 2002 plus.\cite{Ruckman1992Psalms}}
[10] \textcolor[rgb]{0.00,0.00,1.00}{O God, how long shall the adversary reproach? shall the enemy blaspheme thy name for ever?}\index[AWIP]{O!Psalms!Psa 074:010}\index[AWIP]{God!Psalms!Psa 074:010}\index[AWIP]{how!Psalms!Psa 074:010}\index[AWIP]{long!Psalms!Psa 074:010}\index[AWIP]{shall!Psalms!Psa 074:010}\index[AWIP]{the!Psalms!Psa 074:010}\index[AWIP]{adversary!Psalms!Psa 074:010}\index[AWIP]{reproach!Psalms!Psa 074:010}\index[AWIP]{shall!Psalms!Psa 074:010 (2)}\index[AWIP]{the!Psalms!Psa 074:010 (2)}\index[AWIP]{enemy!Psalms!Psa 074:010}\index[AWIP]{blaspheme!Psalms!Psa 074:010}\index[AWIP]{thy!Psalms!Psa 074:010}\index[AWIP]{name!Psalms!Psa 074:010}\index[AWIP]{for!Psalms!Psa 074:010}\index[AWIP]{ever!Psalms!Psa 074:010}\index[NWIV]{16!Psalms!Psa 074:010}\index[PNIP]{God!Psalms!Psa 074:010}\footnote{[RUCKMAN] It is “the adversary” who reproaches (vs. 10). See Isaiah 50:8 and more especially 1 Peter 5:8. The “adversary” is engaged in blasphemy (vs. 10). See Revelation 13:5--6 and Daniel 11:36. The scholars lost the truth trying to “find the original intent of the original author in the original, verbally inspired, Hebrew original autograph.” Par for the course. The situation is even worse than the Nicolaitans imagined, for in the context, Moses and Elijah have come and gone (see Rev. 11:11--14). When he says “there is no more any prophet,” he is talking for a pitiful handful of Jews in Sela, Petra (see Lam. 5:15--21) who are awaiting total annihilation, after the post-Tribulation rapture. ALL of the commentators--theist, Fundamentalist, Catholic, Liberal, Conservative, Modernist, Neo Evangelical, Orthodox, and Jewish-- miss all the references. Naturally; what else would you expect? There is nothing on this earth (or in hell or heaven) that will mess a Christian scholar up any worse than believing that his final authority in “all matters of faith and practice” is a pile of lost papers nobody ever read. Nothing on this earth--including Marxism, Darwinism, Papalism, or Communism--could keep you from finding the truth anymore than THAT. The very idea itself is so far “off the wall” that you couldn’t get an unsaved man with an I.Q. of 90 to believe it. Bob Jones IV and the “Congress of Fundamentalists” believe it. Funnymentalism.\cite{Ruckman1992Psalms}}
[11] \textcolor[rgb]{0.00,0.00,1.00}{Why withdrawest thou thy hand, even thy right hand? pluck \emph{it} out of thy bosom.}\index[AWIP]{Why!Psalms!Psa 074:011}\index[AWIP]{withdrawest!Psalms!Psa 074:011}\index[AWIP]{thou!Psalms!Psa 074:011}\index[AWIP]{thy!Psalms!Psa 074:011}\index[AWIP]{hand!Psalms!Psa 074:011}\index[AWIP]{even!Psalms!Psa 074:011}\index[AWIP]{thy!Psalms!Psa 074:011 (2)}\index[AWIP]{right!Psalms!Psa 074:011}\index[AWIP]{hand!Psalms!Psa 074:011 (2)}\index[AWIP]{pluck!Psalms!Psa 074:011}\index[AWIP]{\emph{it}!Psalms!Psa 074:011}\index[AWIP]{out!Psalms!Psa 074:011}\index[AWIP]{of!Psalms!Psa 074:011}\index[AWIP]{thy!Psalms!Psa 074:011 (3)}\index[AWIP]{bosom!Psalms!Psa 074:011}\index[NWIV]{15!Psalms!Psa 074:011}\footnote{[RUCKMAN] “Why withdrawest thou thy hand...?” Why have you quit dealing with us? “Pluck it out of thy bosom.” Then it must have been put there before it was “withdrawn.” Moses shows how it was done (Exod. 4:6). God’s right hand typifies the Lord Jesus Christ in Psalm 17:7, 18:35, 20:6, 44:3, 48:10, etc. God is “at rest” while hiding from Israel (Deut. 31:17–18). He is “sleeping”—although this is plainly figurative (see Ps. 121:4)—in the Church Age, as far as Israel is concerned. The picture is a man lying down with his right hand across his chest and tucked into a bathrobe or “pajama top” (see Ps. 78:65 and comments).\cite{Ruckman1992Psalms}}
[12] \textcolor[rgb]{0.00,0.00,1.00}{For God \emph{is} my King of old, working salvation in the midst of the earth.}\index[AWIP]{For!Psalms!Psa 074:012}\index[AWIP]{God!Psalms!Psa 074:012}\index[AWIP]{\emph{is}!Psalms!Psa 074:012}\index[AWIP]{my!Psalms!Psa 074:012}\index[AWIP]{King!Psalms!Psa 074:012}\index[AWIP]{of!Psalms!Psa 074:012}\index[AWIP]{old!Psalms!Psa 074:012}\index[AWIP]{working!Psalms!Psa 074:012}\index[AWIP]{salvation!Psalms!Psa 074:012}\index[AWIP]{in!Psalms!Psa 074:012}\index[AWIP]{the!Psalms!Psa 074:012}\index[AWIP]{midst!Psalms!Psa 074:012}\index[AWIP]{of!Psalms!Psa 074:012 (2)}\index[AWIP]{the!Psalms!Psa 074:012 (2)}\index[AWIP]{earth!Psalms!Psa 074:012}\index[NWIV]{15!Psalms!Psa 074:012}\index[PNIP]{God!Psalms!Psa 074:012}\index[PNIP]{King!Psalms!Psa 074:012}\footnote{[RUCKMAN ] “Why withdrawest thou thy hand...?” Why have you quit dealing with us? “Pluck it out of thy bosom.” Then it must have been put there before it was “withdrawn.” Moses shows how it was done (Exod. 4:6). God’s right hand typifies the Lord Jesus Christ in Psalm 17:7, 18:35, 20:6, 44:3, 48:10, etc. God is “at rest” while hiding from Israel (Deut. 31:17–18). He is “sleeping”-- although this is plainly figurative (see Ps. 121:4)--in the Church Age, as far as Israel is concerned. The picture is a man lying down with his right hand across his chest and tucked into a bathrobe or “pajama top” (see Ps. 78:65 and comments).\cite{Ruckman1992Psalms}}
[13] \textcolor[rgb]{0.00,0.00,1.00}{Thou didst divide the sea by thy \fcolorbox{blue}{yellow}{strength}: thou brakest the heads of the dragons in the waters.}\index[AWIP]{Thou!Psalms!Psa 074:013}\index[AWIP]{didst!Psalms!Psa 074:013}\index[AWIP]{divide!Psalms!Psa 074:013}\index[AWIP]{the!Psalms!Psa 074:013}\index[AWIP]{sea!Psalms!Psa 074:013}\index[AWIP]{by!Psalms!Psa 074:013}\index[AWIP]{thy!Psalms!Psa 074:013}\index[AWIP]{strength!Psalms!Psa 074:013}\index[AWIP]{thou!Psalms!Psa 074:013}\index[AWIP]{brakest!Psalms!Psa 074:013}\index[AWIP]{the!Psalms!Psa 074:013 (2)}\index[AWIP]{heads!Psalms!Psa 074:013}\index[AWIP]{of!Psalms!Psa 074:013}\index[AWIP]{the!Psalms!Psa 074:013 (3)}\index[AWIP]{dragons!Psalms!Psa 074:013}\index[AWIP]{in!Psalms!Psa 074:013}\index[AWIP]{the!Psalms!Psa 074:013 (4)}\index[AWIP]{waters!Psalms!Psa 074:013}\index[NWIV]{18!Psalms!Psa 074:013}\footnote{[RUCKMAN ]You are to believe that these were cobras on the bottom of the Red Sea, if you bought yourself a New King James Version; they translated this Hebrew word as “cobras” in Psalm 91:13. The NIV did the same thing. “The heads of leviathan” fares even worse. The new Bibles all tell you they believe that a crocodile has more than one head! (Scholarship, baby! You’d better believe it; nothing but “recognized” scholarship upholding the “historic positions” of “godly” crackpots whose egos blew what little brains they had out their ears. See comments on Job 41 in that commentary.) The NKJV translators—who had the benefit of reading the heretical “Ruckman” before they sat down to pervert the word of God— pulled their necks in at Job 41:1 and refused to say “crocodile” in so many words; instead, they slipped through the cordon by saying “a large sea creature, exact identity unknown.” Isaiah knew him and identified him (Isa. 27:1). John knew him and identified him (Rev. 12:9). Job knew him and identified him (Job 41:1). But Arthur Farstad, James Price, Harold Willmington, Sumner, Wemp, E. Schyler English, Jerry Falwell, Elmer Towns, and Kroll couldn’t “identify him.” Twenty eight hundred years behind the times, is it? Yep, that is what it is . Fundamental scholars fear ridicule more than death or God. If they had “identified” him, they would have been the laughing stock of Life, Time, Newsweek, Reader’s Digest, the NEA, NAACP, ACLU, Congress, the Scholars Union, and the United Nations. They knew which side their bread was buttered on and who buttered it. “The god of this world” buttered it. The reference was to HIM. They sold the Book out to go along with him. “The Arabic lexicographers quoted by Bochart (Oh don’t you know, baby doll, we is gwine to get somethin’ now!) affirm that Pharaoh, in the Egyptian language, signified a crocodile” (Spurgeon, op cit., p. 28). “Oh goody. Lookee, mommy! Look at Moby Dick! He has seven heads, and he wasn’t even in Ripley’s ‘Believe It or Not’!” “Even as the sea monsters were washed up on the shore and furnished food for the inhabitants of the Red Sea, so the symbolic dragon power of Egypt when destroyed at the Red Sea became food for Israel’s faith...” (Spurgeon, p. 284).Had enough? Need some fresh air? \begin{compactenum}
\item If the reference is to Pharaoh’s army in Exodus, then his troops are demons (vs. 13) for “dragons” are manifestation of THE DRAGON, as “devils” (Mark 16:9) are rnanifestations of THE DEVIL.
\item If the dragon means just “Egypt,” somebody dropped their lunch: Nebuchadnezzar is called a dragon in Jeremiah 51:34, and so is Pharaoh in Ezekiel 29:3. ``A great red dragon'' is neither Egypt, Pharaoh, nor Nebuchadnezzar; he is Satan (Revelation 12:9).
\item “Leviathan” is no more a crocodile than a French poodle. He is typified on earth by the whale (Ps. 104:26), which puts Jonah in pretty rough shape and puts the Charismatics (who believe in the “sign of the fish”) in even worse shape. In actuality, the Leviathan described in Job 41 is no more a crocodile or a dinosaur than he is a computer. He is a seven headed dragon, and that is why the text said “heads” in the plural instead of the singular (vs. 14).
\end{compactenum}
“The plural heads is put for the singular” (Jamieson, Fausset, and Brown). That is: reject the text because you can’t explain it, knowing you can’t explain it because you lost the cross-references to it, and you lost them when you began to mess with the Book. “His monstrous head being equal in size to many heads” (Jamieson, Fausset, and Brown). Kiss my grits. \cite{Ruckman1992Psalms} }
[14] \textcolor[rgb]{0.00,0.00,1.00}{Thou brakest the heads of leviathan in pieces, \emph{and} gavest him \emph{to} \emph{be} \fcolorbox{blue}{yellow}{meat} to the people inhabiting the wilderness.}\index[AWIP]{Thou!Psalms!Psa 074:014}\index[AWIP]{brakest!Psalms!Psa 074:014}\index[AWIP]{the!Psalms!Psa 074:014}\index[AWIP]{heads!Psalms!Psa 074:014}\index[AWIP]{of!Psalms!Psa 074:014}\index[AWIP]{leviathan!Psalms!Psa 074:014}\index[AWIP]{in!Psalms!Psa 074:014}\index[AWIP]{pieces!Psalms!Psa 074:014}\index[AWIP]{\emph{and}!Psalms!Psa 074:014}\index[AWIP]{gavest!Psalms!Psa 074:014}\index[AWIP]{him!Psalms!Psa 074:014}\index[AWIP]{\emph{to}!Psalms!Psa 074:014}\index[AWIP]{\emph{be}!Psalms!Psa 074:014}\index[AWIP]{meat!Psalms!Psa 074:014}\index[AWIP]{to!Psalms!Psa 074:014}\index[AWIP]{the!Psalms!Psa 074:014 (2)}\index[AWIP]{people!Psalms!Psa 074:014}\index[AWIP]{inhabiting!Psalms!Psa 074:014}\index[AWIP]{the!Psalms!Psa 074:014 (3)}\index[AWIP]{wilderness!Psalms!Psa 074:014}\index[NWIV]{20!Psalms!Psa 074:014}
[15] \textcolor[rgb]{0.00,0.00,1.00}{Thou didst cleave the fountain and the flood: thou driedst up mighty rivers.}\footnote{[RUCKMAN] According to Kroll, Egypt was given to Israel to eat in the wilderness! And the funniest of all the Funnymentalists was Spurgeon’s writer telling you that the inhabitants of the Sinai Peninsula ATE large fishes that washed up on shore. The Jews complained about no fish to eat all the time they were on that peninsula. “Behold how great a matter a little King James Bible kindleth!” Where were the “mighty rivers” at the Red Sea crossing (vs. 15)? Only one river was dried up; it was Jordan, and that wasn’t at the Red Sea crossing. “Cleave the fountain”? What fountain? Jamieson, Fausset, and Brown get a “flood” out of the Rock, but then have to add Jabbok and Arnon to Jordan to get “rivers.” Jabbok and Arnon never dried up one time from Genesis 8 to Revelation 3. Motyer (just as lost as a golf ball in high weeds) has to have the corpses of Egyptian soldiers washed up on the beach for Arabians to eat on. Good old Kyle Yates will set us right, won’t he? Sic’em boy! “Using symbolic language and descriptive terminology drawn from the mythology of the Canaanites, the psalmist insists that it is God who has won the mighty victories of the PAST...while the figures of speech are derived from ancient Cretan stories....” I’ll “up you” one: “Confidence in an unfaithful man in time of trouble is like a broken tooth, and a foot out of joint” (Prov. 25:19). Yates has both feet planted firmly--in mid air. His scholarly exegesis (and the washed up fish above) remind me of a teacher who ordered a boy to make a sentence using the word “amphibious.” The student replied: “Most fish stories am fibious.” \cite{Ruckman1992Psalms} }
[16] \textcolor[rgb]{0.00,0.00,1.00}{The day \emph{is} thine, the night also \emph{is} thine: thou hast prepared the light and the sun.}\index[AWIP]{The!Psalms!Psa 074:016}\index[AWIP]{day!Psalms!Psa 074:016}\index[AWIP]{\emph{is}!Psalms!Psa 074:016}\index[AWIP]{thine!Psalms!Psa 074:016}\index[AWIP]{the!Psalms!Psa 074:016}\index[AWIP]{night!Psalms!Psa 074:016}\index[AWIP]{also!Psalms!Psa 074:016}\index[AWIP]{\emph{is}!Psalms!Psa 074:016 (2)}\index[AWIP]{thine!Psalms!Psa 074:016 (2)}\index[AWIP]{thou!Psalms!Psa 074:016}\index[AWIP]{hast!Psalms!Psa 074:016}\index[AWIP]{prepared!Psalms!Psa 074:016}\index[AWIP]{the!Psalms!Psa 074:016 (2)}\index[AWIP]{light!Psalms!Psa 074:016}\index[AWIP]{and!Psalms!Psa 074:016}\index[AWIP]{the!Psalms!Psa 074:016 (3)}\index[AWIP]{sun!Psalms!Psa 074:016}\index[NWIV]{17!Psalms!Psa 074:016}
[17] \textcolor[rgb]{0.00,0.00,1.00}{Thou hast set all the borders of the earth: thou hast made summer and winter.}\index[AWIP]{Thou!Psalms!Psa 074:017}\index[AWIP]{hast!Psalms!Psa 074:017}\index[AWIP]{set!Psalms!Psa 074:017}\index[AWIP]{all!Psalms!Psa 074:017}\index[AWIP]{the!Psalms!Psa 074:017}\index[AWIP]{borders!Psalms!Psa 074:017}\index[AWIP]{of!Psalms!Psa 074:017}\index[AWIP]{the!Psalms!Psa 074:017 (2)}\index[AWIP]{earth!Psalms!Psa 074:017}\index[AWIP]{thou!Psalms!Psa 074:017}\index[AWIP]{hast!Psalms!Psa 074:017 (2)}\index[AWIP]{made!Psalms!Psa 074:017}\index[AWIP]{summer!Psalms!Psa 074:017}\index[AWIP]{and!Psalms!Psa 074:017}\index[AWIP]{winter!Psalms!Psa 074:017}\index[NWIV]{15!Psalms!Psa 074:017}
[18] \textcolor[rgb]{0.00,0.00,1.00}{Remember this, \emph{that} the enemy hath reproached, O LORD, and \emph{that} the foolish people have blasphemed thy name.}\index[AWIP]{Remember!Psalms!Psa 074:018}\index[AWIP]{this!Psalms!Psa 074:018}\index[AWIP]{\emph{that}!Psalms!Psa 074:018}\index[AWIP]{the!Psalms!Psa 074:018}\index[AWIP]{enemy!Psalms!Psa 074:018}\index[AWIP]{hath!Psalms!Psa 074:018}\index[AWIP]{reproached!Psalms!Psa 074:018}\index[AWIP]{O!Psalms!Psa 074:018}\index[AWIP]{LORD!Psalms!Psa 074:018}\index[AWIP]{and!Psalms!Psa 074:018}\index[AWIP]{\emph{that}!Psalms!Psa 074:018 (2)}\index[AWIP]{the!Psalms!Psa 074:018 (2)}\index[AWIP]{foolish!Psalms!Psa 074:018}\index[AWIP]{people!Psalms!Psa 074:018}\index[AWIP]{have!Psalms!Psa 074:018}\index[AWIP]{blasphemed!Psalms!Psa 074:018}\index[AWIP]{thy!Psalms!Psa 074:018}\index[AWIP]{name!Psalms!Psa 074:018}\index[NWIV]{18!Psalms!Psa 074:018}\index[PNIP]{LORD!Psalms!Psa 074:018}
[19] \textcolor[rgb]{0.00,0.00,1.00}{O deliver not the \fcolorbox{blue}{yellow}{soul} of thy turtledove unto the multitude \emph{of} \emph{the} \emph{wicked}: forget not the congregation of thy poor for ever.}\index[AWIP]{O!Psalms!Psa 074:019}\index[AWIP]{deliver!Psalms!Psa 074:019}\index[AWIP]{not!Psalms!Psa 074:019}\index[AWIP]{the!Psalms!Psa 074:019}\index[AWIP]{soul!Psalms!Psa 074:019}\index[AWIP]{of!Psalms!Psa 074:019}\index[AWIP]{thy!Psalms!Psa 074:019}\index[AWIP]{turtledove!Psalms!Psa 074:019}\index[AWIP]{unto!Psalms!Psa 074:019}\index[AWIP]{the!Psalms!Psa 074:019 (2)}\index[AWIP]{multitude!Psalms!Psa 074:019}\index[AWIP]{\emph{of}!Psalms!Psa 074:019}\index[AWIP]{\emph{the}!Psalms!Psa 074:019}\index[AWIP]{\emph{wicked}!Psalms!Psa 074:019}\index[AWIP]{forget!Psalms!Psa 074:019}\index[AWIP]{not!Psalms!Psa 074:019 (2)}\index[AWIP]{the!Psalms!Psa 074:019 (3)}\index[AWIP]{congregation!Psalms!Psa 074:019}\index[AWIP]{of!Psalms!Psa 074:019 (2)}\index[AWIP]{thy!Psalms!Psa 074:019 (2)}\index[AWIP]{poor!Psalms!Psa 074:019}\index[AWIP]{for!Psalms!Psa 074:019}\index[AWIP]{ever!Psalms!Psa 074:019}\index[NWIV]{23!Psalms!Psa 074:019}
[20] \textcolor[rgb]{0.00,0.00,1.00}{Have respect unto the covenant: for the dark places of the earth are full of the habitations of cruelty.}\index[AWIP]{Have!Psalms!Psa 074:020}\index[AWIP]{respect!Psalms!Psa 074:020}\index[AWIP]{unto!Psalms!Psa 074:020}\index[AWIP]{the!Psalms!Psa 074:020}\index[AWIP]{covenant!Psalms!Psa 074:020}\index[AWIP]{for!Psalms!Psa 074:020}\index[AWIP]{the!Psalms!Psa 074:020 (2)}\index[AWIP]{dark!Psalms!Psa 074:020}\index[AWIP]{places!Psalms!Psa 074:020}\index[AWIP]{of!Psalms!Psa 074:020}\index[AWIP]{the!Psalms!Psa 074:020 (3)}\index[AWIP]{earth!Psalms!Psa 074:020}\index[AWIP]{are!Psalms!Psa 074:020}\index[AWIP]{full!Psalms!Psa 074:020}\index[AWIP]{of!Psalms!Psa 074:020 (2)}\index[AWIP]{the!Psalms!Psa 074:020 (4)}\index[AWIP]{habitations!Psalms!Psa 074:020}\index[AWIP]{of!Psalms!Psa 074:020 (3)}\index[AWIP]{cruelty!Psalms!Psa 074:020}\index[NWIV]{19!Psalms!Psa 074:020}\index[PNIP]{Have!Psalms!Psa 074:020}
[21] \textcolor[rgb]{0.00,0.00,1.00}{O let not the oppressed return ashamed: let the poor and needy praise thy name.}\index[AWIP]{O!Psalms!Psa 074:021}\index[AWIP]{let!Psalms!Psa 074:021}\index[AWIP]{not!Psalms!Psa 074:021}\index[AWIP]{the!Psalms!Psa 074:021}\index[AWIP]{oppressed!Psalms!Psa 074:021}\index[AWIP]{return!Psalms!Psa 074:021}\index[AWIP]{ashamed!Psalms!Psa 074:021}\index[AWIP]{let!Psalms!Psa 074:021 (2)}\index[AWIP]{the!Psalms!Psa 074:021 (2)}\index[AWIP]{poor!Psalms!Psa 074:021}\index[AWIP]{and!Psalms!Psa 074:021}\index[AWIP]{needy!Psalms!Psa 074:021}\index[AWIP]{praise!Psalms!Psa 074:021}\index[AWIP]{thy!Psalms!Psa 074:021}\index[AWIP]{name!Psalms!Psa 074:021}\index[NWIV]{15!Psalms!Psa 074:021}
[22] \textcolor[rgb]{0.00,0.00,1.00}{Arise, O God, plead thine own cause: remember how the foolish man reproacheth thee daily.}\index[AWIP]{Arise!Psalms!Psa 074:022}\index[AWIP]{O!Psalms!Psa 074:022}\index[AWIP]{God!Psalms!Psa 074:022}\index[AWIP]{plead!Psalms!Psa 074:022}\index[AWIP]{thine!Psalms!Psa 074:022}\index[AWIP]{own!Psalms!Psa 074:022}\index[AWIP]{cause!Psalms!Psa 074:022}\index[AWIP]{remember!Psalms!Psa 074:022}\index[AWIP]{how!Psalms!Psa 074:022}\index[AWIP]{the!Psalms!Psa 074:022}\index[AWIP]{foolish!Psalms!Psa 074:022}\index[AWIP]{man!Psalms!Psa 074:022}\index[AWIP]{reproacheth!Psalms!Psa 074:022}\index[AWIP]{thee!Psalms!Psa 074:022}\index[AWIP]{daily!Psalms!Psa 074:022}\index[NWIV]{15!Psalms!Psa 074:022}\index[PNIP]{God!Psalms!Psa 074:022}
[23] \textcolor[rgb]{0.00,0.00,1.00}{Forget not the voice of thine enemies: the tumult of those that rise up against thee increaseth continually.}\index[AWIP]{Forget!Psalms!Psa 074:023}\index[AWIP]{not!Psalms!Psa 074:023}\index[AWIP]{the!Psalms!Psa 074:023}\index[AWIP]{voice!Psalms!Psa 074:023}\index[AWIP]{of!Psalms!Psa 074:023}\index[AWIP]{thine!Psalms!Psa 074:023}\index[AWIP]{enemies!Psalms!Psa 074:023}\index[AWIP]{the!Psalms!Psa 074:023 (2)}\index[AWIP]{tumult!Psalms!Psa 074:023}\index[AWIP]{of!Psalms!Psa 074:023 (2)}\index[AWIP]{those!Psalms!Psa 074:023}\index[AWIP]{that!Psalms!Psa 074:023}\index[AWIP]{rise!Psalms!Psa 074:023}\index[AWIP]{up!Psalms!Psa 074:023}\index[AWIP]{against!Psalms!Psa 074:023}\index[AWIP]{thee!Psalms!Psa 074:023}\index[AWIP]{increaseth!Psalms!Psa 074:023}\index[AWIP]{continually!Psalms!Psa 074:023}\index[NWIV]{18!Psalms!Psa 074:023}\index[PNIP]{Forget!Psalms!Psa 074:023}
