\section{Psalm 68 Outlines}

\subsection{My Outlines}

\subsubsection{Some things which Belong to God}

\index[speaker]{Keith Anthony!Psalm 068 (Some things which Belong to God)}
\index[series]{Psalms (Keith Anthony)!Psalm 068 (Some things which Belong to God)}
\index[2018/08/12]{unknown!Psalm 068 (Some things which Belong to God) (Keith Anthony)}
\begin{compactenum}[I.]
    \item The \textbf{Removal} of his Enemies \index[scripture]{Psalms!Psa 068:02}(Psa 68:2)
    \item \textbf{Ministry}  \index[scripture]{Psalms!Psa 068:11}(Psa 68:11)
    \begin{compactenum}[A.]
    	\item To Captives \index[scripture]{Psalms!Psa 068:05}(Psa 68:5)
    	\item To Orphans \index[scripture]{Psalms!Psa 068:05}(Psa 68:5)
    	\item To Widows \index[scripture]{Psalms!Psa 068:05}(Psa 68:5)
    	\item To Sinners \index[scripture]{Psalms!Psa 068:20}(Psa 68:20)
    \end{compactenum}
    \item A \textbf{Message}  \index[scripture]{Psalms!Psa 068:11}(Psa 68:11)
    \item \textbf{Men}  \index[scripture]{Psalms!Psa 068:18}(Psa 68:18)
    \item Special \textbf{Music}  \index[scripture]{Psalms!Psa 068:25}(Psa 68:25)
    \item A \textbf{Millennial Reign}  \index[scripture]{Psalms!Psa 068:29}(Psa 68:29)
    \item A \textbf{Might Voice}  \index[scripture]{Psalms!Psa 068:33}(Psa 68:33)
\end{compactenum}

\subsubsection{Psalm 68: The First Half}

\index[speaker]{Keith Anthony!Psalm 068:01-18 (Psalm 68: The First Half)}
\index[series]{Psalms (Keith Anthony)!Psalm 068:01-18 (Psalm 68: The First Half)}
\index[2018/08/12]{unknown!Psalm 068:01-18 (Psalm 68: The First Half) (Keith Anthony)}
\begin{compactenum}[I.]
	\item A \textbf{Named Helper} \index[scripture]{Psalms!Psa 068:01-06}(Psa 68:1-6) In the Psalm the word ``God'' is found 31 times, the word ``Lord'' 7 times, the word ``LORD'' 2 times, the word ``Akmighty'' 1 times, the name ``JAH'' 1 time (only times in scripture). Names of God 15 times in the first 11 verses. But more than the specific names of God, he Psalm identifes God by what he does: (1) scatter shie enemeis (1), rides upon the heavens (4), takes care of orphans and widows (5), provides freedom for the captives  (6), punishes the rebellious (6), leads his perople through the wilderness (7), send the rain (9), provids for the poor (10), empowers the faithful (13), frees the captives (18). Verse 18 specifically speaks of the Lord freeing the Old Testament Jews waiting for him in Abraham's bosom. 	Verse 19 speaks of God daily loading his people with benefits. Vers 20 names God as the God of salvation. Remnds me of Psalm 74:12: For God is my King of old, working salvation in the midst of the earth. Verse 22 describes God as the one who brings his people from the depths of sea, picture a promised resurrection. Verse 29 describes him as one who will receive gifts from kings at his temple (has to be the Millennium).
	\item A \textbf{National History} \index[scripture]{Psalms!Psa 068:07-10}(Psa 68:7-10)(Assisted by Phillips) A variety of things distinguish Israel's history from other nations: 
	\begin{compactenum}[A.]
	\item Divine Presence \index[scripture]{Psalms!Psa 068:07-08}(Psa 68:7-8)
	\item Divine Power
	\item Divine Providence
	\item Divine Plan - even the  church Age is part of the pan
	\end{compactenum}
	\item The \textbf{National Heritage} \index[scripture]{Psalms!Psa 068:11-14}(Psa 68:11-14)
	\item A \textbf{Notable Homeland} \index[scripture]{Psalms!Psa 068:15-18}(Psa 68:15-18)
\end{compactenum}
