\section{Psalm 74 Comments}

\subsection{Numeric Nuggets}
\textbf{13: } Verse 15 has 13 words.  Verses 12, 16, 17, and 21 have 13 unique words.  The 13-letter word ``congregations'' is used in verse 4.

\subsection{Psalm 74:3}
The phrase ``perpetual desolations'' is found 4 times in the AV: (1) Psalm 74:3, (2) Jeremiah 25:9, (3) Jeremiah 25:12, and (4) Ezekiel 35:9. Specifically it refers to the the destruction of Babylon after the 70  year captivity of the Jews. In Ezekiel 35:2, they boast of the desolation they have brought upon Israel -- God will ``do unto others, as they have done unto Israel!''. \textbf{Ezekiel 35:9--15}: I will make thee perpetual desolations, and thy cities shall not return: and ye shall know that I am the LORD. [10] Because thou hast said, These two nations and these two countries shall be mine, and we will possess it; whereas the LORD was there: [11] Therefore, as I live, saith the Lord GOD, I will even do according to thine anger, and according to thine envy which thou hast used out of thy hatred against them; and I will make myself known among them, when I have judged thee. [12] And thou shalt know that I am the LORD, and that I have heard all thy blasphemies which thou hast spoken against the mountains of Israel, saying, They are laid desolate, they are given us to consume. [13] Thus with your mouth ye have boasted against me, and have multiplied your words against me: I have heard them. [14] Thus saith the Lord GOD; When the whole earth rejoiceth, I will make thee desolate. [15] As thou didst rejoice at the inheritance of the house of Israel, because it was desolate, so will I do unto thee: thou shalt be desolate, O mount Seir, and all Idumea, even all of it: and they shall know that I am the LORD.\cite{Ruckman1992PsalmsV2}

\subsection{Psalm 74:8}
\include{19OT-Psalms/CorruptionAlerts/Psalm-74-8}

\subsection{Psalm 74:9}
The signs that the Jews seek do not cease until the Jews had completely rejected the kingdom offer in the Book of Acts. 

\subsection{Psalm 74:10}
Suggestions for specific identity of ``the adversary'' are provided in scripture. See, for example, Lamentations 4:12 (tribulation content), Matthew 5:25 (tribulation content), 1 Timothy 5:14, 1 Peter 5:8.\footnote{\textbf{Lamentations 4:12} - The kings of the earth, and all the inhabitants of the world, would not have believed that the adversary and the enemy should have entered into the gates of Jerusalem.}\footnote{\textbf{Matthew 5:25} - Agree with thine adversary quickly, whiles thou art in the way with him; lest at any time the adversary deliver thee to the judge, and the judge deliver thee to the officer, and thou be cast into prison.}\footnote{\textbf{1 Timothy 5:14} - I will therefore that the younger women marry, bear children, guide the house, give none occasion to the adversary to speak reproachfully.}\footnote{\textbf{1 Peter 5:8} - I will therefore that the younger women marry, bear children, guide the house, give none occasion to the adversary to speak reproachfully.}
