\section{Psalm 77 Comments}

\subsection{Numeric Nuggets}
Verses 4, 8, and 12 have 13 words. Verses 1 and 16 have 13 unique words. The word ``I'' is used 13 times in the chapter (the word ``I'' in italics is found once). The 13$^{th}$ word in the chapter is the word ``voice'' (it is also the 7$^{th}$ word). The use of the word ``I'' ceases in verse 12. Verse 13 seems to be a transition verse: it has 13 words that are not italic! Verse 13 contains the word \emph{our} indicating the psalmist's recognition and acceptance of his place among God's redeemed people, Israel. The psalmist sends out six questions in verses 7-9, before the second ``Selah'' in verse 9 (the other two are in verses 3 and 15). Three ``Selahs'' are likely quite significant and likely have something to do with specific dealings of the LORD with Tribulation Israel.

\subsection{Psalm 77 Introduction}
The doctrinal content of this psalm is the Second Advent of Jesus Christ and his rescue of his people Israel. Spiritually, a sinner must recognize his desperate, deplorable, and hopeless condition before he will cry out to God for salvation. 

\subsection{Psalm 77:1}
Jeremiah 51:16 connects the ``voice'' with lightnings (as seen in verse 18).\footnote{\textbf{Jeremiah 51:16} - When he uttereth his voice, there is a multitude of waters in the heavens; and he causeth the vapours to ascend from the ends of the earth: he maketh lightnings with rain, and bringeth forth the wind out of his treasures.}

\subsection{Psalm 77:2}
This ``sore'' is the loathsome disease spoken of in Psalm 38:7.
\input{19OT-Psalms/CorruptionAlerts/Psalm-77-2}

\subsection{Psalm 77:6}
Compare this ``diligent search'' with the diligent search carried out by the wicked.\footnote{\textbf{Psalm 64:6} - They search out iniquities; they accomplish a diligent search: both the inward thought of every one of them, and the heart, is deep. }

\subsection{Psalm 77:7-9}
The psalmist poses six questions:
\begin{compactenum}
    \item Will the Lord cast off for ever?
    \item Will he be favourable no more?
    \item Is his mercy clean gone for ever?
    \item Doth his promise fail for evermore?
    \item Hath God forgotten to be gracious 
    \item Hath he in anger shut up his tender mercies?\\
\end{compactenum}

\subsection{Psalm 77:10}
Note the mention of body, soul, and spirit in verses 2 and 3.
\include{19OT-Psalms/CorruptionAlerts/Psalm-77-10}

\noindent The answer (to the six questions), in general, with respect to Israel, is a resounding ``No!'' The mercies are called for by David in 2 Samuel 24:14 and 1 Chronicles 21:13.\footnote{\textbf{2 Samuel 24:14} - And David said unto Gad, I am in a great strait: let us fall now into the hand of the LORD; for his mercies are great: and let me not fall into the hand of man.}\footnote{\textbf{1 Chronicles 21:13} - And David said unto Gad, I am in a great strait: let me fall now into the hand of the LORD; for very great are his mercies: but let me not fall into the hand of man.}\cite{Ruckman1992PsalmsV2}

\subsection{Psalm 77:9}
The phrase ``tender mercies'' shows up eleven times in scripture, ten occurrences of which speak of the Lord's ``tender mercies.'' All of these are in Psalms (Psalms 25:6, 40:11, 51:1, 69:16, 77:9, 79:8, 103:4, 119:77, 119:156, and  145:9.) Number eleven describes the ``tender mercies'' of the wicked, called cruel. So, question number six is answered (confirmed in Lamentations 3:22). \footnote{\textbf{Lamentations 3:22} - It is of the LORD’S mercies that we are not consumed, because his compassions fail not.} But, in Jeremiah 16:5, they are temporarily taken away.\footnote{\textbf{Jeremiah 16:5} - For thus saith the LORD, Enter not into the house of mourning, neither go to lament nor bemoan them: for I have taken away my peace from this people, saith the LORD, even lovingkindness and mercies.}\cite{Ruckman1992PsalmsV2}

\subsection{Psalm 77:17-19}
Psalm 18 is a wonderful parallel passage to Psalm 77. Verse 14 speaks of God's arrows and lightnings. It also speaks of the ``channels'' of waters spoke of here in verse 18. This ``path in the great waters'' is the route the LORD will take with his armies for is return at the Second Advent.\footnote{\textbf{PSalm 18} - I will love thee, O LORD, my strength. [2] The LORD is my rock, and my fortress, and my deliverer; my God, my strength, in whom I will trust; my buckler, and the horn of my salvation, and my high tower. [3] I will call upon the LORD, who is worthy to be praised: so shall I be saved from mine enemies. [4] The sorrows of death compassed me, and the floods of ungodly men made me afraid. [5] The sorrows of hell compassed me about: the snares of death prevented me. [6] In my distress I called upon the LORD, and cried unto my God: he heard my voice out of his temple, and my cry came before him, even into his ears. [7] Then the earth shook and trembled; the foundations also of the hills moved and were shaken, because he was wroth. [8] There went up a smoke out of his nostrils, and fire out of his mouth devoured: coals were kindled by it. [9] He bowed the heavens also, and came down: and darkness was under his feet. [10] And he rode upon a cherub, and did fly: yea, he did fly upon the wings of the wind. [11] He made darkness his secret place; his pavilion round about him were dark waters and thick clouds of the skies. [12] At the brightness that was before him his thick clouds passed, hail stones and coals of fire. [13] The LORD also thundered in the heavens, and the Highest gave his voice; hail stones and coals of fire. [14] Yea, he sent out his arrows, and scattered them; and he shot out lightnings, and discomfited them. [15] Then the channels of waters were seen, and the foundations of the world were discovered at thy rebuke, O LORD, at the blast of the breath of thy nostrils. [16] He sent from above, he took me, he drew me out of many waters. [17] He delivered me from my strong enemy, and from them which hated me: for they were too strong for me. [18] They prevented me in the day of my calamity: but the LORD was my stay. [19] He brought me forth also into a large place; he delivered me, because he delighted in me. [20] The LORD rewarded me according to my righteousness; according to the cleanness of my hands hath he recompensed me. [21] For I have kept the ways of the LORD, and have not wickedly departed from my God. [22] For all his judgments were before me, and I did not put away his statutes from me. [23] I was also upright before him, and I kept myself from mine iniquity. [24] Therefore hath the LORD recompensed me according to my righteousness, according to the cleanness of my hands in his eyesight. [25] With the merciful thou wilt shew thyself merciful; with an upright man thou wilt shew thyself upright; [26] With the pure thou wilt shew thyself pure; and with the froward thou wilt shew thyself froward. [27] For thou wilt save the afflicted people; but wilt bring down high looks. [28] For thou wilt light my candle: the LORD my God will enlighten my darkness. [29] For by thee I have run through a troop; and by my God have I leaped over a wall. [30] As for God, his way is perfect: the word of the LORD is tried: he is a buckler to all those that trust in him. [31] For who is God save the LORD? or who is a rock save our God? [32] It is God that girdeth me with strength, and maketh my way perfect. [33] He maketh my feet like hinds’ feet, and setteth me upon my high places. [34] He teacheth my hands to war, so that a bow of steel is broken by mine arms. [35] Thou hast also given me the shield of thy salvation: and thy right hand hath holden me up, and thy gentleness hath made me great. [36] Thou hast enlarged my steps under me, that my feet did not slip. [37] I have pursued mine enemies, and overtaken them: neither did I turn again till they were consumed. [38] I have wounded them that they were not able to rise: they are fallen under my feet. [39] For thou hast girded me with strength unto the battle: thou hast subdued under me those that rose up against me. [40] Thou hast also given me the necks of mine enemies; that I might destroy them that hate me. [41] They cried, but there was none to save them: even unto the LORD, but he answered them not. [42] Then did I beat them small as the dust before the wind: I did cast them out as the dirt in the streets. [43] Thou hast delivered me from the strivings of the people; and thou hast made me the head of the heathen: a people whom I have not known shall serve me. [44] As soon as they hear of me, they shall obey me: the strangers shall submit themselves unto me. [45] The strangers shall fade away, and be afraid out of their close places. [46] The LORD liveth; and blessed be my rock; and let the God of my salvation be exalted. [47] It is God that avengeth me, and subdueth the people under me. [48] He delivereth me from mine enemies: yea, thou liftest me up above those that rise up against me: thou hast delivered me from the violent man. [49] Therefore will I give thanks unto thee, O LORD, among the heathen, and sing praises unto thy name. [50] Great deliverance giveth he to his king; and sheweth mercy to his anointed, to David, and to his seed for evermore.}\cite{Ruckman1992PsalmsV2}

\subsection{Psalm 77:20}
Another comparison is the in Numbers 33:1.\footnote{\textbf{Numbers 33:1} - These are the journeys of the children of Israel, which went forth out of the land of Egypt with their armies under the hand of Moses and Aaron.}\cite{Ruckman1992PsalmsV2}

