\chapter{Judges 13 Notes \& Analysis}
\section{Judges 13:1}
\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{JudgesTOC}{Return to end of Table of Contents.}}}\textcolor[rgb]{0.00,0.00,1.00}{And the children of Israel did evil again in the sight of the LORD; and the LORD delivered them into the hand of the Philistines forty years.}\\
\\
\section{Judges 13:2}
\P \textcolor[rgb]{0.00,0.00,1.00}{And there was a certain man of Zorah, of the family of the Danites, whose name \emph{was} Manoah; and his wife \emph{was} barren, and bare not.}
\section{Judges 13:3}
[3] \textcolor[rgb]{0.00,0.00,1.00}{And the angel of the LORD appeared unto the woman, and said unto her, Behold now, thou \emph{art} barren, and bearest not: but thou shalt conceive, and bear a son.}
\section{Judges 13:4}
[4] \textcolor[rgb]{0.00,0.00,1.00}{Now therefore beware, I pray thee, and drink not wine nor strong drink, and eat not any unclean \emph{thing}:}
\section{Judges 13:5}
[5] \textcolor[rgb]{0.00,0.00,1.00}{For, lo, thou shalt conceive, and bear a son; and no razor shall come on his head: for the child shall be a Nazarite unto God from the womb: and he shall begin to deliver Israel out of the hand of the Philistines.}\\
\\
Just a quick comment or two about Nazirites. Read all about it in Number 6. Mostly it was a vow which somebody made for a limited time -- usually 30 days. Samson, however, was to be a Nazirite all his life. The name Nazirite means ‘separate’ or ‘set apart’. Three main commands are given – 1) They could not drink or eat fruit from the vine. (No wine, grapes etc.) 2) Could not go near a dead body, or defile themselves by touching anything ‘unclean’. 3) Could not cut their hair all their days. Now while there is no command concerning Nazirites in the New Testament, all of these things can be applied to the believer today. God is still looking for those that are truly His to use. The wine or fruit of the vine is used as a type in scripture of human joy… worldly pleasures and pursuits. Our joy should come from knowing the Lord. Not touching a dead body or things unclean, speak of improper associations or relationships with those spiritually dead. That is why 2 Cor 6:17 is quoted in the context of not being bound together with unbelievers. Finally, long hair seems to speak of God’s strength in our weakness. This was certainly the case with Samson in that the cutting of his hair equates with losing his strength from God.
\section{Judges 13:6}
\P \textcolor[rgb]{0.00,0.00,1.00}{Then the woman came and told her husband, saying, A man of God came unto me, and his countenance \emph{was} like the countenance of an angel of God, very terrible: but I asked him not whence he \emph{was}, neither told he me his name:}
\section{Judges 13:7}
[7] \textcolor[rgb]{0.00,0.00,1.00}{But he said unto me, Behold, thou shalt conceive, and bear a son; and now drink no wine nor strong drink, neither eat any unclean \emph{thing}: for the child shall be a Nazarite to God from the womb to the day of his death.}\\
\\
It is not a type as such, just a parallel. As the book of Judges progresses we see more and more of the truth expressed in the last verse of the book coming into play -- ‘In those days there was no king in Israel; everyone did what was right in his own eyes.’ We are even starting to see this in Samson’s life, and He was God’s deliverer! Does this not remind us of the last Church age mentioned in Revelation – Laodicea, which means ‘the peoples opinions’ or ‘the peoples rule.’ And do we not see this increasing when we look at the western church as a whole today? Jesus isn’t being enthroned as King and even his people (professed) are starting to ‘do what is right in their own eyes.’
\section{Judges 13:8}
\P \textcolor[rgb]{0.00,0.00,1.00}{Then Manoah intreated the LORD, and said, O my Lord, let the man of God which thou didst send come again unto us, and teach us what we shall do unto the child that shall be born.}
\section{Judges 13:7}
[9] \textcolor[rgb]{0.00,0.00,1.00}{And God hearkened to the voice of Manoah; and the angel of God came again unto the woman as she sat in the field: but Manoah her husband \emph{was} not with her.}
\section{Judges 13:10}
[10] \textcolor[rgb]{0.00,0.00,1.00}{And the woman made haste, and ran, and shewed her husband, and said unto him, Behold, the man hath appeared unto me, that came unto me the \emph{other} day.}
\section{Judges 13:11}
[11] \textcolor[rgb]{0.00,0.00,1.00}{And Manoah arose, and went after his wife, and came to the man, and said unto him, \emph{Art} thou the man that spakest unto the woman? And he said, I \emph{am}.}
\section{Judges 13:12}
[12] \textcolor[rgb]{0.00,0.00,1.00}{And Manoah said, Now let thy words come to pass. How shall we order the child, and \emph{how} shall we do unto him?}
\section{Judges 13:13}
[13] \textcolor[rgb]{0.00,0.00,1.00}{And the angel of the LORD said unto Manoah, Of all that I said unto the woman let her beware.}
\section{Judges 13:14}
[14] \textcolor[rgb]{0.00,0.00,1.00}{She may not eat of any \emph{thing} that cometh of the vine, neither let her drink wine or strong drink, nor eat any unclean \emph{thing}: all that I commanded her let her observe.}\\
\\
\section{Judges 13:15}
\P \textcolor[rgb]{0.00,0.00,1.00}{And Manoah said unto the angel of the LORD, I pray thee, let us detain thee, until we shall have made ready a kid for thee.}
\section{Judges 13:16}
[16] \textcolor[rgb]{0.00,0.00,1.00}{And the angel of the LORD said unto Manoah, Though thou detain me, I will not eat of thy bread: and if thou wilt offer a burnt offering, thou must offer it unto the LORD. For Manoah knew not that he \emph{was} an angel of the LORD.}
\section{Judges 13:17}
[17] \textcolor[rgb]{0.00,0.00,1.00}{And Manoah said unto the angel of the LORD, What \emph{is} thy name, that when thy sayings come to pass we may do thee honour?}
\section{Judges 13:18}
[18] \textcolor[rgb]{0.00,0.00,1.00}{And the angel of the LORD said unto him, Why askest thou thus after my name, seeing it \emph{is} secret?}
\section{Judges 13:19}
[19] \textcolor[rgb]{0.00,0.00,1.00}{So Manoah took a kid with a meat offering, and offered \emph{it} upon a rock unto the LORD: and \emph{the angel} did wondrously; and Manoah and his wife looked on.}
\section{Judges 13:20}
[20] \textcolor[rgb]{0.00,0.00,1.00}{For it came to pass, when the flame went up toward heaven from off the altar, that the angel of the LORD ascended in the flame of the altar. And Manoah and his wife looked on \emph{it}, and fell on their faces to the ground.}
\section{Judges 13:21}
[21] \textcolor[rgb]{0.00,0.00,1.00}{But the angel of the LORD did no more appear to Manoah and to his wife. Then Manoah knew that he \emph{was} an angel of the LORD.}
\section{Judges 13:22}
[22] \textcolor[rgb]{0.00,0.00,1.00}{And Manoah said unto his wife, We shall surely die, because we have seen God.}
\section{Judges 13:23}
[23] \textcolor[rgb]{0.00,0.00,1.00}{But his wife said unto him, If the LORD were pleased to kill us, he would not have received a burnt offering and a meat offering at our hands, neither would he have shewed us all these \emph{things}, nor would as at this time have told us \emph{such things} as these.}\\
\\
\section{Judges 13:24}
\P \textcolor[rgb]{0.00,0.00,1.00}{And the woman bare a son, and called his name Samson: and the child grew, and the LORD blessed him.}
\section{Judges 13:25}
[25] \textcolor[rgb]{0.00,0.00,1.00}{And the Spirit of the LORD began to move him at times in the camp of Dan between Zorah and Eshtaol.}
\newpage
