\chapter{Judges 15}
 %  \textcolor[cmyk]{0.99998,1,0,0}{

\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{SAMSON'S ADVENTURES}\\ (Judges 15) \begin{compactenum}[I.][8]
    \item  A \textbf{Regifting} \index[scripture]{Judges!Jdg 15:02} (Jdg 15:2) 
    \item  \textbf{Revenge} \index[scripture]{Judges!Jdg 15:05} (Jdg 15:5) 
    \item  The \textbf{Removing} of the Killers \index[scripture]{Judges!Jdg 15:08} (Jdg 15:8) 
    \item  \textbf{Rulers} \index[scripture]{Judges!Jdg 15:11} (Jdg 15:11) 
    \item  \textbf{Ropes} \index[scripture]{Judges!Jdg 15:13} (Jdg 15:13) 
    \item  \textbf{Rage} \index[scripture]{Judges!Jdg 15:15} (Jdg 15:15) 
    \item  \textbf{Revival} \index[scripture]{Judges!Jdg 15:19} (Jdg 15:19) 
\end{compactenum}}


\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{JudgesTOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/judges_15.html}{\textcolor[cmyk]{0.99998,1,0,0}{Judges 15 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{But it came \fcolorbox{bone}{bone}{to} pass within a while after, in the time of wheat harvest, that Samson visited his wife with a kid; and he said, I will go in \fcolorbox{bone}{bone}{to} my wife into the chamber. But her father would not suffer him \fcolorbox{bone}{bone}{to} go in.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And her father said, I verily thought that thou hadst utterly hated her; therefore I gave her \fcolorbox{bone}{bone}{to} thy companion: \emph{is} not her younger sister fairer than she? take her, I pray thee, instead of her.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Samson said concerning them, Now shall I be more blameless than the Philistines, though I do them a displeasure.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And Samson went and caught three hundred foxes, and took firebrands, and turned tail \fcolorbox{bone}{bone}{to} tail, and put a firebrand in the midst between two tails.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{And when he had set the brands on fire, he let \emph{them} go into the standing corn of the Philistines, and burnt up both the shocks, and also the standing corn, with the vineyards \emph{and} olives.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Then the Philistines said, Who hath done this? And they answered, Samson, the son in law of the Timnite, because he had taken his wife, and given her \fcolorbox{bone}{bone}{to} his companion. And the Philistines came up, and burnt her and her father with fire.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And Samson said unto them, Though ye have done this, yet will I be avenged of you, and after that I will cease.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And he smote them hip and thigh with a great slaughter: and he went down and dwelt in the top of the rock Etam.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Then the Philistines went up, and pitched in Judah, and spread themselves in Lehi.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{And the men of Judah said, Why are ye come up against us? And they answered, To bind Samson are we come up, \fcolorbox{bone}{bone}{to} do \fcolorbox{bone}{bone}{to} him as he hath done \fcolorbox{bone}{bone}{to} us.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{Then three thousand men of Judah went \fcolorbox{bone}{bone}{to} the top of the rock Etam, and said \fcolorbox{bone}{bone}{to} Samson, Knowest thou not that the Philistines \emph{are} rulers over us? what \emph{is} this \emph{that} thou hast done unto us? And he said unto them, As they did unto me, so have I done unto them.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And they said unto him, We are come down \fcolorbox{bone}{bone}{to} bind thee, that we may deliver thee into the hand of the Philistines. And Samson said unto them, Swear unto me, that ye will not fall upon me yourselves.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And they spake unto him, saying, No; but we will bind thee fast, and deliver thee into their hand: but surely we will not kill thee. And they bound him with two new cords, and brought him up from the rock.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\emph{And} when he came unto Lehi, the Philistines shouted against him: and the Spirit of the LORD came mightily upon him, and the cords that \emph{were} upon his arms became as flax that was burnt with fire, and his bands loosed from off his hands.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{And he found a new jawbone of an ass, and put forth his hand, and took it, and slew a thousand men therewith.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And it came \fcolorbox{bone}{bone}{to} pass, when he had made an end of speaking, that he cast away the jawbone out of his hand, and called that place Ramath-lehi.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And he was sore athirst, and called on the LORD, and said, Thou hast given this great deliverance into the hand of thy servant: and now shall I die for thirst, and fall into the hand of the uncircumcised?}
[19] \textcolor[cmyk]{0.99998,1,0,0}{But God clave an hollow place that \emph{was} in the jaw, and there came water thereout; and when he had drunk, his spirit came again, and he revived: wherefore he called the name thereof En-hakkore, which \emph{is} in Lehi unto this day.}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And he judged Israel in the days of the Philistines twenty years.}