\chapter{Judges 10}
 %  \textcolor[cmyk]{0.99998,1,0,0}{

\marginpar{\scriptsize \centering \fcolorbox{black}{lime}{\textbf{2$^{nd}$} WAVE OF JUDGES}\\ (Judges 10) \begin{compactenum}[I.][8]
    \item  \textbf{Declining Character} \index[scripture]{Judges!Jdg 10:04}(Jdg 10:4) -- Tola and Jair are famous for wealth, Jephthah and Samson for their failures
    \item  \textbf{Desperate Conditions} \index[scripture]{Judges!Jdg 10:08}(Jdg 10:8)
    \item  \textbf{Despicable Conduct} \index[scripture]{Judges!Jdg 10:06}(Jdg 10:6)
    \item  A \textbf{Dash of Conscience} \index[scripture]{Judges!Jdg 10:15}(Jdg 10:15)
    \item  A \textbf{Deliverance Cry} \index[scripture]{Judges!Jdg 10:15}(Jdg 10:15)
    \item   \textbf{Dismissed Charges} \index[scripture]{Judges!Jdg 10:16}(Jdg 10:16)
    \item  A \textbf{Desired Champion} \index[scripture]{Judges!Jdg 10:18}(Jdg 10:18)
\end{compactenum}}


\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{JudgesTOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/judges_10.html}{\textcolor[cmyk]{0.99998,1,0,0}{Judges 10 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And after Abimelech there arose to defend \fcolorbox{bone}{bone}{Israel} Tola the son of Puah, the son of Dodo, a man of Issachar; and he dwelt in Shamir in mount Ephraim.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And he judged \fcolorbox{bone}{bone}{Israel} twenty and three years, and died, and was buried in Shamir.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And after him arose Jair, a Gileadite, and judged \fcolorbox{bone}{bone}{Israel} twenty and two years.}
[4] \textcolor[cmyk]{0.99998,1,0,0}{And he had thirty sons that rode on thirty ass colts, and they had thirty cities, which are called Havoth-jair unto this day, which \emph{are} in the land of Gilead.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And Jair died, and was buried in Camon.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel} did evil again in the sight of the LORD, and served Baalim, and Ashtaroth, and the gods of Syria, and the gods of Zidon, and the gods of Moab, and the gods of \fcolorbox{bone}{bone}{the children of} Ammon, and the gods of the Philistines, and forsook the LORD, and served not him.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And the anger of the LORD was hot against \fcolorbox{bone}{bone}{Israel}, and he sold them into the hands of the Philistines, and into the hands of \fcolorbox{bone}{bone}{the children of} Ammon.}
[8] \textcolor[cmyk]{0.99998,1,0,0}{And that year they vexed and oppressed \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel}: eighteen years, all \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel} that \emph{were} on the other side Jordan in the land of the Amorites, which \emph{is} in Gilead.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{Moreover \fcolorbox{bone}{bone}{the children of} Ammon passed over Jordan to fight also against Judah, and against Benjamin, and against the house of Ephraim; so that \fcolorbox{bone}{bone}{Israel} was sore distressed.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel} cried unto the LORD, saying, We have sinned against thee, both because we have forsaken our God, and also served Baalim.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And the LORD said unto \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel}, \emph{Did} not \emph{I} \emph{deliver} \emph{you} from the Egyptians, and from the Amorites, from \fcolorbox{bone}{bone}{the children of} Ammon, and from the Philistines?}
[12] \textcolor[cmyk]{0.99998,1,0,0}{The Zidonians also, and the Amalekites, and the Maonites, did oppress you; and ye cried to me, and I delivered you out of their hand.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{Yet ye have forsaken me, and served other gods: wherefore I will deliver you no more.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{Go and cry unto the gods which ye have chosen; let them deliver you in the time of your tribulation.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel} said unto the LORD, We have sinned: do thou unto us whatsoever seemeth good unto thee; deliver us only, we pray thee, this day.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And they put away the strange gods from among them, and served the LORD: and his soul was grieved for the misery of \fcolorbox{bone}{bone}{Israel}.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{Then \fcolorbox{bone}{bone}{the children of} Ammon were gathered together, and encamped in Gilead. And \fcolorbox{bone}{bone}{the children of} \fcolorbox{bone}{bone}{Israel} assembled themselves together, and encamped in Mizpeh.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{And the people \emph{and} princes of Gilead said one to another, What man \emph{is} \emph{he} that will begin to fight against \fcolorbox{bone}{bone}{the children of} Ammon? he shall be head over all the inhabitants of Gilead.}