\chapter{Judges 12}
 %  \textcolor[cmyk]{0.99998,1,0,0}{

\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{TRIBAL TROUBLES}\\ (Judges 12) \begin{compactenum}[I.][8]
    \item  Ephraim's \textbf{Leanings} %\index[scripture]{Judges!Jdg 10:04}(Jdg 10:4) -- Tola and Jair are famous for wealth, Jephthah and Samson for their failures
    \item  Jephthah's \textbf{Legacy} %\index[scripture]{Judges!Jdg 10:04}(Jdg 10:4)  
     \item  A \textbf{Litmus} Test \index[scripture]{Judges!Jdg 12:06}(Jdg 12:6)
	\item  Painful \textbf{Losses}  \index[scripture]{Judges!Jdg 12:06}(Jdg 12:6)
	\item  Tragic \textbf{Litany}  of Judges %\index[scripture]{Jdg!Judges 12:06}(Jdg 12:6) 
	\item   \textbf{Little} Things % \index[scripture]{Judges!Jdg 12:06}(Jdg 12:6)
\end{compactenum}}


\footnote{\textcolor[rgb]{0.00,0.25,0.00}{\hyperlink{JudgesTOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/judges_12.html}{\textcolor[cmyk]{0.99998,1,0,0}{Judges 12 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} the men of Ephraim gathered themselves together, and went northward, and said unto Jephthah, Wherefore passedst thou over to fight against the children of Ammon, and didst not call us to go with thee? we will burn thine house upon thee with fire.}
[2] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} Jephthah said unto them, I and my people were at great strife with the children of Ammon; and when I called you, ye delivered me not out of their hands.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} when I saw that ye delivered \emph{me} not, I put my life in my hands, and passed over against the children of Ammon, and the LORD delivered them into my hand: wherefore then are ye come up unto me this day, to fight against me?}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Then Jephthah gathered together all the men of Gilead, and fought with Ephraim: and the men of Gilead smote Ephraim, because they said, Ye Gileadites \emph{are} fugitives of Ephraim among the Ephraimites, \emph{and} among the Manassites.}
[5] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} the Gileadites took the passages of Jordan before the Ephraimites: and it was \emph{so}, that when those Ephraimites which were escaped said, Let me go over; that the men of Gilead said unto him, \emph{Art} thou an Ephraimite? If he said, Nay;}
[6] \textcolor[cmyk]{0.99998,1,0,0}{Then said they unto him, Say now Shibboleth: and he said Sibboleth: for he could not frame to pronounce \emph{it} right. Then they took him, and slew him at the passages of Jordan: and there fell at that time of the Ephraimites forty and two thousand.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} Jephthah judged Israel six years. Then died Jephthah the Gileadite, and was buried in \emph{one} \emph{of} the cities of Gilead.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} after him Ibzan of Beth-lehem judged Israel.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} he had thirty sons, and thirty daughters, \emph{whom} he sent abroad, and took in thirty daughters from abroad for his sons. \fcolorbox{bone}{bone}{And} he judged Israel seven years.}
[10] \textcolor[cmyk]{0.99998,1,0,0}{Then died Ibzan, and was buried at Beth-lehem.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} after him Elon, a Zebulonite, judged Israel; and he judged Israel ten years.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} Elon the Zebulonite died, and was buried in Aijalon in the country of Zebulun.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} after him Abdon the son of Hillel, a Pirathonite, judged Israel.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} he had forty sons and thirty nephews, that rode on threescore and ten ass colts: and he judged Israel eight years.}
[15] \textcolor[cmyk]{0.99998,1,0,0}{\fcolorbox{bone}{bone}{And} Abdon the son of Hillel the Pirathonite died, and was buried in Pirathon in the land of Ephraim, in the mount of the Amalekites.}